---
title: "Sex Differences in Functional Connectivity"
author: "Audrey Luo"
output: 
  html_document:
    highlight: haddock
    code_folding: hide
    number_sections: no
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    number_sections: no
    toc: yes
    toc_depth: '4'
  word_document:
    toc: yes
    toc_depth: '4'
urlcolor: blue
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, include = TRUE) 
library(cowplot)
library(effsize)
library(ggdist)
library(ggpubr)
library(ggseg)
library(ggsegSchaefer)
library(kableExtra)
library(knitr)
library(paletteer)
library(purrr)
library(scales)
library(tidyverse)
 
# Set project root depending on whether code is running on PARCC or locally
if (dir.exists("/ceph/projects/sattertt/pennlinc-parcc/network_replication")) {
  root <- "/ceph/projects/sattertt/pennlinc-parcc/network_replication"
} else if (dir.exists("~/parcc/network_replication")) {
  root <- path.expand("~/parcc/network_replication")
} else {
  stop("Could not find network_replication project.")
}

# set directories
proj_root <- file.path(root, "covariate_analyses/sex_diff/")
input_root <- paste0(proj_root, "input")
output_root <- paste0(proj_root, "output")  
 
source(file.path(proj_root, "code/results/main_figures.R"))
source(file.path(root, "software/perm.sphere.p.R"))
```

```{r set color palette}
red_teal_white_base <- rev(c( "#A51122FF","#E14C21FF", "#F8A86BFF", "#FFFFFFFF","#ACDFD3FF", "#0B8CACFF","#324DA0FF"))
red_teal_white <- colorRampPalette(red_teal_white_base)
```

```{r load SAaxis and labels and spin test}
# load S-A axis
schaefer200x17_SAaxis <- read.csv(file.path(root, "SAaxis", "schaefer200x17_SAaxis.csv"))
schaefer200x17_SAaxis <- schaefer200x17_SAaxis %>% rename(region=label)

# load parcel labels
schaefer200x17.labels <- read.csv(file.path(root, "atlases", "parcellations", "schaefer200x17_regionlist_final.csv"))
schaefer200x17.labels <- schaefer200x17.labels$label
  
# load network-pair labels
schaefer200x17.networkpair.labels <- read.csv(file.path(root, "atlases", "parcellations", "schaefer200x17_netpair_labels_noduplicates.csv"))
schaefer200x17.networkpair.labels <- schaefer200x17.networkpair.labels[,1]

# load permuted schaefer200
perm.id.full_schaefer200x17 <- readRDS(file.path(root, "software", "rotate_parcellation", "schaefer200x17.coords_sphericalrotations_N10k_seed10.rds"))
```

## Sex contrast convention:
### Male = reference
### Female - Male
### Positive effect = Female > Male
### Negative effect = Male > Female

# 1. Males exhibit greater functional connectivity strength across the cortex
```{r load FC_strength sex effect}
sex.main.PNC.FC_strength <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "FC_strength"))
sex.main.PNC.FC_strength$region <- paste0("17", sex.main.PNC.FC_strength$region)
sex.main.PNC.FC_strength <- sig.effects(sex.main.PNC.FC_strength, "FC_strength", "sex", "PNC")
resi.PNC.FC_strength <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "PNC", "resi", "FC_strength", "PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.PNC.FC_strength$region <- paste0("17", resi.PNC.FC_strength$region )
resi.PNC.FC_strength <- resi.PNC.FC_strength %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.PNC.FC_strength <- merge(sex.main.PNC.FC_strength, resi.PNC.FC_strength)

sex.main.HCPD.FC_strength <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "FC_strength"))
sex.main.HCPD.FC_strength <- sig.effects(sex.main.HCPD.FC_strength, "FC_strength", "sex", "HCPD")
sex.main.HCPD.FC_strength$region <- paste0("17", sex.main.HCPD.FC_strength$region)
resi.HCPD.FC_strength <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HCPD", "resi", "FC_strength", "HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.HCPD.FC_strength$region <- paste0("17", resi.HCPD.FC_strength$region )
resi.HCPD.FC_strength <- resi.HCPD.FC_strength %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HCPD.FC_strength <- merge(sex.main.HCPD.FC_strength, resi.HCPD.FC_strength)

sex.main.NKI.FC_strength <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "FC_strength"))
sex.main.NKI.FC_strength <- sig.effects(sex.main.NKI.FC_strength, "FC_strength", "sex", "NKI")
sex.main.NKI.FC_strength$region <- paste0("17", sex.main.NKI.FC_strength$region)
resi.NKI.FC_strength <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "NKI", "resi", "FC_strength", "NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.NKI.FC_strength$region <- paste0("17", resi.NKI.FC_strength$region )
resi.NKI.FC_strength <- resi.NKI.FC_strength %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.NKI.FC_strength <- merge(sex.main.NKI.FC_strength, resi.NKI.FC_strength)

sex.main.HBN.FC_strength <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "FC_strength"))
sex.main.HBN.FC_strength <- sig.effects(sex.main.HBN.FC_strength, "FC_strength", "sex", "HBN")
sex.main.HBN.FC_strength$region <- paste0("17", sex.main.HBN.FC_strength$region)
resi.HBN.FC_strength <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HBN", "resi", "FC_strength", "HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.HBN.FC_strength$region <- paste0("17", resi.HBN.FC_strength$region )
resi.HBN.FC_strength <- resi.HBN.FC_strength %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HBN.FC_strength <- merge(sex.main.HBN.FC_strength, resi.HBN.FC_strength)

sex.main.all_datasets.FC_strength <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "FC_strength"))
sex.main.all_datasets.FC_strength <- sig.effects(sex.main.all_datasets.FC_strength, "FC_strength", "sex", "all_datasets")
sex.main.all_datasets.FC_strength$region <- paste0("17", sex.main.all_datasets.FC_strength$region)
resi.all_datasets.FC_strength <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "resi", "FC_strength", "all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.all_datasets.FC_strength$region <- paste0("17", resi.all_datasets.FC_strength$region )
resi.all_datasets.FC_strength <- resi.all_datasets.FC_strength %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.all_datasets.FC_strength <- merge(sex.main.all_datasets.FC_strength, resi.all_datasets.FC_strength)
```

```{r make FC_strength plots across datasets with resi, message = FALSE, warning = FALSE, fig.width = 5, fig.height = 6}
sex.main.PNC.FC_strength_lh_resi <- plot_cortex(sex.main.PNC.FC_strength, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.PNC.FC_strength_rh_resi <- plot_cortex(sex.main.PNC.FC_strength, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 

sex.main.HCPD.FC_strength_lh_resi <- plot_cortex(sex.main.HCPD.FC_strength, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.HCPD.FC_strength_rh_resi <- plot_cortex(sex.main.HCPD.FC_strength, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 

sex.main.NKI.FC_strength_lh_resi <- plot_cortex(sex.main.NKI.FC_strength, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.NKI.FC_strength_rh_resi <- plot_cortex(sex.main.NKI.FC_strength, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 

sex.main.HBN.FC_strength_lh_resi <- plot_cortex(sex.main.HBN.FC_strength, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.HBN.FC_strength_rh_resi <- plot_cortex(sex.main.HBN.FC_strength, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
 
sex.main.all_datasets.FC_strength_lh_resi <- plot_cortex(sex.main.all_datasets.FC_strength, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.FC_strength_rh_resi <- plot_cortex(sex.main.all_datasets.FC_strength, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200", horizontal_layout = TRUE) 

  
# legend
ylim1 = -0.26
ylim2 = 0.1
p <- ggplot() + 
  geom_brain(data = sex.main.HBN.FC_strength, atlas = schaefer17_200, mapping = aes(fill = RESI), show.legend = TRUE) +
  scale_fill_gradientn(colours = red_teal_white(256), values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
  theme_void() +
  theme(legend.title = element_blank(), legend.text = element_text(size = 10), legend.position = "bottom", legend.box = "horizontal",
        legend.key.height = unit(0.53, "cm"), legend.key.width = unit(1.07, "cm"), plot.margin = unit(c(0, 0.53, 0, -0.27), "cm"))

legend <- get_legend(p)
legend <- ggdraw() +
  draw_plot(legend, x = 0.23, y = 0, width = 0.54, height = 1) +
  draw_label("Male > Female", x = 0.075, y = 0.66, size = 10, hjust = 0) +
  draw_label("Female > Male", x = 0.925, y = 0.66, size = 10, hjust = 1) 

# arrange plots 
# PNC
FC_strength_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.FC_strength_lh_resi, sex.main.PNC.FC_strength_rh_resi, ncol = 2),
  top = text_grob("PNC", size = 10, face = "bold")
)

# HCP-D
FC_strength_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.FC_strength_lh_resi, sex.main.HCPD.FC_strength_rh_resi, ncol = 2),
  top = text_grob("HCP-D", size = 10, face = "bold")
)

# NKI
FC_strength_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.FC_strength_lh_resi, sex.main.NKI.FC_strength_rh_resi, ncol = 2),
  top = text_grob("NKI", size = 10, face = "bold")
)

# HBN
FC_strength_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.FC_strength_lh_resi, sex.main.HBN.FC_strength_rh_resi, ncol = 2),
  top = text_grob("HBN", size = 10, face = "bold")
)

 
# pooled dataset / all datasets
FC_strength_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.FC_strength_lh_resi, sex.main.all_datasets.FC_strength_rh_resi, ncol = 2),
  top = text_grob("Pooled Dataset", size = 10, face = "bold")
)


# blank plot for formatting
blank_space <- ggplot() + theme_void()

FC_strength_plots_row1 <- plot_grid(FC_strength_PNC, FC_strength_HCPD, ncol = 2)
FC_strength_plots_row2 <- plot_grid(FC_strength_NKI, FC_strength_HBN, ncol = 2)
FC_strength_plots_row1and2 <- plot_grid(FC_strength_plots_row1, FC_strength_plots_row2, nrow = 2)
FC_strength_plots <- annotate_figure(
  plot_grid(blank_space, FC_strength_plots_row1and2, FC_strength_all, legend, nrow = 4, rel_heights = c(0.05, 1.2, 0.35, 0.2)),
  top = text_grob("Functional Connectivity Strength", size = 10, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 10, y = 1)
)

```

```{r make FC_strength overlapping effects plot with resi}
# overlap plots
df_list_FC_strength <- list(
  PNC  = sex.main.PNC.FC_strength[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.FC_strength[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.FC_strength[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.FC_strength[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.FC_strength <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_FC_strength)
sex.main.overlap.FC_strength$signif_count <- rowSums(sex.main.overlap.FC_strength[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.FC_strength$signif_count_factor <- factor(
  sex.main.overlap.FC_strength$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.FC_strength <- sex.main.overlap.FC_strength %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))

count_colors <- c(
  "0" = "white",
  "1" = "white",
  "2" = "#fcdac0",
  "3" = "#e87b96",
  "4" = "#ad2a72"
)



FC_strength_overlap.lh <- plot_cortex_overlap(sex.main.overlap.FC_strength, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
FC_strength_overlap.rh <- plot_cortex_overlap(sex.main.overlap.FC_strength, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

FC_strength_overlap <- annotate_figure(
  plot_grid(FC_strength_overlap.lh, FC_strength_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 10, face = "bold")
)
# legend for overlap
count_colors_legend <- c(
  "0–1" = "white",
  "2"   = "#fcdac0",
  "3"   = "#e87b96",
  "4"   = "#ad2a72"
)

legend_df <- data.frame(
  overlap = factor(names(count_colors_legend),
                   levels = names(count_colors_legend))
)

legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(
    values = count_colors_legend,
    guide = guide_legend(
      direction = "horizontal",
      label.position = "bottom",
      override.aes = list(
        colour = "black",   # outline boxes
        size = 1
      )
    )
  ) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 10),
    legend.key.size = unit(0.7, "cm"),
    legend.position = "bottom"
  )

# Extract the horizontal legend
overlap_legend <- get_legend(legend_plot)

overlap_FC_strength_plots <- annotate_figure(plot_grid(FC_strength_overlap, blank_space, overlap_legend, nrow = 3, rel_heights = c(1, 0.25, 0.1)), bottom = text_grob("Number of Datasets", size = 10, y = -0.4))

FC_strength_plots_final <- plot_grid(
  FC_strength_plots, overlap_FC_strength_plots, blank_space,
  nrow = 3, rel_heights = c(1, 0.277, 0.05),
  labels = c("A", "B", ""), label_size = 10,
  label_x = 0.015, label_y = c(0.99, 0.967, 1),
  hjust = 0, vjust = 1)
```

```{r FC_strength_plots_final, fig.width = 5, fig.height = 8} 
FC_strength_plots_final
#ggsave("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/sex_diff_manuscript/drafts/figures/fig1.tiff", plot = FC_strength_plots_final, width = 5, height = 8, units = "in")
```

### Regions showing significantly greater FC strength in females than males in two or more datasets.
```{r check-FC_strength-female-greater, echo=FALSE, message=FALSE, warning=FALSE}
df_list_FC_strength <- list(
  PNC  = sex.main.PNC.FC_strength[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_PNC = Anova.cov.pvalue.fdr, RESI_PNC = RESI),
  HCPD = sex.main.HCPD.FC_strength[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_HCPD = Anova.cov.pvalue.fdr, RESI_HCPD = RESI),
  NKI  = sex.main.NKI.FC_strength[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_NKI = Anova.cov.pvalue.fdr, RESI_NKI = RESI),
  HBN  = sex.main.HBN.FC_strength[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_HBN = Anova.cov.pvalue.fdr, RESI_HBN = RESI)
)

sex.main.overlap.FC_strength <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_FC_strength) %>%
  mutate(
    female_greater_count =
      (p_PNC < .05 & RESI_PNC > 0) +
      (p_HCPD < .05 & RESI_HCPD > 0) +
      (p_NKI < .05 & RESI_NKI > 0) +
      (p_HBN < .05 & RESI_HBN > 0)
  )

female_greater_FC_strength <- sex.main.overlap.FC_strength %>%
  filter(female_greater_count >= 2) %>%
  select(region, female_greater_count) %>%
  arrange(desc(female_greater_count))

 
if (nrow(female_greater_FC_strength) == 0) {
  female_greater_FC_strength <- tibble(
    region = "None",
    female_greater_count = NA_integer_
  )
}

female_greater_FC_strength %>%
  mutate(
    region = sub("^17Networks_", "", region),
    female_greater_count = replace_na(as.character(female_greater_count), "—")
  ) %>%
  kbl(
    col.names = c("Region", "No. of datasets")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  column_spec(1, width = "22em") %>%
  column_spec(2, width = "8em", bold = TRUE) %>%
  row_spec(0, bold = TRUE)
```

# 2. Greater average between-network connectivity contributes to greater FC strength in males.
```{r load BNC sex effect}
sex.main.PNC.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "BNC"))
sex.main.PNC.BNC$region <- paste0("17", sex.main.PNC.BNC$region)
sex.main.PNC.BNC <- sig.effects(sex.main.PNC.BNC, "BNC", "sex", "PNC")
resi.PNC.BNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "PNC", "resi", "BNC", "PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.PNC.BNC$region <- paste0("17", resi.PNC.BNC$region )
resi.PNC.BNC <- resi.PNC.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.PNC.BNC <- merge(sex.main.PNC.BNC, resi.PNC.BNC)

sex.main.HCPD.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "BNC"))
sex.main.HCPD.BNC <- sig.effects(sex.main.HCPD.BNC, "BNC", "sex", "HCPD")
sex.main.HCPD.BNC$region <- paste0("17", sex.main.HCPD.BNC$region)
resi.HCPD.BNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HCPD", "resi", "BNC", "HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.HCPD.BNC$region <- paste0("17", resi.HCPD.BNC$region )
resi.HCPD.BNC <- resi.HCPD.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HCPD.BNC <- merge(sex.main.HCPD.BNC, resi.HCPD.BNC)

sex.main.NKI.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "BNC"))
sex.main.NKI.BNC <- sig.effects(sex.main.NKI.BNC, "BNC", "sex", "NKI")
sex.main.NKI.BNC$region <- paste0("17", sex.main.NKI.BNC$region)
resi.NKI.BNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "NKI", "resi", "BNC", "NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.NKI.BNC$region <- paste0("17", resi.NKI.BNC$region )
resi.NKI.BNC <- resi.NKI.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.NKI.BNC <- merge(sex.main.NKI.BNC, resi.NKI.BNC)

sex.main.HBN.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "BNC"))
sex.main.HBN.BNC <- sig.effects(sex.main.HBN.BNC, "BNC", "sex", "HBN")
sex.main.HBN.BNC$region <- paste0("17", sex.main.HBN.BNC$region)
resi.HBN.BNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HBN", "resi", "BNC", "HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.HBN.BNC$region <- paste0("17", resi.HBN.BNC$region )
resi.HBN.BNC <- resi.HBN.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HBN.BNC <- merge(sex.main.HBN.BNC, resi.HBN.BNC)

sex.main.all_datasets.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "BNC"))
sex.main.all_datasets.BNC <- sig.effects(sex.main.all_datasets.BNC, "BNC", "sex", "all_datasets")
sex.main.all_datasets.BNC$region <- paste0("17", sex.main.all_datasets.BNC$region)
resi.all_datasets.BNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "resi", "BNC", "all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.all_datasets.BNC$region <- paste0("17", resi.all_datasets.BNC$region )
resi.all_datasets.BNC <- resi.all_datasets.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.all_datasets.BNC <- merge(sex.main.all_datasets.BNC, resi.all_datasets.BNC)
```

```{r make BNC plots across datasets with resi, message = FALSE, warning = FALSE, fig.width = 5, fig.height = 6}
sex.main.PNC.BNC_lh_resi <- plot_cortex(sex.main.PNC.BNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.PNC.BNC_rh_resi <- plot_cortex(sex.main.PNC.BNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 

sex.main.HCPD.BNC_lh_resi <- plot_cortex(sex.main.HCPD.BNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.HCPD.BNC_rh_resi <- plot_cortex(sex.main.HCPD.BNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 

sex.main.NKI.BNC_lh_resi <- plot_cortex(sex.main.NKI.BNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.NKI.BNC_rh_resi <- plot_cortex(sex.main.NKI.BNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 

sex.main.HBN.BNC_lh_resi <- plot_cortex(sex.main.HBN.BNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
sex.main.HBN.BNC_rh_resi <- plot_cortex(sex.main.HBN.BNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
 
sex.main.all_datasets.BNC_lh_resi <- plot_cortex(sex.main.all_datasets.BNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.BNC_rh_resi <- plot_cortex(sex.main.all_datasets.BNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200", horizontal_layout = TRUE) 

  
# legend
ylim1 = -0.26
ylim2 = 0.1
p <- ggplot() + 
  geom_brain(data = sex.main.HBN.BNC, atlas = schaefer17_200, mapping = aes(fill = RESI), show.legend = TRUE) +
  scale_fill_gradientn(colours = red_teal_white(256), values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
  theme_void() +
  theme(legend.title = element_blank(), legend.text = element_text(size = 10), legend.position = "bottom", legend.box = "horizontal",
        legend.key.height = unit(0.53, "cm"), legend.key.width = unit(1.07, "cm"), plot.margin = unit(c(0, 0.53, 0, -0.27), "cm"))

legend <- get_legend(p)
legend <- ggdraw() +
  draw_plot(legend, x = 0.23, y = 0, width = 0.54, height = 1) +
  draw_label("Male > Female", x = 0.075, y = 0.66, size = 10, hjust = 0) +
  draw_label("Female > Male", x = 0.925, y = 0.66, size = 10, hjust = 1) 

# arrange plots 
# PNC
BNC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.BNC_lh_resi, sex.main.PNC.BNC_rh_resi, ncol = 2),
  top = text_grob("PNC", size = 10, face = "bold")
)

# HCP-D
BNC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.BNC_lh_resi, sex.main.HCPD.BNC_rh_resi, ncol = 2),
  top = text_grob("HCP-D", size = 10, face = "bold")
)

# NKI
BNC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.BNC_lh_resi, sex.main.NKI.BNC_rh_resi, ncol = 2),
  top = text_grob("NKI", size = 10, face = "bold")
)

# HBN
BNC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.BNC_lh_resi, sex.main.HBN.BNC_rh_resi, ncol = 2),
  top = text_grob("HBN", size = 10, face = "bold")
)

 
# pooled dataset / all datasets
BNC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.BNC_lh_resi, sex.main.all_datasets.BNC_rh_resi, ncol = 2),
  top = text_grob("Pooled Dataset", size = 10, face = "bold")
)


# blank plot for formatting
blank_space <- ggplot() + theme_void()

BNC_plots_row1 <- plot_grid(BNC_PNC, BNC_HCPD, ncol = 2)
BNC_plots_row2 <- plot_grid(BNC_NKI, BNC_HBN, ncol = 2)
BNC_plots_row1and2 <- plot_grid(BNC_plots_row1, BNC_plots_row2, nrow = 2)
BNC_plots <- annotate_figure(
  plot_grid(blank_space, BNC_plots_row1and2, BNC_all, legend, nrow = 4, rel_heights = c(0.05, 1.2, 0.35, 0.2)),
  top = text_grob("Average Between-Network Connectivity", size = 10, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 10, y = 1)
)

```

```{r make BNC overlapping effects plot with resi}
# overlap plots
df_list_BNC <- list(
  PNC  = sex.main.PNC.BNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.BNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.BNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.BNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.BNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_BNC)
sex.main.overlap.BNC$signif_count <- rowSums(sex.main.overlap.BNC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.BNC$signif_count_factor <- factor(
  sex.main.overlap.BNC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.BNC <- sex.main.overlap.BNC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))

count_colors <- c(
  "0" = "white",
  "1" = "white",
  "2" = "#fcdac0",
  "3" = "#e87b96",
  "4" = "#ad2a72"
)



BNC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.BNC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
BNC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.BNC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

BNC_overlap <- annotate_figure(
  plot_grid(BNC_overlap.lh, BNC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 10, face = "bold")
)
# legend for overlap
count_colors_legend <- c(
  "0–1" = "white",
  "2"   = "#fcdac0",
  "3"   = "#e87b96",
  "4"   = "#ad2a72"
)

legend_df <- data.frame(
  overlap = factor(names(count_colors_legend),
                   levels = names(count_colors_legend))
)

legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(
    values = count_colors_legend,
    guide = guide_legend(
      direction = "horizontal",
      label.position = "bottom",
      override.aes = list(
        colour = "black",   # outline boxes
        size = 1
      )
    )
  ) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 10),
    legend.key.size = unit(0.7, "cm"),
    legend.position = "bottom"
  )

# Extract the horizontal legend
overlap_legend <- get_legend(legend_plot)

overlap_BNC_plots <- annotate_figure(plot_grid(BNC_overlap, blank_space, overlap_legend, nrow = 3, rel_heights = c(1, 0.25, 0.1)), bottom = text_grob("Number of Datasets", size = 10, y = -0.4))

BNC_plots_final <- plot_grid(
  BNC_plots, overlap_BNC_plots, blank_space,
  nrow = 3, rel_heights = c(1, 0.277, 0.05),
  labels = c("A", "B", ""), label_size = 10,
  label_x = 0.015, label_y = c(0.99, 0.967, 1),
  hjust = 0, vjust = 1)
```

```{r BNC_plots_final, fig.width = 5, fig.height = 8} 
BNC_plots_final
ggsave("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/sex_diff_manuscript/drafts/figures/fig2.tiff", plot = BNC_plots_final, width = 5, height = 8, units = "in")
```



### Regions showing significantly greater BNC in females than males in two or more datasets.
```{r check-BNC-female-greater, echo=FALSE, message=FALSE, warning=FALSE}
df_list_BNC <- list(
  PNC  = sex.main.PNC.BNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_PNC = Anova.cov.pvalue.fdr, RESI_PNC = RESI),
  HCPD = sex.main.HCPD.BNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_HCPD = Anova.cov.pvalue.fdr, RESI_HCPD = RESI),
  NKI  = sex.main.NKI.BNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_NKI = Anova.cov.pvalue.fdr, RESI_NKI = RESI),
  HBN  = sex.main.HBN.BNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_HBN = Anova.cov.pvalue.fdr, RESI_HBN = RESI)
)

sex.main.overlap.BNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_BNC) %>%
  mutate(
    female_greater_count =
      (p_PNC < .05 & RESI_PNC > 0) +
      (p_HCPD < .05 & RESI_HCPD > 0) +
      (p_NKI < .05 & RESI_NKI > 0) +
      (p_HBN < .05 & RESI_HBN > 0)
  )

female_greater_BNC <- sex.main.overlap.BNC %>%
  filter(female_greater_count >= 2) %>%
  select(region, female_greater_count) %>%
  arrange(desc(female_greater_count))

 
if (nrow(female_greater_BNC) == 0) {
  female_greater_BNC <- tibble(
    region = "None",
    female_greater_count = NA_integer_
  )
}

female_greater_BNC %>%
  mutate(
    region = sub("^17Networks_", "", region),
    female_greater_count = replace_na(as.character(female_greater_count), "—")
  ) %>%
  kbl(
    col.names = c("Region", "No. of datasets")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  column_spec(1, width = "22em") %>%
  column_spec(2, width = "8em", bold = TRUE) %>%
  row_spec(0, bold = TRUE)
```

# 3. Females exhibit greater average within-network connectivity in medial prefrontal, posterior cingulate, precuneus, and inferior parietal cortices
```{r load WNC sex effect}
sex.main.PNC.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "WNC"))
sex.main.PNC.WNC$region <- paste0("17", sex.main.PNC.WNC$region)
sex.main.PNC.WNC <- sig.effects(sex.main.PNC.WNC, "WNC", "sex", "PNC")
resi.PNC.WNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "PNC", "resi", "WNC", "PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.PNC.WNC$region <- paste0("17", resi.PNC.WNC$region )
resi.PNC.WNC <- resi.PNC.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.PNC.WNC <- merge(sex.main.PNC.WNC, resi.PNC.WNC)

sex.main.HCPD.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "WNC"))
sex.main.HCPD.WNC <- sig.effects(sex.main.HCPD.WNC, "WNC", "sex", "HCPD")
sex.main.HCPD.WNC$region <- paste0("17", sex.main.HCPD.WNC$region)
resi.HCPD.WNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HCPD", "resi", "WNC", "HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.HCPD.WNC$region <- paste0("17", resi.HCPD.WNC$region )
resi.HCPD.WNC <- resi.HCPD.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HCPD.WNC <- merge(sex.main.HCPD.WNC, resi.HCPD.WNC)

sex.main.NKI.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "WNC"))
sex.main.NKI.WNC <- sig.effects(sex.main.NKI.WNC, "WNC", "sex", "NKI")
sex.main.NKI.WNC$region <- paste0("17", sex.main.NKI.WNC$region)
resi.NKI.WNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "NKI", "resi", "WNC", "NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.NKI.WNC$region <- paste0("17", resi.NKI.WNC$region )
resi.NKI.WNC <- resi.NKI.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.NKI.WNC <- merge(sex.main.NKI.WNC, resi.NKI.WNC)

sex.main.HBN.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "WNC"))
sex.main.HBN.WNC <- sig.effects(sex.main.HBN.WNC, "WNC", "sex", "HBN")
sex.main.HBN.WNC$region <- paste0("17", sex.main.HBN.WNC$region)
resi.HBN.WNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HBN", "resi", "WNC", "HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.HBN.WNC$region <- paste0("17", resi.HBN.WNC$region )
resi.HBN.WNC <- resi.HBN.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HBN.WNC <- merge(sex.main.HBN.WNC, resi.HBN.WNC)

sex.main.all_datasets.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "WNC"))
sex.main.all_datasets.WNC <- sig.effects(sex.main.all_datasets.WNC, "WNC", "sex", "all_datasets")
sex.main.all_datasets.WNC$region <- paste0("17", sex.main.all_datasets.WNC$region)
resi.all_datasets.WNC <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "resi", "WNC", "all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv"))
resi.all_datasets.WNC$region <- paste0("17", resi.all_datasets.WNC$region )
resi.all_datasets.WNC <- resi.all_datasets.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.all_datasets.WNC <- merge(sex.main.all_datasets.WNC, resi.all_datasets.WNC)
```

```{r make WNC plots across datasets with resi, message = FALSE, warning = FALSE, fig.width = 5, fig.height = 6}
sex.main.PNC.WNC_lh_resi <- plot_cortex(sex.main.PNC.WNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 
sex.main.PNC.WNC_rh_resi <- plot_cortex(sex.main.PNC.WNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 

sex.main.HCPD.WNC_lh_resi <- plot_cortex(sex.main.HCPD.WNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 
sex.main.HCPD.WNC_rh_resi <- plot_cortex(sex.main.HCPD.WNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 

sex.main.NKI.WNC_lh_resi <- plot_cortex(sex.main.NKI.WNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 
sex.main.NKI.WNC_rh_resi <- plot_cortex(sex.main.NKI.WNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 

sex.main.HBN.WNC_lh_resi <- plot_cortex(sex.main.HBN.WNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 
sex.main.HBN.WNC_rh_resi <- plot_cortex(sex.main.HBN.WNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 
 
sex.main.all_datasets.WNC_lh_resi <- plot_cortex(sex.main.all_datasets.WNC, hemi = "left", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.WNC_rh_resi <- plot_cortex(sex.main.all_datasets.WNC, hemi = "right", measure = "RESI", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200", horizontal_layout = TRUE) 

  
# legend
ylim1 = -0.26
ylim2 = 0.3
p <- ggplot() + 
  geom_brain(data = sex.main.HBN.WNC, atlas = schaefer17_200, mapping = aes(fill = RESI), show.legend = TRUE) +
  scale_fill_gradientn(colours = red_teal_white(256), values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
  theme_void() +
  theme(legend.title = element_blank(), legend.text = element_text(size = 10), legend.position = "bottom", legend.box = "horizontal",
        legend.key.height = unit(0.53, "cm"), legend.key.width = unit(1.07, "cm"), plot.margin = unit(c(0, 0.53, 0, -0.27), "cm"))

legend <- get_legend(p)
legend <- ggdraw() +
  draw_plot(legend, x = 0.23, y = 0, width = 0.54, height = 1) +
  draw_label("Male > Female", x = 0.075, y = 0.66, size = 10, hjust = 0) +
  draw_label("Female > Male", x = 0.925, y = 0.66, size = 10, hjust = 1) 

# arrange plots 
# PNC
WNC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.WNC_lh_resi, sex.main.PNC.WNC_rh_resi, ncol = 2),
  top = text_grob("PNC", size = 10, face = "bold")
)

# HCP-D
WNC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.WNC_lh_resi, sex.main.HCPD.WNC_rh_resi, ncol = 2),
  top = text_grob("HCP-D", size = 10, face = "bold")
)

# NKI
WNC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.WNC_lh_resi, sex.main.NKI.WNC_rh_resi, ncol = 2),
  top = text_grob("NKI", size = 10, face = "bold")
)

# HBN
WNC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.WNC_lh_resi, sex.main.HBN.WNC_rh_resi, ncol = 2),
  top = text_grob("HBN", size = 10, face = "bold")
)

 
# pooled dataset / all datasets
WNC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.WNC_lh_resi, sex.main.all_datasets.WNC_rh_resi, ncol = 2),
  top = text_grob("Pooled Dataset", size = 10, face = "bold")
)


# blank plot for formatting
blank_space <- ggplot() + theme_void()

WNC_plots_row1 <- plot_grid(WNC_PNC, WNC_HCPD, ncol = 2)
WNC_plots_row2 <- plot_grid(WNC_NKI, WNC_HBN, ncol = 2)
WNC_plots_row1and2 <- plot_grid(WNC_plots_row1, WNC_plots_row2, nrow = 2)
WNC_plots <- annotate_figure(
  plot_grid(blank_space, WNC_plots_row1and2, WNC_all, legend, nrow = 4, rel_heights = c(0.05, 1.2, 0.35, 0.2)),
  top = text_grob("Average Within-Network Connectivity", size = 10, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 10, y = 1)
)

```

```{r make WNC overlapping effects plot with resi}
# overlap plots
df_list_WNC <- list(
  PNC  = sex.main.PNC.WNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.WNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.WNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.WNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.WNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_WNC)
sex.main.overlap.WNC$signif_count <- rowSums(sex.main.overlap.WNC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.WNC$signif_count_factor <- factor(
  sex.main.overlap.WNC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.WNC <- sex.main.overlap.WNC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))

count_colors <- c(
  "0" = "white",
  "1" = "white",
  "2" = "#fcdac0",
  "3" = "#e87b96",
  "4" = "#ad2a72"
)



WNC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.WNC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
WNC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.WNC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

WNC_overlap <- annotate_figure(
  plot_grid(WNC_overlap.lh, WNC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 10, face = "bold")
)
# legend for overlap
count_colors_legend <- c(
  "0–1" = "white",
  "2"   = "#fcdac0",
  "3"   = "#e87b96",
  "4"   = "#ad2a72"
)

legend_df <- data.frame(
  overlap = factor(names(count_colors_legend),
                   levels = names(count_colors_legend))
)

legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(
    values = count_colors_legend,
    guide = guide_legend(
      direction = "horizontal",
      label.position = "bottom",
      override.aes = list(
        colour = "black",   # outline boxes
        size = 1
      )
    )
  ) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 10),
    legend.key.size = unit(0.7, "cm"),
    legend.position = "bottom"
  )

# Extract the horizontal legend
overlap_legend <- get_legend(legend_plot)

overlap_WNC_plots <- annotate_figure(plot_grid(WNC_overlap, blank_space, overlap_legend, nrow = 3, rel_heights = c(1, 0.25, 0.1)), bottom = text_grob("Number of Datasets", size = 10, y = -0.4))

WNC_plots_final <- plot_grid(
  WNC_plots, overlap_WNC_plots, blank_space,
  nrow = 3, rel_heights = c(1, 0.277, 0.05),
  labels = c("A", "B", ""), label_size = 10,
  label_x = 0.015, label_y = c(0.99, 0.967, 1),
  hjust = 0, vjust = 1)
```

```{r WNC_plots_final, fig.width = 5, fig.height = 8} 
WNC_plots_final
ggsave("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/sex_diff_manuscript/drafts/figures/fig3.tiff", plot = WNC_plots_final, width = 5, height = 8, units = "in")
```


### Regions showing significantly greater WNC in males than females in two or more datasets.
```{r check-WNC-male-greater, echo=FALSE, message=FALSE, warning=FALSE}
df_list_WNC <- list(
  PNC  = sex.main.PNC.WNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_PNC = Anova.cov.pvalue.fdr, RESI_PNC = RESI),
  HCPD = sex.main.HCPD.WNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_HCPD = Anova.cov.pvalue.fdr, RESI_HCPD = RESI),
  NKI  = sex.main.NKI.WNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_NKI = Anova.cov.pvalue.fdr, RESI_NKI = RESI),
  HBN  = sex.main.HBN.WNC[, c("region", "Anova.cov.pvalue.fdr", "RESI")] |> rename(p_HBN = Anova.cov.pvalue.fdr, RESI_HBN = RESI)
)

sex.main.overlap.WNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_WNC) %>%
  mutate(
    male_greater_count =
      (p_PNC < .05 & RESI_PNC < 0) +
      (p_HCPD < .05 & RESI_HCPD < 0) +
      (p_NKI < .05 & RESI_NKI < 0) +
      (p_HBN < .05 & RESI_HBN < 0)
  )

male_greater_WNC <- sex.main.overlap.WNC %>%
  filter(male_greater_count >= 2) %>%
  select(region, male_greater_count) %>%
  arrange(desc(male_greater_count))

 
male_greater_WNC %>%
  mutate(region = sub("^17Networks_", "", region)) %>%
  kbl(
    col.names = c("Region", "No. of datasets")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  column_spec(1, width = "22em") %>%
  column_spec(2, width = "8em", bold = TRUE) %>%
  row_spec(0, bold = TRUE) 
```

# 4. Neurosynth-based contextualization of replicable sex differences in between- and within-network connectivity

Which Neurosynth terms show significant functional activation (z \> 1.64) within the parcels where females have higher WNC? What about where males have higher BNC?

```{r load neurosynth}
# code adapted from Val Sydnor's https://github.com/PennLINC/thalamocortical_development/blob/main/results/developmental_effects/thalamocortical_connectivity_development.Rmd
#Neurosynth z-score maps generated by nimare. Nimare uses multilevel kernel density analysis- Chi-square analysis + FDR-correction to use the same procedure as Neurosynth
neurosynth.terms <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "input", "neurosynth_annotations", "schaefer200", "schaefer200x17_neurosynth_125terms.csv")) %>% select(-regionID) %>% rename(region = label)
neurosynth.termlist <- names(neurosynth.terms)[-1] #list of terms  
```

We examined the 10 most negatively correlated Neurosynth terms with the BNC sex difference map, focusing on negative correlations because they indicate cognitive domains whose spatial patterns overlap with regions showing greater BNC in males relative to females. In contrast, we examined the ten most positively correlated Neurosynth terms with the WNC sex difference map, focusing on positively correlations because they indicate cognitive domains whose spatial patterns overlap with regions showing greater WNC in females relative to males.

```{r overlapping effects neurosynth decoding of sex differences, fig.height = 7, fig.width = 7}
# identify overlapping significant effects across datasets (2 or more datasets), and get avg RESI for each of those parcels
BNC_sexeffect_overlap <- identify_sexeffect_overlap("BNC") %>% mutate(significant_status = ifelse(signif_2plus == 1, "Sig", "Nonsig"))
WNC_sexeffect_overlap <- identify_sexeffect_overlap("WNC") %>% mutate(significant_status = ifelse(signif_2plus == 1, "Sig", "Nonsig"))
 
# fdr correction of neurosynth terms correlations with BNC and WNC sex effect maps
BNC_neurosynth <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "spin_test", "neurosynth", "BNC_neurosynth_spin_test_results_overlap.csv"))
BNC_neurosynth$pvalue.fdr <- p.adjust(BNC_neurosynth$p_spin, method = c("fdr")) 
BNC_neurosynth_fdr <- BNC_neurosynth %>% filter(pvalue.fdr < 0.05)  
BNC_neurosynth_top10 <- rbind(slice_min(BNC_neurosynth_fdr, order_by = term.correlation, n = 10)) # 10 most negatively correlated neurosynth terms with the sex diff map. Looking at negative correlations because they reflect cognitive terms that spatially align with regions showing higher BNC in males (male > female).
BNC_neurosynth_top10$term <- tools::toTitleCase(gsub("_", " ", BNC_neurosynth_top10$term))

WNC_neurosynth <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "spin_test", "neurosynth", "WNC_neurosynth_spin_test_results_overlap.csv"))
WNC_neurosynth$pvalue.fdr <- p.adjust(WNC_neurosynth$p_spin, method = c("fdr")) 
WNC_neurosynth_fdr <- WNC_neurosynth %>% filter(pvalue.fdr < 0.05)  
WNC_neurosynth_top10 <- rbind(slice_max(WNC_neurosynth_fdr, order_by = term.correlation, n = 10)) # 10 most positively correlated neurosynth terms with the sex diff map. Looking at positive correlations because they reflect cognitive terms that spatially align with regions showing higher WNC in females (female > male).
WNC_neurosynth_top10$term <- tools::toTitleCase(gsub("_", " ", WNC_neurosynth_top10$term))
WNC_neurosynth_top10$term <- gsub("Autobiographical Memory", "Autobio. Memory", WNC_neurosynth_top10$term)

 
```

```{r overlap RESI plots}
# plot avg RESI 
BNC_overlap_RESI_plot_lh <- plot_cortex(BNC_sexeffect_overlap, hemi = "left", measure = "mean_resi_sig2", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
BNC_overlap_RESI_plot_rh <- plot_cortex(BNC_sexeffect_overlap, hemi = "right", measure = "mean_resi_sig2", ylim1 = -0.26, ylim2 = 0.1, atlas = "schaefer17_200") 
 
WNC_overlap_RESI_plot_lh <- plot_cortex(WNC_sexeffect_overlap, hemi = "left", measure = "mean_resi_sig2", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 
WNC_overlap_RESI_plot_rh <- plot_cortex(WNC_sexeffect_overlap, hemi = "right", measure = "mean_resi_sig2", ylim1 = -0.26, ylim2 = 0.3, atlas = "schaefer17_200") 
  
# legend for BNC overlap
ylim1 = -0.26
ylim2 = 0.1
p_BNC <- ggplot() + 
    geom_brain(data = BNC_sexeffect_overlap, atlas = schaefer17_200, 
               mapping=aes(fill=mean_resi_sig2), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 10),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(0.4, 'cm'),
        legend.key.width = unit(0.9, 'cm'),
        plot.margin = unit(c(0, 0.5, 0, -0.5), "cm"))
  
legend_BNC_overlap <- get_legend(p_BNC)

# legend for WNC overlap
ylim1 = -0.26
ylim2 = 0.3
p_WNC <- ggplot() + 
    geom_brain(data = WNC_sexeffect_overlap, atlas = schaefer17_200, 
               mapping=aes(fill=mean_resi_sig2), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 10),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(0.4, 'cm'),
        legend.key.width = unit(0.9, 'cm'),
        plot.margin = unit(c(0, 0.5, 0, -0.5), "cm"))
  
legend_WNC_overlap <- get_legend(p_WNC)


# arrange plots 
BNC_overlap_RESI_plot <- annotate_figure(
  plot_grid(
    blank_space,
    annotate_figure(plot_grid(BNC_overlap_RESI_plot_lh, BNC_overlap_RESI_plot_rh, ncol = 2)),
    blank_space,
    legend_BNC_overlap,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 2.2, 0.3, 0.1, 0.05)
  ),
  top = text_grob("Average Between-Network Connectivity", size = 10, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 10, y = 0.15)
)


 
WNC_overlap_RESI_plot <- annotate_figure(
  plot_grid(
    blank_space,
    annotate_figure(plot_grid(WNC_overlap_RESI_plot_lh, WNC_overlap_RESI_plot_rh, ncol = 2)),
    blank_space,
    legend_WNC_overlap,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 2.2, 0.3, 0.1, 0.05)
  ),
  top = text_grob("Average Within-Network Connectivity", size = 10, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 10, y = 0.15)
)
 
```

```{r overlap neurosynth plots}
# BNC: negative correlations
BNC_neurosynth_plot <- ggplot(
  BNC_neurosynth_top10,
  aes(x = term.correlation, y = reorder(term, abs(term.correlation)))
) +
  geom_segment(
    aes(x = 0, xend = term.correlation, yend = reorder(term, abs(term.correlation))),
    color = "gray80", linewidth = 0.5
  ) +
  geom_point(aes(color = term.correlation), size = 5) +
  scale_color_gradient(low = "#ad2a72", high = "#fcdac0") +
  scale_x_continuous(limits = c(-0.6, 0), breaks = seq(-0.6, 0, by = 0.2), expand = c(0, 0)) +
  scale_y_discrete(position = "right") +
  labs(x = "Spatial Correlation") +
  theme_classic() +
  coord_cartesian(clip = "off") +
  theme(
    panel.grid.major.y = element_blank(), panel.grid.minor = element_blank(),
    legend.position = "none", axis.title.y = element_blank(),
    axis.title.x = element_text(size = 10, color = "black"),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black"),
    plot.margin = unit(c(0, 0.5, 0, 0), "cm")
  )

# WNC: positive correlations
WNC_neurosynth_plot <- ggplot(
  WNC_neurosynth_top10,
  aes(x = term.correlation, y = reorder(term, term.correlation))
) +
  geom_segment(
    aes(x = 0, xend = term.correlation, yend = reorder(term, term.correlation)),
    color = "gray80", linewidth = 0.5
  ) +
  geom_point(aes(color = term.correlation), size = 5) +
  scale_color_gradient(low = "#fcdac0", high = "#ad2a72") +
  scale_x_continuous(limits = c(0, 0.6), breaks = seq(0, 0.6, by = 0.2), expand = c(0, 0)) +
  scale_y_discrete(position = "left") +
  labs(x = "Spatial Correlation") +
  theme_classic() +
  coord_cartesian(clip = "off") +
  theme(
    panel.grid.major.y = element_blank(), panel.grid.minor = element_blank(),
    legend.position = "none", axis.title.y = element_blank(),
    axis.title.x = element_text(size = 10, color = "black"),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black"),
    plot.margin = unit(c(0, 0, 0, 0.5), "cm")
  )
```



```{r overlap neurosynth figure, fig.width = 6.5, fig.height = 6}
neurosynth_plots_row1 <- plot_grid(BNC_overlap_RESI_plot, blank_space, WNC_overlap_RESI_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
neurosynth_plots_row1 <- ggdraw(neurosynth_plots_row1) + 
  draw_label("A", x = -0.02, y = 0.981, size = 10, fontface = "bold", hjust = 0, vjust = 1) +
  draw_label("B", x = 0.51, y = 0.981, size = 10, fontface = "bold", hjust = 0, vjust = 1)

neurosynth_plots_row2 <- plot_grid(blank_space, blank_space, ncol = 2)

BNC_neurosynth_panel <- plot_grid(BNC_neurosynth_plot, blank_space, ncol = 2, rel_widths = c(1, 0.1))
WNC_neurosynth_panel <- plot_grid(blank_space, WNC_neurosynth_plot, ncol = 2, rel_widths = c(0.03, 1))
neurosynth_plots_row3 <- plot_grid(BNC_neurosynth_panel, WNC_neurosynth_panel, ncol = 2)
neurosynth_plots_row3 <- annotate_figure(neurosynth_plots_row3, left = text_grob("Neurosynth Term", size = 10, rot = 90, x = -0.35, y = 0.55))
neurosynth_plots_row3 <- ggdraw(neurosynth_plots_row3) + 
  draw_label("C", x = -0.02, y = 0.968, size = 10, fontface = "bold", hjust = 0, vjust = 1) + 
  draw_label("D", x = 0.51, y = 0.968, size = 10, fontface = "bold", hjust = 0, vjust = 1)

neurosynth_plots <- plot_grid(blank_space, neurosynth_plots_row1, neurosynth_plots_row2, neurosynth_plots_row3, nrow = 4, rel_heights = c(0.05, 1, 0.1, 1))

neurosynth_plots_final <- plot_grid(blank_space, neurosynth_plots, blank_space, ncol = 3, rel_widths = c(0.07, 1, 0.07))
neurosynth_plots_final

#ggsave("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/sex_diff_manuscript/drafts/figures/fig4.tiff", plot = neurosynth_plots_final, width = 6.5, height = 6, units = "in")
```

 
# 5. Sex differences in network-level connectivity

```{r load networkpair sex for 17 networks}
num_networks = 17
sex.main.PNC.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "PNC", "networkpair", num_networks))
sex.main.HCPD.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HCPD", "networkpair", num_networks))
sex.main.NKI.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "NKI", "networkpair", num_networks))
sex.main.HBN.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HBN", "networkpair", num_networks))
sex.main.all_datasets.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "all_datasets", "networkpair", num_networks))


# make two new columns identifying network 1 and network 2
sex.main.PNC.networkpair.17<- sex.main.PNC.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HCPD.networkpair.17<- sex.main.HCPD.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.NKI.networkpair.17<- sex.main.NKI.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HBN.networkpair.17<- sex.main.HBN.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.all_datasets.networkpair.17<- sex.main.all_datasets.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))

# fdr correction on non-duplicated pairs only and sorts pairs
sex.main.PNC.networkpair.17<- prep_networkpair_df(sex.main.PNC.networkpair.17, "networkpair", "sex", "PNC")
sex.main.HCPD.networkpair.17<- prep_networkpair_df(sex.main.HCPD.networkpair.17,  "networkpair", "sex", "HCPD")
sex.main.NKI.networkpair.17<- prep_networkpair_df(sex.main.NKI.networkpair.17,  "networkpair", "sex", "NKI")
sex.main.HBN.networkpair.17<- prep_networkpair_df(sex.main.HBN.networkpair.17,  "networkpair", "sex", "HBN")
sex.main.all_datasets.networkpair.17<- prep_networkpair_df(sex.main.all_datasets.networkpair.17,  "networkpair", "sex", "All datasets")

resi.PNC.networkpair <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "PNC", "resi", "networkpair", "PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")) %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.HCPD.networkpair <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HCPD", "resi", "networkpair", "HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")) %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.NKI.networkpair <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "NKI", "resi", "networkpair", "NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")) %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.HBN.networkpair <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HBN", "resi", "networkpair", "HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")) %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.all_datasets.networkpair <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "resi", "networkpair", "all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")) %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)

sex.main.PNC.networkpair.17 <- merge(sex.main.PNC.networkpair.17, resi.PNC.networkpair)
sex.main.NKI.networkpair.17 <- merge(sex.main.NKI.networkpair.17, resi.NKI.networkpair)
sex.main.HCPD.networkpair.17 <- merge(sex.main.HCPD.networkpair.17, resi.HCPD.networkpair)
sex.main.HBN.networkpair.17 <- merge(sex.main.HBN.networkpair.17, resi.HBN.networkpair)
sex.main.all_datasets.networkpair.17 <- merge(sex.main.all_datasets.networkpair.17, resi.all_datasets.networkpair)
```
 
 
```{r plot networkpair sex for 17 networks with resi, fig.width = 6.5, fig.height = 7.5}
# plot each dataset
networkpair_resi_PNC <- annotate_figure(
  make_networkpair17_plot(sex.main.PNC.networkpair.17, dataset = "PNC", ylim1 = -0.3, ylim2 = 0.3, fontsize = 7, fontsize_label = 2.4, measure = "RESI"))
 
networkpair_resi_HCPD <- annotate_figure(
  make_networkpair17_plot(sex.main.HCPD.networkpair.17, dataset = "HCP-D", ylim1 = -0.3, ylim2 = 0.3, fontsize = 7, fontsize_label = 2.4, measure = "RESI"))

networkpair_resi_NKI <- annotate_figure(
  make_networkpair17_plot(sex.main.NKI.networkpair.17, dataset = "NKI", ylim1 = -0.3, ylim2 = 0.3, fontsize = 7, fontsize_label = 2.4, measure = "RESI"))

networkpair_resi_HBN <- annotate_figure(
  make_networkpair17_plot(sex.main.HBN.networkpair.17, dataset = "HBN", ylim1 = -0.3, ylim2 = 0.3, fontsize = 7, fontsize_label = 2.4, measure = "RESI"))

networkpair_resi_all_datasets_plot_tmp <- annotate_figure(
  make_networkpair17_plot(sex.main.all_datasets.networkpair.17, dataset = "Pooled Dataset", ylim1 = -0.3, ylim2 = 0.3, fontsize = 7, fontsize_label = 2.4, measure = "RESI"))

networkpair_row1 <- plot_grid(blank_space, networkpair_resi_PNC, blank_space, networkpair_resi_HCPD, ncol = 4, 
                              rel_widths = c(0.03, 1, 0.1, 1))
networkpair_row2 <- plot_grid(blank_space, networkpair_resi_NKI, blank_space, networkpair_resi_HBN, ncol = 4, 
                              rel_widths = c(0.03, 1, 0.1, 1))
networkpair_datasets_plot <- plot_grid(networkpair_row1, networkpair_row2, nrow = 2)

# legend
ylim1 = -0.3
ylim2 = 0.3
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.BNC, atlas = schaefer17_200, 
               mapping=aes(fill=RESI), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 10),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(0.4, 'cm'),
        legend.key.width = unit(0.9, 'cm'),
        plot.margin = unit(c(0, 0.5, 0, 0.5), "cm"))
  
legend <- get_legend(p)
```

```{r plot networkpair overlap with resi}

# overlap of datasets:
df_list_networkpair <- list(
  PNC  = sex.main.PNC.networkpair.17[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.networkpair.17[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.networkpair.17[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.networkpair.17[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.networkpair <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_networkpair)

sex.main.overlap.networkpair <- sex.main.overlap.networkpair %>%
  mutate(
    signif_count = rowSums(across(starts_with("p_")) < 0.05, na.rm = TRUE),
    signif_count_factor = factor(
      signif_count,
      levels = 0:4,
      labels = c("0", "1", "2", "3", "4")
    ),
    signif_greater_than_one = ifelse(signif_count > 1, "1", "0")
  )

sex.main.overlap.networkpair_plot_df <- sex.main.overlap.networkpair %>%
  mutate(
    network1 = str_extract(region, "^[[:alpha:]]+"),
    network2 = str_extract(region, "(?<=_).*")
  )


# overlap legend
legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(values = count_colors_legend,
                    guide = guide_legend(direction = "horizontal",
                                         label.position = "bottom",
                                         override.aes = list(colour = "black", size = 1))) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 10),
    legend.key.size = unit(0.6, "cm"),
    legend.position = "bottom"
  )

overlap_legend_tmp <- get_legend(legend_plot)
networkpair_resi_overlap_plot_tmp <-  plot_networkpair_overlap(sex.main.overlap.networkpair_plot_df)
 
```


```{r plot networkpair with resi, fig.width = 6.2, fig.height = 8}
# pnc, nki, hcpd, hbn
networkpair_resi_row1 <- networkpair_datasets_plot

# all datasets + legend
resi_legend <- annotate_figure(plot_grid(
  NULL, legend,
  ncol = 2,
  rel_widths = c(0.2, 0.75)), bottom = text_grob("Sex Effect (RESI)", size = 10, y = -0.3, x = 0.6))
networkpair_resi_all_datasets_plot <- plot_grid(networkpair_resi_all_datasets_plot_tmp, blank_space, resi_legend, blank_space, 
                                                nrow = 4, rel_heights = c(1, 0.05, 0.1,  0.05))
# overlap + legend
overlap_legend <- annotate_figure(plot_grid(
  NULL, overlap_legend_tmp,
  ncol = 2,
  rel_widths = c(0.2, 0.75)), bottom = text_grob("Number of Datasets", size = 10, y = -0.3, x = 0.6))
networkpair_overlap_plot <- plot_grid(networkpair_resi_overlap_plot_tmp, blank_space, overlap_legend, blank_space, 
                                      nrow = 4, rel_heights = c(1, 0.05, 0.1,  0.05))

 

networkpair_resi_row2 <- plot_grid(blank_space, networkpair_resi_all_datasets_plot, blank_space, networkpair_overlap_plot, ncol = 4, 
                              rel_widths = c(0.03, 1, 0.1, 1))
 
networkpair_plot_final <- plot_grid(networkpair_resi_row1, networkpair_resi_row2, nrow = 2, rel_heights = c(1.2, 0.72))

networkpair_plot_final <- ggdraw(networkpair_plot_final) +
  draw_label("A", x = 0.03, y = 0.989, fontface = "bold", size = 10) +
  draw_label("B", x = 0.53, y = 0.364, fontface = "bold", size = 10)

networkpair_plot_final
#ggsave("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/sex_diff_manuscript/drafts/figures/fig5.tiff", plot = networkpair_plot_final, width = 6.2, height = 8, units = "in")
```
 

```{r table of largest network pair effects}
networkpair_list <- list(
  PNC = sex.main.PNC.networkpair.17, NKI = sex.main.NKI.networkpair.17,
  `HCP-D` = sex.main.HCPD.networkpair.17, HBN = sex.main.HBN.networkpair.17,
  `Pooled Dataset` = sex.main.all_datasets.networkpair.17
)

pretty_network <- c(
  defaultA = "default mode A", defaultB = "default mode B", defaultC = "default mode C",
  frontoparietalControlA = "control A", frontoparietalControlB = "control B", frontoparietalControlC = "control C",
  dorsalAttentionA = "dorsal attention A", dorsalAttentionB = "dorsal attention B",
  salienceVentralAttentionA = "salience/ventral attention A", salienceVentralAttentionB = "salience/ventral attention B",
  limbicOrbitofrontal = "limbic orbitofrontal", limbicTemporopolar = "limbic temporal pole",
  somatomotorA = "somatomotor A", somatomotorB = "somatomotor B",
  visualCentral = "visual central", visualPeripheral = "visual peripheral", temporalParietal = "temporal parietal"
)

pretty_pair <- function(region) {
  nets <- strsplit(region, "_")[[1]]
  nets <- ifelse(nets %in% names(pretty_network), unname(pretty_network[nets]), nets)
  if (nets[1] == nets[2]) paste(nets[1], "within") else paste(nets[1], "with", nets[2])
}

fmt <- function(region, resi) sprintf("%s (%.2f)", pretty_pair(region), resi)

summarise_dataset <- function(df, dataset_name) {
  sig <- df %>% filter(significant_status == "Sig")
  female <- sig %>% filter(RESI > 0) %>% arrange(desc(RESI)) %>% mutate(rank = row_number())
  male <- sig %>% filter(RESI < 0) %>% arrange(RESI)

  female_cell <- fmt(female$region[1], female$RESI[1])
  dmnA <- female %>% filter(region == "defaultA_defaultA")

  if (female$region[1] != "defaultA_defaultA" && nrow(dmnA) == 1)
    female_cell <- paste0(female_cell, "; ", pretty_pair(dmnA$region), sprintf(" (%.2f; rank %d)", dmnA$RESI, dmnA$rank))

  tibble(Dataset = dataset_name, `Female > Male` = female_cell, `Male > Female` = fmt(male$region[1], male$RESI[1]))
}

networkpair_summary <- imap_dfr(networkpair_list, summarise_dataset)

networkpair_summary %>%
  kbl(caption = "Largest significant sex effects (RESI) on network-pair connectivity",
      col.names = c("Dataset", "Female > Male", "Male > Female"), align = c("l", "l", "l"), booktabs = TRUE, escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE, position = "center", font_size = 20) %>%
  column_spec(1, bold = TRUE, width = "8em") %>%
  column_spec(2, width = "28em") %>%
  column_spec(3, width = "28em") %>%
  row_spec(0, bold = TRUE)

```
 
 
```{r dmnA male partner network effects}

partners <- c("dorsalAttentionA", "dorsalAttentionB",
              "salienceVentralAttentionA", "salienceVentralAttentionB",
              "visualCentral", "visualPeripheral", "frontoparietalControlA")

dmnA_partner_table <- imap_dfr(networkpair_list, function(df, dataset_name) {
  df %>%
    mutate(net1 = sub("_.*", "", region), net2 = sub(".*_", "", region)) %>%
    filter((net1 == "defaultA" & net2 %in% partners) | (net2 == "defaultA" & net1 %in% partners)) %>%
    transmute(
      Dataset = dataset_name,
      Partner = ifelse(net1 == "defaultA", net2, net1),
      cell = ifelse(significant_status == "Sig", sprintf("%.2f", RESI), "n.s.")
    )
}) %>%
  mutate(Partner = factor(Partner, levels = partners, labels = unname(pretty_network[partners]))) %>%
  arrange(Partner) %>%
  pivot_wider(names_from = Dataset, values_from = cell)

dmnA_partner_table %>%
  kbl(caption = "Sex effects (RESI) on connectivity between default mode A and attention, visual, and control A networks (negative = male > female; n.s. = not significant)",
      align = c("l", rep("c", length(networkpair_list))), booktabs = TRUE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE, position = "center", font_size = 20) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(0, bold = TRUE)
```
 
 
# 6. Sex differences in edge-level connectivity vary with hierarchical span of functional connections
```{r load edge sex main effect}
# edge gam output
sex.main.PNC.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "edge"))
sex.main.HCPD.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "edge"))
sex.main.NKI.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "edge"))
sex.main.HBN.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "edge"))
sex.main.all_datasets.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "edge"))

# resi
resi.PNC.edge <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "PNC", "resi", "edge", "PNC_t2S_sex_maineffects_schaefer200x17.csv"))
resi.HCPD.edge <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HCPD", "resi", "edge", "HCPD_t2S_sex_maineffects_schaefer200x17.csv"))
resi.NKI.edge <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "NKI", "resi", "edge", "NKI_t2S_sex_maineffects_schaefer200x17.csv"))
resi.HBN.edge <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HBN", "resi", "edge", "HBN_t2S_sex_maineffects_schaefer200x17.csv"))
resi.all_datasets.edge <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "resi", "edge", "all_datasets_t2S_sex_maineffects_schaefer200x17.csv"))

# merge resi
sex.main.PNC.edge <- merge(sex.main.PNC.edge, resi.PNC.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.HCPD.edge <- merge(sex.main.HCPD.edge, resi.HCPD.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.NKI.edge <- merge(sex.main.NKI.edge, resi.NKI.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.HBN.edge <- merge(sex.main.HBN.edge, resi.HBN.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.all_datasets.edge <- merge(sex.main.all_datasets.edge, resi.all_datasets.edge, by = "region", all.x = TRUE, sort = FALSE)

# load vector of differences in S-A rank between the 2 regions connecting each edge
SA.diff <- read.csv(file.path(root, "atlases", "edge", "SA.diff_schaefer200x17.csv"))

# make df for plotting (and do FDR correction)
double.PNC <- make_double_df(sex.main.PNC.edge, "edge", "sex", "PNC")  
double.HCPD <- make_double_df(sex.main.HCPD.edge, "edge", "sex", "HCPD")  
double.NKI <- make_double_df(sex.main.NKI.edge, "edge", "sex", "NKI")  
double.HBN <- make_double_df(sex.main.HBN.edge, "edge", "sex", "HBN")  
double.all_datasets <- make_double_df(sex.main.all_datasets.edge, "edge", "sex", "All datasets")  


# load spin test results
PNC_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "PNC"))
HCPD_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "HCPD"))
NKI_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "NKI"))
HBN_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "HBN"))
all_datasets_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "all_datasets"))

```

We modeled the sex-effect map (t-values) across edges using tensor product smooth:

$$edge.sex.effect \sim te(SArank_{parcel1}, SArank_{parcel2})$$

We assessed significance with a spin test that preserves spatial autocorrelation by rotating the S-A axis and recomputing model fit statistics (R2). The spin test evaluates whether the 2D tensor smooth linking sex effects to S–A axis ranks is stronger than expected given spatial autocorrelation.

We found that sex differences in edge-level connectivity are systematically organized along the cortical hierarchy. We observed stronger connectivity between regions connecting high- to low-ranking

```{r plot edge sex, fig.height = 14, fig.width = 20}

# plot surfaces
PNC_surf_plot <- make_surface_plot(double.PNC, dataset = "PNC", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
HCPD_surf_plot <-  make_surface_plot(double.HCPD, dataset = "HCP-D", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
NKI_surf_plot <-  make_surface_plot(double.NKI, dataset = "NKI", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
HBN_surf_plot <-  make_surface_plot(double.HBN, dataset = "HBN", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
row1 <- plot_grid(PNC_surf_plot, blank_space, HCPD_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
row2 <- plot_grid(NKI_surf_plot, blank_space, HBN_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
combined_surf_plots <- plot_grid(row1, blank_space, row2, ncol = 1, nrow = 3, rel_heights = c(1, 0.1, 1))
combined_surf_plots <- annotate_figure(combined_surf_plots, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))

all_datasets_surf_plot <-  make_surface_plot(double.all_datasets, dataset = "All Datasets", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = bquote(italic(p[spin]) == .(format(round(all_datasets_edges_spin$p_values$R2, 4), scientific = FALSE))))  
all_datasets_surf_plot <- annotate_figure(all_datasets_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))
# make legend
ylim1 = -3
ylim2 = 3
g2 <- gam(GAM.cov.tvalue ~ te(parcel2_SA,parcel1_SA,k=3), data = double.PNC)
  
surface.plot.fig <- gg_tensor(g2) + theme_classic() +
    theme(
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.line = element_line(color = "black"),
      axis.text=element_text(size=24, color = "black")) + 
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") +     geom_vline(xintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    geom_hline(yintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    theme(legend.position='bottom',
          legend.key.height = unit(1, 'cm'),
          legend.key.width = unit(3, 'cm'),
          legend.title = element_blank(),
          legend.text = element_text(size=24),
          strip.background = element_blank(),
          plot.margin = margin(0, 0, 0, 0, "cm"),
          plot.title = element_text(size=24, hjust=0.5))  
  
legend <- get_legend(surface.plot.fig)
blank_space <- ggplot() + theme_void()

# combine plots
combined_surf_plots <- plot_grid(combined_surf_plots, blank_space, all_datasets_surf_plot, ncol = 3, rel_widths = (c(1, 0.05, 1)))

final_surf_plots <- plot_grid(blank_space, combined_surf_plots, legend, nrow = 3, rel_heights = c(0.05, 1, 0.2))
annotate_figure(final_surf_plots, 
                bottom = text_grob("Sex Effect (t-value)", size = 20, x = 0.5, y = 2))



```

```{r plot edge sex effect with resi, fig.height = 14, fig.width = 20}
# plot surfaces
PNC_surf_plot <- make_surface_plot(double.PNC, dataset = "PNC", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
HCPD_surf_plot <-  make_surface_plot(double.HCPD, dataset = "HCP-D", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
NKI_surf_plot <-  make_surface_plot(double.NKI, dataset = "NKI", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
HBN_surf_plot <-  make_surface_plot(double.HBN, dataset = "HBN", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
row1 <- plot_grid(PNC_surf_plot, blank_space, HCPD_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
row2 <- plot_grid(NKI_surf_plot, blank_space, HBN_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
combined_surf_plots <- plot_grid(row1, blank_space, row2, ncol = 1, nrow = 3, rel_heights = c(1, 0.1, 1))
combined_surf_plots <- annotate_figure(combined_surf_plots, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))

all_datasets_surf_plot <-  make_surface_plot(double.all_datasets, dataset = "All Datasets", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = bquote(italic(p[spin]) == .(format(round(all_datasets_edges_spin$p_values$R2, 4), scientific = FALSE))))  
all_datasets_surf_plot <- annotate_figure(all_datasets_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))
# make legend
ylim1 = -0.1
ylim2 = 0.1
g2 <- gam(RESI ~ te(parcel2_SA,parcel1_SA,k=3), data = double.PNC)
  
surface.plot.fig <- gg_tensor(g2) + theme_classic() +
    theme(
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.line = element_line(color = "black"),
      axis.text=element_text(size=24, color = "black")) + 
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") +     
  geom_vline(xintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    geom_hline(yintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    theme(legend.position='bottom',
          legend.key.height = unit(1, 'cm'),
          legend.key.width = unit(3, 'cm'),
          legend.title = element_blank(),
          legend.text = element_text(size=24),
          strip.background = element_blank(),
          plot.margin = margin(0, 0, 0, 0, "cm"),
          plot.title = element_text(size=24, hjust=0.5))  
  
legend <- get_legend(surface.plot.fig)


# combine plots
combined_surf_plots <- plot_grid(combined_surf_plots, blank_space, all_datasets_surf_plot, ncol = 3, rel_widths = (c(1, 0.05, 1)))

final_surf_plots <- plot_grid(blank_space, combined_surf_plots, legend, nrow = 3, rel_heights = c(0.05, 1, 0.2))
annotate_figure(final_surf_plots, 
                bottom = text_grob("Sex Effect (RESI)", size = 20, x = 0.5, y = 2))


#ggsave(paste0("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/Conferences/SOBP2026/", "fig3_edge.png"), annotate_figure(final_surf_plots, 
               # bottom = text_grob("Sex Effect (RESI)", size = 20, x = 0.5, y = 2)), height = 14, width = 20, units = "in", bg = "white")
 
```

## edge plot colored by RESI of edges surviving FDR correction only

```{r plot edge fdr sig sex effect with resi, fig.height = 14, fig.width = 20}
# plot surfaces
PNC_sigonly_surf_plot <- make_surface_plot(double.PNC, dataset = "PNC", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
HCPD_sigonly_surf_plot <-  make_surface_plot(double.HCPD, dataset = "HCP-D", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
NKI_sigonly_surf_plot <-  make_surface_plot(double.NKI, dataset = "NKI", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
HBN_sigonly_surf_plot <-  make_surface_plot(double.HBN, dataset = "HBN", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
row1 <- plot_grid(PNC_sigonly_surf_plot, blank_space, HCPD_sigonly_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
row2 <- plot_grid(NKI_sigonly_surf_plot, blank_space, HBN_sigonly_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
combined_sigonly_surf_plots <- plot_grid(row1, blank_space, row2, ncol = 1, nrow = 3, rel_heights = c(1, 0.1, 1))
combined_sigonly_surf_plots <- annotate_figure(combined_sigonly_surf_plots, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))

all_datasets_sigonly_surf_plot <-  make_surface_plot(double.all_datasets, dataset = "All Datasets", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = bquote(italic(p[spin]) == .(format(round(all_datasets_edges_spin$p_values$R2, 4), scientific = FALSE))), significant_only = TRUE)  
all_datasets_sigonly_surf_plot <- annotate_figure(all_datasets_sigonly_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))
# make legend
ylim1 = -0.1
ylim2 = 0.1
g2 <- gam(RESI ~ te(parcel2_SA,parcel1_SA,k=3), data = double.PNC)
  
surface.plot.fig <- gg_tensor(g2) + theme_classic() +
    theme(
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.line = element_line(color = "black"),
      axis.text=element_text(size=24, color = "black")) + 
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") +     
  geom_vline(xintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    geom_hline(yintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    theme(legend.position='bottom',
          legend.key.height = unit(1, 'cm'),
          legend.key.width = unit(3, 'cm'),
          legend.title = element_blank(),
          legend.text = element_text(size=24),
          strip.background = element_blank(),
          plot.margin = margin(0, 0, 0, 0, "cm"),
          plot.title = element_text(size=24, hjust=0.5))  
  
legend <- get_legend(surface.plot.fig)


# combine plots
combined_sigonly_surf_plots <- plot_grid(combined_sigonly_surf_plots, blank_space, all_datasets_sigonly_surf_plot, ncol = 3, rel_widths = (c(1, 0.05, 1)))

final_sigonly_surf_plots <- plot_grid(blank_space, combined_sigonly_surf_plots, legend, nrow = 3, rel_heights = c(0.05, 1, 0.2))
annotate_figure(final_sigonly_surf_plots, 
                bottom = text_grob("Sex Effect (RESI)", size = 20, x = 0.5, y = 2))

 
```

Sex effects at the edge-level appear to be distributed hierarchically, with males showing stronger connectivity in edges connecting regions across the S-A axis and in the middle of the axis (i.e. association-sensorimotor and middle-middle ranking regions) and females showing higher connectivity between similarly ranked regions (i.e. association-association and sensorimotor-sensorimotor regions). Connectivity in males appear to be more integrative, whereas females exhibit greater segregation.

```{r resi rain cloud plot}

RESI_all_datasets <- rbind(sex.main.PNC.edge %>% mutate(Dataset="PNC"), sex.main.HCPD.edge %>% mutate(Dataset="HCP-D"), sex.main.NKI.edge %>% mutate(Dataset="NKI"), sex.main.HBN.edge %>% mutate(Dataset="HBN"), sex.main.all_datasets.edge %>% mutate(Dataset="All datasets"))
RESI_all_datasets$Dataset <- factor(RESI_all_datasets$Dataset, levels = c("PNC", "HCP-D", "NKI", "HBN", "All datasets"))


# raincloud of RESI edge distribution of data
ggplot(RESI_all_datasets, aes(Dataset, RESI, fill = Dataset, color = Dataset)) +
  
  ggdist::stat_halfeye(
    adjust = .5, 
    width = .6, 
    .width = 0,
    justification = -.3,
    alpha = 0.9,        
    size = 0.6        
  ) +
  
  geom_boxplot(
    width = .25,
    outlier.shape = NA,
    alpha = 0.7,
    linewidth = 0.7
  ) +
  
  geom_hline(
    yintercept = 0,
    linetype = "dashed",
    color = "black",
    linewidth = 0.5
  ) +
  
  paletteer::scale_fill_paletteer_d("PNWColors::Shuksan") +
  paletteer::scale_color_paletteer_d("PNWColors::Shuksan") +
  
  theme_classic() + 
  
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    plot.margin = margin(0, 0, -0.1, 0.5, "cm"),
    axis.text.y = element_text(size = 20),
    axis.text.x = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.line = element_line(color = "black"),
    axis.text = element_text(size = 10, color = "black")
  )


```

Raincloud distribution of RESI sex effect sizes of edges show comparable distributions across datasets. Median effect size appears to be above zero, indicating a shift toward greater connectivity in males across connections, though magnitude of effects at individual edges was small.

# 5. Gradients Analysis

global dispersion is consistently greater in females (small to medium effect). females show greater within-network dispersion too, with FPN and limbic OFC showing up the most often (i.e. parcels within a network are more 'different' from each other in females).  between-network dispersion has greatest effects, with greater dispersion in females across the board with really pronounced effects at DMN A, B, and C with somatomotor and visual networks (so those networks are way more different from each other in females than males; i.e. a these two networks' centroids on PC1 are way more far apart in females).

also HBN is very much the problem child in this analysis. this isn't the best measure of data quality, but one of the things i looked at earlier was comparing PC1 (for the group average connectivity matrix) in thresholded (keep top 10% edges) vs unthresholded matrices. and the correlation in HBN was 0.05 :face_with_spiral_eyes:

For reference, PNC was 0.72, NKI: 0.26, HCPD: 0.25, pooled dataset: 0.49

```{r global dispersion, fig.height = 9, fig.width = 15}
blank_space <- ggplot() + theme_void()
global_disp_row1 <- plot_grid(plot_global_dispersion("PNC", "PNC"), blank_space, plot_global_dispersion("HCPD", "HCP-D"), ncol = 3, rel_widths = c(1, 0.1, 1))
global_disp_row2 <- plot_grid(plot_global_dispersion("NKI", "NKI"), blank_space, plot_global_dispersion("HBN", "HBN"), ncol = 3, rel_widths = c(1, 0.1, 1))
global_disp_p1 <- plot_grid(global_disp_row1, blank_space, global_disp_row2, nrow = 3, rel_heights = c(1, 0.05, 1))


global_disp_p2 <- plot_grid(global_disp_p1, blank_space, plot_global_dispersion("all_datasets", "Pooled Dataset"), ncol = 3, rel_widths = c(1, 0.1, 1))
global_disp_p3 <- plot_grid(blank_space, global_disp_p2, nrow = 2, rel_heights = c(0.05, 1))


annotate_figure(global_disp_p3,
      top = text_grob("Global Dispersion", size = 30), 
      left = text_grob("Dispersion", size = 10, rot = 90))
```

```{r within network dispersion, fig.height = 12, fig.width = 20}
blank_space <- ggplot() + theme_void()
within_disp_row1 <- plot_grid(plot_within_dispersion("PNC", "PNC"), blank_space, plot_within_dispersion("HCPD", "HCP-D"), ncol = 3, rel_widths = c(1, 0.02, 1))
within_disp_row2 <- plot_grid(plot_within_dispersion("NKI", "NKI"), blank_space, plot_within_dispersion("HBN", "HBN"), ncol = 3, rel_widths = c(1, 0.02, 1))
within_disp_p1 <- plot_grid(within_disp_row1, blank_space, within_disp_row2, nrow = 3, rel_heights = c(1, 0.02, 1))
within_disp_datasets <- annotate_figure(within_disp_p1, bottom = text_grob("Sex Effect (RESI)", size = 20))
      
within_disp_p2 <- plot_grid(plot_within_dispersion("all_datasets", "Pooled Dataset"), blank_space, plot_within_overlap(), nrow = 3, rel_heights = c(1, 0.05, 1))
 
within_disp_final <- plot_grid(within_disp_p1, blank_space,  within_disp_p2, blank_space, ncol = 4, rel_widths = c(1, 0.01, 0.5, 0.05))
 

annotate_figure(within_disp_final,
      top = text_grob("Within-Network Dispersion", size = 30))
 
```

```{r between network dispersion,  fig.height = 12, fig.width = 18}
 
# plots
between_PNC <- plot_between_dispersion("PNC", "PNC")
between_HCPD <- plot_between_dispersion("HCPD", "HCP-D")
between_NKI <- plot_between_dispersion("NKI", "NKI")
between_HBN <- plot_between_dispersion("HBN", "HBN")
between_all <- plot_between_dispersion("all_datasets", "Pooled Dataset")
between_overlap <- plot_between_overlap()

# RESI legend
resi_legend_plot <- ggplot(data.frame(x = 1, y = 1, z = 0), aes(x, y, fill = z)) +
  geom_tile() +
  scale_fill_gradientn(colours = red_teal_white(256), values = scales::rescale(c(-0.2, 0, 0.2)),
                       limits = c(-0.23, 0.2), oob = squish, name = NULL) +
  theme_void() +
  theme(legend.position = "bottom", legend.text = element_text(size = 18),
        legend.key.height = unit(0.8, "cm"), legend.key.width = unit(3, "cm"))

resi_legend <- get_legend(resi_legend_plot)

# overlap legend
count_colors <- c("0-1" = "white", "2" = "#F6D0B5", "3" = "#D95F8D", "4" = "#AD2A72")

overlap_legend_plot <- ggplot(
  data.frame(overlap = factor(c("0-1", "2", "3", "4"), levels = c("0-1", "2", "3", "4"))),
  aes(x = overlap, fill = overlap)
) +
  geom_bar() +
  scale_fill_manual(values = count_colors, drop = FALSE,
                    guide = guide_legend(direction = "horizontal", label.position = "bottom",
                                         override.aes = list(colour = "black", linewidth = 0.5))) +
  theme_void() +
  theme(legend.title = element_blank(), legend.text = element_text(size = 18),
        legend.key.size = unit(1.3, "cm"), legend.position = "bottom")

overlap_legend <- get_legend(overlap_legend_plot)

# left column: 4 datasets + RESI legend
between_four <- plot_grid(between_PNC, between_HCPD, between_NKI, between_HBN, ncol = 2)

between_col1 <- annotate_figure(
  plot_grid(between_four, resi_legend, nrow = 2, rel_heights = c(1, 0.08)),
  bottom = text_grob("Sex Effect (RESI)", size = 20, y = 0.5)
)

# right column: pooled + overlap + overlap legend
between_col2_plots <- plot_grid(between_all, between_overlap, nrow = 2)

overlap_legend_layout <- plot_grid(blank_space, overlap_legend, ncol = 2, rel_widths = c(0.08, 1))
overlap_legend_layout <- plot_grid(overlap_legend_layout, blank_space, nrow = 2, rel_heights = c(1, 0.1))

between_col2 <- annotate_figure(
  plot_grid(between_col2_plots, overlap_legend_layout, nrow = 2, rel_heights = c(1, 0.1)),
  bottom = text_grob("Number of Datasets", size = 20, y = 0.9, x = 0.5)
)

# final layout
between_dispersion_figure <- plot_grid(blank_space, plot_grid(between_col1, between_col2, blank_space,
                                       ncol = 3, rel_widths = c(2, 1, 0.1)), nrow = 2, rel_heights = c(0.01, 1))

annotate_figure(between_dispersion_figure,
                top = text_grob("Between-Network Dispersion", size = 10))

```

## Distribution of PC1

Interestingly, the overall male/female PC1 distributions and mean cortical PC1 maps look quite similar. so the dispersion sex effects above don’t seem to reflect a simple overall difference in PC1... and i think the key is that dispersion is looking within subjects (i.e. in a given subject, how spread out are their 200 parcel loadings around that subject’s own PC1 median?). So even though females and males have a very similar average PC1 spatial organization, within individuals, females tend to have parcels/networks that are more spread out along PC1. And looking at average PC1 loadings ends up obscuring these within-individual difference between males/females

```{r distribution of PC1, fig.height = 7, fig.width = 15}
sex_colors <- c(Female = "#C53121", Male = "#0B8CACFF")

root <- file.path(root, "covariate_analyses", "sex_diff")
datasets <- c("PNC", "NKI", "HCPD", "HBN", "all_datasets")

 
pc1_long <- map_dfr(datasets, function(dataset) {
  df <- read.csv(sprintf("%s/output/%s/gradient_dispersion/pc1_loadings_long_%s.csv", root, dataset, dataset))
  if(dataset == "all_datasets") df$dataset <- "all_datasets"
  df
})

pc1_long$sex <- factor(pc1_long$sex, levels = c("Male", "Female"))

plot_pc1_density <- function(dataset, title) {
  df <- pc1_long %>% filter(dataset == !!dataset)
  
  ggplot(df, aes(x = pc1, fill = sex, color = sex)) +
    geom_density(alpha = 0.25, linewidth = 1) +
    scale_fill_manual(values = sex_colors) +
    scale_color_manual(values = sex_colors) +
    coord_cartesian(xlim = c(-4, 6)) +
    labs(title = title, x = NULL, y = NULL) +
    theme_classic(base_size = 20) +
    theme(legend.position = "none",
          plot.title = element_text(size = 20, hjust = 0.5),
          axis.text = element_text(size = 20, color = "black"))
}

pc1_density_PNC <- plot_pc1_density("PNC", "PNC")
pc1_density_HCPD <- plot_pc1_density("HCPD", "HCP-D")
pc1_density_NKI <- plot_pc1_density("NKI", "NKI")
pc1_density_HBN <- plot_pc1_density("HBN", "HBN")
pc1_density_all <- plot_pc1_density("all_datasets", "Pooled Dataset")

sex_legend_plot <- ggplot(data.frame(sex = factor(c("Female", "Male"), levels = c("Male", "Female")), x = 1:2, y = 1),
                          aes(x, y, fill = sex, color = sex)) +
  geom_point(shape = 21, size = 6) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  guides(fill = guide_legend(direction = "horizontal", override.aes = list(size = 6, alpha = 0.5)), color = "none") +
  theme_void() +
  theme(legend.position = "bottom", legend.title = element_blank(),
        legend.text = element_text(size = 20), legend.key.size = unit(1.1, "cm"))

sex_legend <- get_legend(sex_legend_plot)

blank_space <- ggplot() + theme_void()

pc1_density_row1 <- plot_grid(pc1_density_PNC, blank_space, pc1_density_HCPD, ncol = 3, rel_widths = c(1, 0.1, 1))
pc1_density_row2 <- plot_grid(pc1_density_NKI, blank_space, pc1_density_HBN, ncol = 3, rel_widths = c(1, 0.1, 1))
pc1_density_p1 <- plot_grid(pc1_density_row1, blank_space, pc1_density_row2, nrow = 3, rel_heights = c(1, 0.05, 1))
pc1_density_p2 <- plot_grid(pc1_density_p1, blank_space, pc1_density_all, ncol = 3, rel_widths = c(1, 0.1, 1))

pc1_density_figure <- plot_grid(pc1_density_p2, sex_legend, nrow = 2, rel_heights = c(1, 0.08))

pc1_density_figure <- annotate_figure(pc1_density_figure,
                                      top = text_grob("PC1 Distribution", size = 30),
                                      left = text_grob("Density", size = 10, rot = 90),
                                      bottom = text_grob("PC1 Loading", size = 10))

pc1_density_figure

```

## PC1 loadings in males vs females

```{r PC1 in males and females, fig.height = 10, fig.width = 15}

library(tidyverse)
library(ggseg)
library(ggsegSchaefer)
library(cowplot)
library(scales)
library(paletteer)

root <- file.path(root, "covariate_analyses", "sex_diff")
datasets <- c("PNC", "NKI", "HCPD", "HBN", "all_datasets")

pc1_brain <- map_dfr(datasets, function(dataset) {
  if(dataset == "all_datasets") {
    df <- read.csv(sprintf("%s/output/%s/gradient_dispersion/pc1_loadings_long_%s.csv", root, dataset, dataset)) %>%
      group_by(sex, parcel, parcel_label, hemisphere, network) %>%
      summarise(pc1_mean = mean(pc1, na.rm = TRUE), # fyi: pc1_mean at parcel 1 = mean(PC1 at parcel 1 for every female subject across PNC + NKI + HCPD + HBN)
                pc1_median = median(pc1, na.rm = TRUE),
                pc1_sd = sd(pc1, na.rm = TRUE),
                n = sum(!is.na(pc1)),
                pc1_se = pc1_sd / sqrt(n), .groups = "drop") %>%
      mutate(dataset = "all_datasets")
  } else {
    df <- read.csv(sprintf("%s/output/%s/gradient_dispersion/pc1_parcel_by_sex_%s.csv", root, dataset, dataset))
  }
  
  df <- df %>% rename(region = parcel_label) %>% mutate(region = paste0("17", region))
  df
})




# common symmetric PC1 scale across all datasets and both sexes
pc1_lim <- max(abs(pc1_brain$pc1_mean), na.rm = TRUE)
ylim1 <- -pc1_lim
ylim2 <- pc1_lim

# adapted from your existing plot_cortex() function
plot_cortex_pc1 <- function(df, hemi, sex_name, ylim1, ylim2, horizontal_layout = NULL) {
  df <- df %>% filter(sex == sex_name)

  if(hemi == "left") {
    cortical_pos1 <- "left lateral"
    cortical_pos2 <- "left medial"
  } else {
    cortical_pos1 <- "right lateral"
    cortical_pos2 <- "right medial"
  }

  plot_lateral <- ggplot() +
    geom_brain(data = df, atlas = schaefer17_200, mapping = aes(fill = pc1_mean),
               show.legend = TRUE, hemi = hemi, position = position_brain(cortical_pos1)) +
    paletteer::scale_fill_paletteer_c("pals::ocean.curl",
                                      limits = c(ylim1, ylim2), oob = squish, na.value = "white") +
    theme_void() +
    theme(legend.position = "none",
          legend.title = element_blank(),
          plot.margin = unit(c(0.1, -1, 0.1, -1), "cm"),
          plot.title = element_blank())

  plot_medial <- ggplot() +
    geom_brain(data = df, atlas = schaefer17_200, mapping = aes(fill = pc1_mean),
               show.legend = TRUE, hemi = hemi, position = position_brain(cortical_pos2)) +
    paletteer::scale_fill_paletteer_c("pals::ocean.curl",
                                      limits = c(ylim1, ylim2), oob = squish, na.value = "white") +
    theme_void() +
    theme(legend.position = "none",
          legend.title = element_blank(),
          plot.margin = unit(c(0.1, -1, 0.1, -1), "cm"),
          plot.title = element_blank())

  if(is.null(horizontal_layout)) {
    return(plot_grid(plot_lateral, plot_medial, ncol = 1, rel_heights = c(1, 1), align = "v", axis = "lr"))
  } else {
    return(plot_grid(plot_lateral, plot_medial, ncol = 2, align = "v", axis = "lr"))
  }
}

# individual datasets: female and male side-by-side;
# each sex has left/right hemispheres, each shown lateral + medial vertically
plot_pc1_dataset <- function(dataset, title) {
  df <- pc1_brain %>% filter(dataset == !!dataset)

  female_left <- plot_cortex_pc1(df, "left", "Female", ylim1, ylim2)
  female_right <- plot_cortex_pc1(df, "right", "Female", ylim1, ylim2)
  male_left <- plot_cortex_pc1(df, "left", "Male", ylim1, ylim2)
  male_right <- plot_cortex_pc1(df, "right", "Male", ylim1, ylim2)

  female <- plot_grid(female_left, female_right, ncol = 2)
  male <- plot_grid(male_left, male_right, ncol = 2)

  female <- plot_grid(ggdraw() + draw_label("Female", size = 18),
                      female, ncol = 1, rel_heights = c(0.08, 1))
  male <- plot_grid(ggdraw() + draw_label("Male", size = 18),
                    male, ncol = 1, rel_heights = c(0.08, 1))

  brains <- plot_grid(female, male, ncol = 2)

  plot_grid(ggdraw() + draw_label(title, size = 20),
            brains, ncol = 1, rel_heights = c(0.08, 1))
}

# pooled dataset: all 8 views in one row
plot_pc1_pooled <- function() {
  df <- pc1_brain %>% filter(dataset == "all_datasets")

  female_left <- plot_cortex_pc1(df, "left", "Female", ylim1, ylim2, horizontal_layout = TRUE)
  female_right <- plot_cortex_pc1(df, "right", "Female", ylim1, ylim2, horizontal_layout = TRUE)
  male_left <- plot_cortex_pc1(df, "left", "Male", ylim1, ylim2, horizontal_layout = TRUE)
  male_right <- plot_cortex_pc1(df, "right", "Male", ylim1, ylim2, horizontal_layout = TRUE)

  female <- plot_grid(female_left, female_right, ncol = 2)
  male <- plot_grid(male_left, male_right, ncol = 2)

  female <- plot_grid(ggdraw() + draw_label("Female", size = 18),
                      female, ncol = 1, rel_heights = c(0.10, 1))
  male <- plot_grid(ggdraw() + draw_label("Male", size = 18),
                    male, ncol = 1, rel_heights = c(0.10, 1))

  blank_space <- ggplot() + theme_void()

  brains <- plot_grid(female, blank_space, male, ncol = 3, rel_widths = c(1, 0.08, 1))

  plot_grid(ggdraw() + draw_label("Pooled Dataset", size = 20),
            brains, ncol = 1, rel_heights = c(0.10, 1))
}
# dataset plots
pc1_brain_PNC <- plot_pc1_dataset("PNC", "PNC")
pc1_brain_HCPD <- plot_pc1_dataset("HCPD", "HCP-D")
pc1_brain_NKI <- plot_pc1_dataset("NKI", "NKI")
pc1_brain_HBN <- plot_pc1_dataset("HBN", "HBN")
pc1_brain_pooled <- plot_pc1_pooled()

# shared PC1 legend
pc1_legend_plot <- ggplot(data.frame(x = 1, y = 1, pc1 = 0), aes(x, y, fill = pc1)) +
  geom_tile() +
  paletteer::scale_fill_paletteer_c("pals::ocean.curl",
                                    limits = c(ylim1, ylim2), oob = squish, name = NULL) +
  theme_void() +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 18),
        legend.key.height = unit(0.8, "cm"),
        legend.key.width = unit(3, "cm"))

pc1_legend <- get_legend(pc1_legend_plot)
blank_space <- ggplot() + theme_void()

# four individual datasets
pc1_brain_row1 <- plot_grid(pc1_brain_PNC, blank_space, pc1_brain_HCPD,
                            ncol = 3, rel_widths = c(1, 0.1, 1))

pc1_brain_row2 <- plot_grid(pc1_brain_NKI, blank_space, pc1_brain_HBN,
                            ncol = 3, rel_widths = c(1, 0.1, 1))

pc1_brain_four <- plot_grid(pc1_brain_row1, blank_space, pc1_brain_row2,
                            nrow = 3, rel_heights = c(1, 0.1, 1))

# pooled dataset underneath
pc1_brain_main <- plot_grid(pc1_brain_four, blank_space, pc1_brain_pooled,
                            nrow = 3, rel_heights = c(2, 0.1, 0.55))

# legend underneath everything
pc1_brain_with_legend <- plot_grid(pc1_brain_main, blank_space, pc1_legend, blank_space, 
                                   nrow = 4, rel_heights = c(1, 0.06, 0.06, 0.06))

pc1_brain_figure <- annotate_figure(
  pc1_brain_with_legend,
  bottom = text_grob("Mean PC1 Loading", size = 20, vjust = 0.05)
)

pc1_brain_figure
```

# Supplementary analyses

## Histogram of WNC and BNC

```{r BNC and WNC histograms, fig.height = 8, fig.width = 20}
# load subject levels BNC and WNC
PNC_BNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "PNC", "BNC", "BNC_subxparcel_matrix_schaefer200x17.csv"))
HCPD_BNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HCPD", "BNC", "BNC_subxparcel_matrix_schaefer200x17.csv"))
NKI_BNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "NKI", "BNC", "BNC_subxparcel_matrix_schaefer200x17.csv"))
HBN_BNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HBN", "BNC", "BNC_subxparcel_matrix_schaefer200x17.csv"))

PNC_WNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "PNC", "WNC", "WNC_subxparcel_matrix_schaefer200x17.csv"))
HCPD_WNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HCPD", "WNC", "WNC_subxparcel_matrix_schaefer200x17.csv"))
NKI_WNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "NKI", "WNC", "WNC_subxparcel_matrix_schaefer200x17.csv"))
HBN_WNC_subxparcel <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "HBN", "WNC", "WNC_subxparcel_matrix_schaefer200x17.csv"))

# hist function
make_hist_plot <- function(subxparcel_df, dataset, xlim1, xlim2, color) {
  long_df <- subxparcel_df %>%
    pivot_longer(cols = -subject, names_to = "region", values_to = "value") %>%
    filter(!is.na(value))
  
  p <- ggplot(long_df, aes(x = value)) +
    geom_histogram(bins = 20, color = color, fill = color, linewidth = 0.7, alpha = 0.7) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "#33271EFF", linewidth = 0.7) +
    theme_classic() +
    labs(x = "", y = "") + ggtitle(dataset) +
    theme(axis.text = element_text(size = 20, color = "#33271EFF"),
          axis.title = element_text(size = 20),
          plot.title = element_text(size = 20, hjust = 0.5)) + xlim(xlim1, xlim2)
  
  return(p)
}


# make histograms
BNC_hist <- plot_grid(blank_space, plot_grid(make_hist_plot(PNC_BNC_subxparcel, "PNC", -0.5, 0.5, color = "#B7E6A5FF"), make_hist_plot(HCPD_BNC_subxparcel, "HCP-D", -0.5, 0.5, color = "#B7E6A5FF"),
                                 make_hist_plot(NKI_BNC_subxparcel,"NKI", -0.5, 0.5, color = "#B7E6A5FF"), make_hist_plot(HBN_BNC_subxparcel,"HBN", -0.5, 0.5, color = "#B7E6A5FF")), 
                      nrow = 2, rel_heights = c(0.03, 1))


WNC_hist <- plot_grid(blank_space, plot_grid(make_hist_plot(PNC_WNC_subxparcel, "PNC", -0.7, 1, color = "#64A8A8FF"), make_hist_plot(HCPD_WNC_subxparcel, "HCP-D", -0.7, 1, color = "#64A8A8FF"),
                                 make_hist_plot(NKI_WNC_subxparcel,"NKI", -0.7, 1, color = "#64A8A8FF"), make_hist_plot(HBN_WNC_subxparcel,"HBN", -0.7, 1, color = "#64A8A8FF")), 
                      nrow = 2, rel_heights = c(0.03, 1))


BNC_hist_plots <- annotate_figure(BNC_hist, bottom = text_grob("Between-Network Connectivity", size = 10),
                left = text_grob("Count", size = 10, rot = 90),
                top = text_grob("Distribution of BNC", size = 10))



WNC_hist_plots <- annotate_figure(WNC_hist, bottom = text_grob("Within-Network Connectivity", size = 10),
                left = text_grob("Count", size = 10, rot = 90),
                top = text_grob("Distribution of WNC", size = 10))


plot_grid(BNC_hist_plots, blank_space, WNC_hist_plots, ncol = 3, rel_widths = c(1, 0.1, 1))
```

## Age-by-sex interaction across ALL datasets

- WNC in 11 regions (5%; schaefer200x7) and 22 regions (11%; schafer200x17) has some age-by-sex effects when datasets are pooled.
- network-pair connectivity also has some significant age-by-sex interactions

```{r load age by sex interaction across datasets}
FC_strength_schaefer7 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "FC_strength", "all_datasets_GAM_agebysex_interaction_schaefer200x7.csv"))
FC_strength_schaefer7 <- sig.effects.all_datasets(FC_strength_schaefer7, "FC_strength", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
FC_strength_schaefer17 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "FC_strength", "all_datasets_GAM_agebysex_interaction_schaefer200x17.csv"))
FC_strength_schaefer17 <- sig.effects.all_datasets(FC_strength_schaefer17, "FC_strength", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")

BNC_schaefer7 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "BNC", "all_datasets_GAM_agebysex_interaction_schaefer200x7.csv"))
BNC_schaefer7 <- sig.effects.all_datasets(BNC_schaefer7, "BNC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
BNC_schaefer17 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "BNC", "all_datasets_GAM_agebysex_interaction_schaefer200x17.csv"))
BNC_schaefer17 <- sig.effects.all_datasets(BNC_schaefer17, "BNC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")

WNC_schaefer7 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "WNC", "all_datasets_GAM_agebysex_interaction_schaefer200x7.csv"))
WNC_schaefer7 <- sig.effects.all_datasets(WNC_schaefer7, "WNC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
WNC_schaefer17 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "WNC", "all_datasets_GAM_agebysex_interaction_schaefer200x17.csv"))
WNC_schaefer17 <- sig.effects.all_datasets(WNC_schaefer17, "WNC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
#WNC_schaefer17 %>% arrange(desc(int_sig_effect))

netpair_schaefer7 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "networkpair", "all_datasets_GAM_agebysex_interaction_schaefer200x7.csv"))
netpair_schaefer7 <- sig.effects.all_datasets(netpair_schaefer7, "netpair", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
netpair_schaefer17 <- read.csv(file.path(root, "covariate_analyses", "sex_diff", "output", "all_datasets", "GAM", "networkpair", "all_datasets_GAM_agebysex_interaction_schaefer200x17.csv"))
netpair_schaefer17 <- sig.effects.all_datasets(netpair_schaefer17, "netpair", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
#netpair_schaefer17 %>% arrange(desc(int_sig_effect))
```

```{r plot WNC age by sex regions, fig.height = 10, fig.width = 10}
WNC_schaefer17 <- WNC_schaefer17 %>% mutate(region = if_else(startsWith(region, "17"), region, paste0("17", region)))
sex.int.all_dataset.WNC_lh <- plot_cortex_int(WNC_schaefer17, hemi = "left", measure = "int_sig_effect", ylim1 = 1, ylim2 = 9, atlas = "schaefer17_200") 
sex.int.all_dataset.WNC_rh <- plot_cortex_int(WNC_schaefer17, hemi = "right", measure = "int_sig_effect", ylim1 = 1, ylim2 = 9, atlas = "schaefer17_200")

ylim1 = 1
ylim2 = 9
p <- ggplot() + 
    geom_brain(data = WNC_schaefer17, atlas = schaefer17_200, 
               mapping=aes(fill=int_sig_effect, colour=significant_status, size=I(0.7)), 
               show.legend=TRUE) +
    scale_fill_paletteer_c("ggthemes::Blue-Green Sequential", na.value = "white") + 
    scale_colour_manual(values = c("Sig" = "black", "Nonsig" = "grey50")) + 
    theme_void() +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 10),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm")) + guides(color = "none")
  
  
legend <- get_legend(p)
blank_space <- ggplot() + theme_void()

annotate_figure(
  plot_grid(
    annotate_figure(
      plot_grid(
        sex.int.all_dataset.WNC_lh,
        sex.int.all_dataset.WNC_rh,
        ncol = 2
      ),
      top = text_grob("WNC age-by-sex all datasets (Schaefer 200x17)", size = 10)
    ),
    legend,
    ncol = 1,
    rel_heights = c(1, 0.2)
  ),
  bottom = text_grob("Interaction (F-value)", size = 10)
)

 print(WNC_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))
```

```{r print networkpair age by sex pairs}
 print(netpair_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))

 print(WNC_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))

```

```{r load WNC age by sex dev trajectories}
agebysex.all_datasets.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_fitted_%4$s.csv", output_root, "all_datasets", "WNC", "schaefer200x17"))
agebysex.all_datasets.WNC$region <- paste0("17", agebysex.all_datasets.WNC$region)
agebysex.all_datasets.WNC <- agebysex.all_datasets.WNC %>% rename(age=smooth_var)

```

```{r WNC dev trajectories vis, fig.height = 20, fig.width = 20}
WNC_interaction_regions <- WNC_schaefer17 %>% filter(significant.fdr == 1) %>% pull(region) #%>% paste0('17', .)
agebysex.all_datasets.WNC.interaction <- agebysex.all_datasets.WNC %>% filter(region %in% WNC_interaction_regions)

colorF = "#e67239"
colorM = "#0B8CACFF"
WNC.interaction.all_datasets.plots <- lapply(WNC_interaction_regions, plot_trajectories_bycov, df = agebysex.all_datasets.WNC, covariate = "sex", y.limits = range(agebysex.all_datasets.WNC$fitted), colorF, colorM, margin = 0)
names(WNC.interaction.all_datasets.plots) <- WNC_interaction_regions 
 
 
# get legend
y.limits = range(agebysex.all_datasets.WNC$fitted)
df_plot <- agebysex.all_datasets.WNC %>% filter(region %in% "17Networks_LH_VisCent_ExStr_3")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(aes(color = sex), linewidth = 3) +
    theme_classic() +
    scale_y_continuous(limits = y.limits) +
    scale_color_manual(values = c("Female" = colorF, "Male" = colorM)) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"))  
dev_traj_legend <- get_legend(plot)


WNC.interaction.all_datasets.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.interaction.all_datasets.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.interaction.all_datasets.plots.text <- annotate_figure(WNC.interaction.all_datasets.plots.combined, bottom = text_grob("Age (years)", size = 10),
                left = text_grob("Within Network Connectivity", size = 10, rot = 90),
                top = text_grob("Developmental Patterns of Within Network Connectivity by Sex", size = 10))


plot_grid(WNC.interaction.all_datasets.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r load netpair age by sex dev trajectories}
agebysex.all_datasets.netpair <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_fitted_%4$s.csv", output_root, "all_datasets", "networkpair", "schaefer200x17"))
agebysex.all_datasets.netpair <- agebysex.all_datasets.netpair %>% rename(age=smooth_var)

```

```{r netpair dev trajectories vis, fig.height = 25, fig.width = 15}
netpair_interaction_regions <- netpair_schaefer17 %>% filter(significant.fdr == 1) %>% pull(region) %>% gsub("_", " - ", .)
agebysex.all_datasets.netpair$region <- gsub("_", " - ", agebysex.all_datasets.netpair$region)
agebysex.all_datasets.netpair.interaction <- agebysex.all_datasets.netpair %>% filter(region %in% netpair_interaction_regions)

colorF = "#A51122FF"
colorM = "#0B8CACFF"
netpair.interaction.all_datasets.plots <- lapply(netpair_interaction_regions, plot_trajectories_bycov, df = agebysex.all_datasets.netpair, covariate = "sex", y.limits = range(agebysex.all_datasets.netpair$fitted), colorF, colorM, margin = 2)
names(netpair.interaction.all_datasets.plots) <- netpair_interaction_regions 

 
# get legend
y.limits = range(agebysex.all_datasets.netpair$fitted)
df_plot <- agebysex.all_datasets.netpair %>% filter(region %in% "defaultA - defaultA")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(aes(color = sex), linewidth = 3) +
    theme_classic() +
    scale_y_continuous(limits = y.limits) +
    scale_color_manual(values = c("Female" = colorF, "Male" = colorM)) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"))  

dev_traj_legend <- get_legend(plot)


netpair.interaction.all_datasets.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = netpair.interaction.all_datasets.plots, ncol = 2), nrow = 2, rel_heights = c(0.03, 1))
netpair.interaction.all_datasets.plots.text <- annotate_figure(netpair.interaction.all_datasets.plots.combined, bottom = text_grob("Age (years)", size = 10),
                left = text_grob("Connectivity between Pairs of Networks", size = 10, rot = 90),
                top = text_grob("Developmental Patterns of Within Network Connectivity by Sex", size = 10))


plot_grid(plot_grid(netpair.interaction.all_datasets.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05)), blank_space, ncol = 2, rel_widths = c(1, 0.05))

```

# Clinical measures exploration - just fyi

- To quantify whether pfactor and sex affect similar edges/networks: topographical overlap of effects

- To test whether one map statistically predicts another: spatial covariance structure

- Goal: Does the pattern of connections that differ by pfactor resemble the pattern that differs by sex?

```{r load edge sex, fig.height = 10, fig.width = 9}
# edge gam output
clinical.main.all_datasets.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_clinical_maineffects_schaefer200x17.csv", output_root, "all_datasets", "edge"))
clinical.main.all_datasets.edge_pfactor <- clinical.main.all_datasets.edge %>% filter(covariate == "p_factor_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
clinical.main.all_datasets.edge_int <- clinical.main.all_datasets.edge %>% filter(covariate == "internalizing_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
clinical.main.all_datasets.edge_ext <- clinical.main.all_datasets.edge %>% filter(covariate == "externalizing_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
clinical.main.all_datasets.edge_att <- clinical.main.all_datasets.edge %>% filter(covariate == "attention_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)

clinical.main.all_datasets.edge_sex <- clinical.main.all_datasets.edge %>% filter(covariate == "sex") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
 

# make df for plotting (and do FDR correction)
double.pfactor <- make_double_df(clinical.main.all_datasets.edge_pfactor, "edge", "pfactor", "All datasets")
double.int <- make_double_df(clinical.main.all_datasets.edge_int, "edge", "internalizing", "All datasets")
double.ext <- make_double_df(clinical.main.all_datasets.edge_ext, "edge", "externalizing", "All datasets")
double.att <- make_double_df(clinical.main.all_datasets.edge_att, "edge", "attention", "All datasets")
double.sex <- make_double_df(clinical.main.all_datasets.edge_sex, "edge", "sex", "All datasets")

pfactor_surf <- make_surface_plot(double.pfactor, dataset = "P-factor", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")

int_surf <- make_surface_plot(double.int, dataset = "Internalizing", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")
 
ext_surf <- make_surface_plot(double.ext, dataset = "Externalizing", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")
att_surf <- make_surface_plot(double.att, dataset = "Attention", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")

row1_clinical <- plot_grid(pfactor_surf, int_surf, ncol=2)
row2_clinical <- plot_grid(ext_surf, att_surf, ncol=2)
plot_grid(row1_clinical, blank_space, row2_clinical, nrow = 3, rel_heights = c(1, 0.2, 1))
  
```

```{r pfactor explore, fig.height = 10, fig.width = 10}
 

PNC_config_data <- fromJSON(file=sprintf(file.path(root, "covariate_analyses", "sex_diff", "code", "config", "config_%1$s.json"), "PNC"))
HCPD_config_data <- fromJSON(file=sprintf(file.path(root, "covariate_analyses", "sex_diff", "code", "config", "config_%1$s.json"), "HCPD"))
NKI_config_data <- fromJSON(file=sprintf(file.path(root, "covariate_analyses", "sex_diff", "code", "config", "config_%1$s.json"), "NKI"))
HBN_config_data <- fromJSON(file=sprintf(file.path(root, "covariate_analyses", "sex_diff", "code", "config", "config_%1$s.json"), "HBN"))

################### 
# Define functions 
###################
# load pfactor data and merge with demographics
load_pfactor_data <- function(file_path) {
  pfactor <- fread(file_path)
  pfactor <- pfactor %>% rename(sub = participant_id)
  pfactor$sub <- paste0("sub-", pfactor$sub)
  pfactor <- pfactor %>% select(sub, p_factor_mcelroy_harmonized_all_samples, internalizing_mcelroy_harmonized_all_samples, externalizing_mcelroy_harmonized_all_samples, attention_mcelroy_harmonized_all_samples)
  pfactor <- pfactor[!duplicated(pfactor), ]
  pfactor <- pfactor[complete.cases(pfactor), ]
  return(pfactor)
}

# load demographics for all datasets and combine
PNC_demographics <- read.csv(PNC_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "PNC") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
NKI_demographics <- read.csv(NKI_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "NKI") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
HBN_demographics <- read.csv(HBN_config_data$demographics, stringsAsFactors = TRUE) %>% rename(site = ses) %>% mutate(dataset_site = paste0("HBN_", site)) %>% select(sub, age, sex, meanFD_avgSes, dataset_site)

#load clinical measures
PNC_pfactor <- load_pfactor_data(file.path(root, "covariate_analyses", "pfactor", "input", "PNC", "sample_info", "study-PNC_desc-participants.tsv"))
NKI_pfactor <- load_pfactor_data(file.path(root, "covariate_analyses", "pfactor", "input", "NKI", "sample_info", "study-NKI_desc-participants.tsv"))
NKI_pfactor$sub <- gsub("sub-", "", NKI_pfactor$sub)
HBN_pfactor <- load_pfactor_data(file.path(root, "covariate_analyses", "pfactor", "input", "HBN", "sample_info", "study-HBN_desc-participants.tsv"))

PNC_demographics <- inner_join(PNC_pfactor, PNC_demographics,by = "sub")
NKI_demographics <- inner_join(NKI_pfactor, NKI_demographics,by = "sub")
HBN_demographics <- inner_join(HBN_pfactor, HBN_demographics,by = "sub")

demographics <- rbind(PNC_demographics, NKI_demographics, HBN_demographics)
# load demographics for all datasets and combine
PNC_demographics <- read.csv(PNC_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "PNC") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
NKI_demographics <- read.csv(NKI_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "NKI") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
HBN_demographics <- read.csv(HBN_config_data$demographics, stringsAsFactors = TRUE) %>% rename(site = ses) %>% mutate(dataset_site = paste0("HBN_", site)) %>% select(sub, age, sex, meanFD_avgSes, dataset_site)

#load clinical measures
PNC_pfactor <- load_pfactor_data(file.path(root, "covariate_analyses", "pfactor", "input", "PNC", "sample_info", "study-PNC_desc-participants.tsv"))
NKI_pfactor <- load_pfactor_data(file.path(root, "covariate_analyses", "pfactor", "input", "NKI", "sample_info", "study-NKI_desc-participants.tsv"))
NKI_pfactor$sub <- gsub("sub-", "", NKI_pfactor$sub)
HBN_pfactor <- load_pfactor_data(file.path(root, "covariate_analyses", "pfactor", "input", "HBN", "sample_info", "study-HBN_desc-participants.tsv"))

PNC_demographics <- inner_join(PNC_pfactor, PNC_demographics,by = "sub")
NKI_demographics <- inner_join(NKI_pfactor, NKI_demographics,by = "sub")
HBN_demographics <- inner_join(HBN_pfactor, HBN_demographics,by = "sub")

demographics <- rbind(PNC_demographics, NKI_demographics, HBN_demographics)



pfactor_plot <- ggplot(demographics, aes(x = sex, y = p_factor_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "P-factor by Sex",
       x = "Sex", y = "P-factor (McElroy Harmonized)") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))



int_plot <- ggplot(demographics, aes(x = sex, y = internalizing_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Internalizing by Sex",
       x = "Sex", y = "Internalizing") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))


ext_plot <- ggplot(demographics, aes(x = sex, y = externalizing_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Externalizing by Sex",
       x = "Sex", y = "Externalizing") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))

att_plot <- ggplot(demographics, aes(x = sex, y = attention_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Attention by Sex",
       x = "Sex", y = "Attention") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))

plot_grid(pfactor_plot, int_plot, ext_plot, att_plot, ncol=2)

```

```{r}
library(ggpubr)
library(dplyr)
library(effsize)

 
# Compute t-test and effect size
t_out <- t.test(p_factor_mcelroy_harmonized_all_samples ~ sex, data = demographics)
cohen_d <- effsize::cohen.d(p_factor_mcelroy_harmonized_all_samples ~ sex, data = demographics)$estimate
 

p_str <- ifelse(t_out$p.value < 0.0001, "< 0.0001",
                sprintf("%.3f", t_out$p.value))

stat_label <- sprintf(
  "t(%.0f) = %.2f, p %s, Cohen's d = %.2f",
  t_out$parameter,
  t_out$statistic,
  p_str,
  cohen_d
)
 
 
```
