---
title: "Sex Differences in Functional Connectivity"
author: "Audrey Luo"
output: 
  html_document:
    highlight: haddock
    code_folding: hide
    number_sections: no
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    number_sections: no
    toc: yes
    toc_depth: '4'
  word_document:
    toc: yes
    toc_depth: '4'
urlcolor: blue
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(ggpubr)
library(ggseg)
library(ggsegSchaefer)
library(effsize)
library(ggdist)
library(knitr)
library(kableExtra)
library(paletteer)
library(scales)
 
source("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/results/sex_diff_draft_figures.R")
source("/cbica/projects/network_replication/software/perm.sphere.p.R")

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, include = TRUE) 


proj_root <- "/cbica/projects/network_replication/covariate_analyses/sex_diff/"
input_root <- paste0(proj_root, "input")
output_root <- paste0(proj_root, "output")
 
```

```{r set color palette}
red_teal_white_base <- c( "#A51122FF","#E14C21FF", "#F8A86BFF", "#FFFFFFFF","#ACDFD3FF", "#0B8CACFF","#324DA0FF")
red_teal_white <- colorRampPalette(red_teal_white_base)
 
```

```{r load SAaxis and labels and spin test}
# load S-A axis
schaefer200x17_SAaxis <- read.csv("/cbica/projects/network_replication/SAaxis/schaefer200x17_SAaxis.csv")
schaefer200x17_SAaxis <- schaefer200x17_SAaxis %>% rename(region=label)

# load parcel labels
schaefer200x17.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x17_regionlist_final.csv")
schaefer200x17.labels <- schaefer200x17.labels$label
  
# load network-pair labels
schaefer200x17.networkpair.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x17_netpair_labels_noduplicates.csv")
schaefer200x17.networkpair.labels <- schaefer200x17.networkpair.labels[,1]

# load permuted schaefer200
perm.id.full_schaefer200x17 <- readRDS("/cbica/projects/network_replication/software/rotate_parcellation/schaefer200x17.coords_sphericalrotations_N10k_seed10.rds")
```


# 1. Sex differences in between- and within-network connectivity
Thus, we hypothesized that males would show greater between-network connectivity, whereas females would show greater within-network connectivity. 

```{r load BNC sex effect}
sex.main.PNC.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "BNC"))
sex.main.PNC.BNC$region <- paste0("17", sex.main.PNC.BNC$region)
sex.main.PNC.BNC <- sig.effects(sex.main.PNC.BNC, "BNC", "sex", "PNC")
resi.PNC.BNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/resi/BNC/PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv") # load RESI effect sizes
resi.PNC.BNC$region <- paste0("17", resi.PNC.BNC$region )
resi.PNC.BNC <- resi.PNC.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.PNC.BNC <- merge(sex.main.PNC.BNC, resi.PNC.BNC)

sex.main.HCPD.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "BNC"))
sex.main.HCPD.BNC <- sig.effects(sex.main.HCPD.BNC, "BNC", "sex", "HCPD")
sex.main.HCPD.BNC$region <- paste0("17", sex.main.HCPD.BNC$region)
resi.HCPD.BNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/resi/BNC/HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.HCPD.BNC$region <- paste0("17", resi.HCPD.BNC$region )
resi.HCPD.BNC <- resi.HCPD.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HCPD.BNC <- merge(sex.main.HCPD.BNC, resi.HCPD.BNC)

sex.main.NKI.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "BNC"))
sex.main.NKI.BNC <- sig.effects(sex.main.NKI.BNC, "BNC", "sex", "NKI")
sex.main.NKI.BNC$region <- paste0("17", sex.main.NKI.BNC$region)
resi.NKI.BNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/resi/BNC/NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.NKI.BNC$region <- paste0("17", resi.NKI.BNC$region )
resi.NKI.BNC <- resi.NKI.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.NKI.BNC <- merge(sex.main.NKI.BNC, resi.NKI.BNC)

sex.main.HBN.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "BNC"))
sex.main.HBN.BNC <- sig.effects(sex.main.HBN.BNC, "BNC", "sex", "HBN")
sex.main.HBN.BNC$region <- paste0("17", sex.main.HBN.BNC$region)
resi.HBN.BNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/resi/BNC/HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.HBN.BNC$region <- paste0("17", resi.HBN.BNC$region )
resi.HBN.BNC <- resi.HBN.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HBN.BNC <- merge(sex.main.HBN.BNC, resi.HBN.BNC)

sex.main.all_datasets.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "BNC"))
sex.main.all_datasets.BNC <- sig.effects(sex.main.all_datasets.BNC, "BNC", "sex", "all_datasets")
sex.main.all_datasets.BNC$region <- paste0("17", sex.main.all_datasets.BNC$region)
resi.all_datasets.BNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/resi/BNC/all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.all_datasets.BNC$region <- paste0("17", resi.all_datasets.BNC$region )
resi.all_datasets.BNC <- resi.all_datasets.BNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.all_datasets.BNC <- merge(sex.main.all_datasets.BNC, resi.all_datasets.BNC)
```


```{r load WNC sex effect}
sex.main.PNC.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "WNC"))
sex.main.PNC.WNC$region <- paste0("17", sex.main.PNC.WNC$region)
sex.main.PNC.WNC <- sig.effects(sex.main.PNC.WNC, "WNC", "sex", "PNC")
resi.PNC.WNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/resi/WNC/PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.PNC.WNC$region <- paste0("17", resi.PNC.WNC$region )
resi.PNC.WNC <- resi.PNC.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.PNC.WNC <- merge(sex.main.PNC.WNC, resi.PNC.WNC)

sex.main.HCPD.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "WNC"))
sex.main.HCPD.WNC <- sig.effects(sex.main.HCPD.WNC, "WNC", "sex", "HCPD")
sex.main.HCPD.WNC$region <- paste0("17", sex.main.HCPD.WNC$region)
resi.HCPD.WNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/resi/WNC/HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.HCPD.WNC$region <- paste0("17", resi.HCPD.WNC$region )
resi.HCPD.WNC <- resi.HCPD.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HCPD.WNC <- merge(sex.main.HCPD.WNC, resi.HCPD.WNC)

sex.main.NKI.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "WNC"))
sex.main.NKI.WNC <- sig.effects(sex.main.NKI.WNC, "WNC", "sex", "NKI")
sex.main.NKI.WNC$region <- paste0("17", sex.main.NKI.WNC$region)
resi.NKI.WNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/resi/WNC/NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.NKI.WNC$region <- paste0("17", resi.NKI.WNC$region )
resi.NKI.WNC <- resi.NKI.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.NKI.WNC <- merge(sex.main.NKI.WNC, resi.NKI.WNC)

sex.main.HBN.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "WNC"))
sex.main.HBN.WNC <- sig.effects(sex.main.HBN.WNC, "WNC", "sex", "HBN")
sex.main.HBN.WNC$region <- paste0("17", sex.main.HBN.WNC$region)
resi.HBN.WNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/resi/WNC/HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.HBN.WNC$region <- paste0("17", resi.HBN.WNC$region )
resi.HBN.WNC <- resi.HBN.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HBN.WNC <- merge(sex.main.HBN.WNC, resi.HBN.WNC)

sex.main.all_datasets.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "WNC"))
sex.main.all_datasets.WNC <- sig.effects(sex.main.all_datasets.WNC, "WNC", "sex", "all_datasets")
sex.main.all_datasets.WNC$region <- paste0("17", sex.main.all_datasets.WNC$region)
resi.all_datasets.WNC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/resi/WNC/all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.all_datasets.WNC$region <- paste0("17", resi.all_datasets.WNC$region )
resi.all_datasets.WNC <- resi.all_datasets.WNC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.all_datasets.WNC <- merge(sex.main.all_datasets.WNC, resi.all_datasets.WNC)


#range(sex.main.PNC.WNC$GAM.cov.tvalue)
#range(sex.main.HCPD.WNC$GAM.cov.tvalue)
#range(sex.main.HBN.WNC$GAM.cov.tvalue)
#range(sex.main.NKI.WNC$GAM.cov.tvalue)
#range(sex.main.all_datasets.WNC$GAM.cov.tvalue)
```
## Sex effect with t-values
```{r make BNC plots across datasets, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 14}

sex.main.PNC.BNC_lh <- plot_cortex(sex.main.PNC.BNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.PNC.BNC_rh <- plot_cortex(sex.main.PNC.BNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 

sex.main.HCPD.BNC_lh <- plot_cortex(sex.main.HCPD.BNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.HCPD.BNC_rh <- plot_cortex(sex.main.HCPD.BNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 

sex.main.NKI.BNC_lh <- plot_cortex(sex.main.NKI.BNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.NKI.BNC_rh <- plot_cortex(sex.main.NKI.BNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 

sex.main.HBN.BNC_lh <- plot_cortex(sex.main.HBN.BNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.HBN.BNC_rh <- plot_cortex(sex.main.HBN.BNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
 
sex.main.all_datasets.BNC_lh <- plot_cortex(sex.main.all_datasets.BNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.BNC_rh <- plot_cortex(sex.main.all_datasets.BNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200", horizontal_layout = TRUE) 


#####
# legend
ylim1 = -2
ylim2 = 10
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.BNC, atlas = schaefer17_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)

# arrange plots 
# PNC
BNC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.BNC_lh, sex.main.PNC.BNC_rh, ncol = 2),
  top = text_grob("PNC", size = 24)
)

# HCP-D
BNC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.BNC_lh, sex.main.HCPD.BNC_rh, ncol = 2),
  top = text_grob("HCP-D", size = 24)
)

# NKI
BNC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.BNC_lh, sex.main.NKI.BNC_rh, ncol = 2),
  top = text_grob("NKI", size = 24)
)

# HBN
BNC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.BNC_lh, sex.main.HBN.BNC_rh, ncol = 2),
  top = text_grob("HBN", size = 24)
)

# pooled dataset / all datasets
BNC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.BNC_lh, sex.main.all_datasets.BNC_rh, ncol = 2),
  top = text_grob("Pooled Dataset", size = 24)
)

# blank plot for formatting
blank_space <- ggplot() + theme_void()

BNC_plots <- annotate_figure(
  plot_grid(
    blank_space,
    plot_grid(BNC_PNC, BNC_HCPD, BNC_NKI, BNC_HBN, ncol = 2),
    BNC_all,
    legend,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.29, 0.2, 0.05)
  ),
  top = text_grob("Between Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 2)
)
 
```


```{r make BNC overlapping effects plot}
# overlap plots
df_list_BNC <- list(
  PNC  = sex.main.PNC.BNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.BNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.BNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.BNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.BNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_BNC)
sex.main.overlap.BNC$signif_count <- rowSums(sex.main.overlap.BNC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.BNC$signif_count_factor <- factor(
  sex.main.overlap.BNC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.BNC <- sex.main.overlap.BNC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))
count_colors <- c(
  "0" = "white",
  "1" = "white",
  "2" = "#fcdac0",
  "3" = "#e87b96",
  "4" = "#ad2a72"
)

BNC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.BNC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
BNC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.BNC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

BNC_overlap <- annotate_figure(
  plot_grid(BNC_overlap.lh, BNC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 24)
)
# legend for overlap
count_colors_legend <- c(
  "0–1" = "white",
  "2"   = "#fcdac0",
  "3"   = "#e87b96",
  "4"   = "#ad2a72"
)

legend_df <- data.frame(
  overlap = factor(names(count_colors_legend),
                   levels = names(count_colors_legend))
)

legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(
    values = count_colors_legend,
    guide = guide_legend(
      direction = "horizontal",
      label.position = "bottom",
      override.aes = list(
        colour = "black",   # outline boxes
        size = 1
      )
    )
  ) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 18),
    legend.key.size = unit(1.3, "cm"),
    legend.position = "bottom"
  )

# Extract the horizontal legend
overlap_legend <- get_legend(legend_plot)

overlap_BNC_plots <- annotate_figure(plot_grid(BNC_overlap, overlap_legend, nrow = 2, rel_heights = c(1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))
 
 
BNC_plots_final <- plot_grid(BNC_plots, overlap_BNC_plots, blank_space, nrow = 3, rel_heights = c(1, 0.3, 0.01), rel_widths = c(1, 0.9, 1))
```



```{r make WNC plots, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 14}
# WNC
sex.main.PNC.WNC_lh <- plot_cortex(sex.main.PNC.WNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 
sex.main.PNC.WNC_rh <- plot_cortex(sex.main.PNC.WNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 

sex.main.HCPD.WNC_lh <- plot_cortex(sex.main.HCPD.WNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 
sex.main.HCPD.WNC_rh <- plot_cortex(sex.main.HCPD.WNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 

sex.main.NKI.WNC_lh <- plot_cortex(sex.main.NKI.WNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 
sex.main.NKI.WNC_rh <- plot_cortex(sex.main.NKI.WNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 

sex.main.HBN.WNC_lh <- plot_cortex(sex.main.HBN.WNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 
sex.main.HBN.WNC_rh <- plot_cortex(sex.main.HBN.WNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -11, ylim2 = 8, atlas = "schaefer17_200") 
 
sex.main.all_datasets.WNC_lh <- plot_cortex(sex.main.all_datasets.WNC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.WNC_rh <- plot_cortex(sex.main.all_datasets.WNC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200", horizontal_layout = TRUE) 

# legend
ylim1 = -11
ylim2 = 8
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.WNC, atlas = schaefer17_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)

# PNC
WNC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.WNC_lh, sex.main.PNC.WNC_rh, ncol = 2),
  top = text_grob("PNC", size = 24)
)

# HCP-D
WNC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.WNC_lh, sex.main.HCPD.WNC_rh, ncol = 2),
  top = text_grob("HCP-D", size = 24)
)

# NKI
WNC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.WNC_lh, sex.main.NKI.WNC_rh, ncol = 2),
  top = text_grob("NKI", size = 24)
)

# HBN
WNC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.WNC_lh, sex.main.HBN.WNC_rh, ncol = 2),
  top = text_grob("HBN", size = 24)
)

# All Datasets
WNC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.WNC_lh, sex.main.all_datasets.WNC_rh, ncol = 2),
  top = text_grob("Pooled Dataset", size = 24)
)


WNC_plots <- annotate_figure(
  plot_grid(
    blank_space,
    plot_grid(WNC_PNC, WNC_HCPD, WNC_NKI, WNC_HBN, ncol = 2),
    WNC_all,
    legend,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.29, 0.2, 0.05)
  ),
  top = text_grob("Within Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 2)
)
  
```

```{r make WNC overlapping effects plot}
# overlap plots
df_list_WNC <- list(
  PNC  = sex.main.PNC.WNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.WNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.WNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.WNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.WNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_WNC)
sex.main.overlap.WNC$signif_count <- rowSums(sex.main.overlap.WNC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.WNC$signif_count_factor <- factor(
  sex.main.overlap.WNC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.WNC <- sex.main.overlap.WNC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))
WNC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.WNC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
WNC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.WNC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

WNC_overlap <- annotate_figure(
  plot_grid(WNC_overlap.lh, WNC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 24)
)

overlap_WNC_plots <- annotate_figure(plot_grid(WNC_overlap, overlap_legend, nrow = 2, rel_heights = c(1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))
 

WNC_plots_final <- plot_grid(WNC_plots, overlap_WNC_plots, blank_space, nrow = 3, rel_heights = c(1, 0.3, 0.01), rel_widths = c(1, 0.9, 1))
```


```{r WNC and BNC plot, fig.width = 17, fig.height = 15}
# final plot
plot_grid(BNC_plots_final, blank_space, WNC_plots_final, ncol = 3, rel_widths = c(1, 0.1, 1))

#ggsave(paste0("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/Conferences/OHBM 2026/", "fig1_BNC_WNC.svg"), plot_grid(BNC_plots_final, blank_space, WNC_plots_final, ncol = 3, rel_widths = c(1, 0.1, 1)), height = 17, width = 15, units = "in")



```


## sex effect with RESI

```{r resi effect size reference}
library(knitr)
library(kableExtra)

effect_table <- data.frame(
  `Cohen's d` = c("[0, 0.2]", "(0.2, 0.5]", "(0.5, 0.8]", "> 0.8"),
  `RESI`      = c("[0, 0.1]", "(0.1, 0.25]", "(0.25, 0.4]", "> 0.4"),
  `Interpretation` = c(
    "No effect – small",
    "Small – medium",
    "Medium – large",
    "Large"
  )
)

effect_table %>%
  kable(
    caption = "Table 1 from RESI paper",
    booktabs = TRUE,
    align = "c"
  ) %>%
  kable_styling(full_width = FALSE)
```

```{r make BNC plots across datasets with resi, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 14}

sex.main.PNC.BNC_lh_resi <- plot_cortex(sex.main.PNC.BNC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.PNC.BNC_rh_resi <- plot_cortex(sex.main.PNC.BNC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.HCPD.BNC_lh_resi <- plot_cortex(sex.main.HCPD.BNC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.HCPD.BNC_rh_resi <- plot_cortex(sex.main.HCPD.BNC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.NKI.BNC_lh_resi <- plot_cortex(sex.main.NKI.BNC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.NKI.BNC_rh_resi <- plot_cortex(sex.main.NKI.BNC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.HBN.BNC_lh_resi <- plot_cortex(sex.main.HBN.BNC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.HBN.BNC_rh_resi <- plot_cortex(sex.main.HBN.BNC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
 
sex.main.all_datasets.BNC_lh_resi <- plot_cortex(sex.main.all_datasets.BNC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.BNC_rh_resi <- plot_cortex(sex.main.all_datasets.BNC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200", horizontal_layout = TRUE) 


#####
# legend
ylim1 = -0.1
ylim2 = 0.26
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.BNC, atlas = schaefer17_200, 
               mapping=aes(fill=RESI), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)

# arrange plots 
# PNC
BNC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.BNC_lh_resi, sex.main.PNC.BNC_rh_resi, ncol = 2),
  top = text_grob("PNC", size = 24)
)

# HCP-D
BNC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.BNC_lh_resi, sex.main.HCPD.BNC_rh_resi, ncol = 2),
  top = text_grob("HCP-D", size = 24)
)

# NKI
BNC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.BNC_lh_resi, sex.main.NKI.BNC_rh_resi, ncol = 2),
  top = text_grob("NKI", size = 24)
)

# HBN
BNC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.BNC_lh_resi, sex.main.HBN.BNC_rh_resi, ncol = 2),
  top = text_grob("HBN", size = 24)
)

# pooled dataset / all datasets
BNC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.BNC_lh_resi, sex.main.all_datasets.BNC_rh_resi, ncol = 2),
  top = text_grob("Pooled Dataset", size = 24)
)

# blank plot for formatting
blank_space <- ggplot() + theme_void()

BNC_plots <- annotate_figure(
  plot_grid(
    blank_space,
    plot_grid(BNC_PNC, BNC_HCPD, BNC_NKI, BNC_HBN, ncol = 2),
    BNC_all,
    legend,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.29, 0.2, 0.05)
  ),
  top = text_grob("Between Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 24, y = 2)
)
 
```


```{r make BNC overlapping effects plot with resi}
# overlap plots
df_list_BNC <- list(
  PNC  = sex.main.PNC.BNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.BNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.BNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.BNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.BNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_BNC)
sex.main.overlap.BNC$signif_count <- rowSums(sex.main.overlap.BNC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.BNC$signif_count_factor <- factor(
  sex.main.overlap.BNC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.BNC <- sex.main.overlap.BNC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))

count_colors <- c(
  "0" = "white",
  "1" = "white",
  "2" = "#fcdac0",
  "3" = "#e87b96",
  "4" = "#ad2a72"
)

 
BNC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.BNC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
BNC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.BNC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

BNC_overlap <- annotate_figure(
  plot_grid(BNC_overlap.lh, BNC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 24)
)
# legend for overlap
count_colors_legend <- c(
  "0–1" = "white",
  "2"   = "#fcdac0",
  "3"   = "#e87b96",
  "4"   = "#ad2a72"
)


legend_df <- data.frame(
  overlap = factor(names(count_colors_legend),
                   levels = names(count_colors_legend))
)

legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(
    values = count_colors_legend,
    guide = guide_legend(
      direction = "horizontal",
      label.position = "bottom",
      override.aes = list(
        colour = "black",   # outline boxes
        size = 1
      )
    )
  ) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 18),
    legend.key.size = unit(1.3, "cm"),
    legend.position = "bottom"
  )

# Extract the horizontal legend
overlap_legend <- get_legend(legend_plot)

overlap_BNC_plots <- annotate_figure(plot_grid(BNC_overlap, overlap_legend, nrow = 2, rel_heights = c(1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))
 
 
BNC_plots_final <- plot_grid(BNC_plots, overlap_BNC_plots, blank_space, nrow = 3, rel_heights = c(1, 0.3, 0.01), rel_widths = c(1, 0.9, 1))
```



```{r make WNC plots with resi, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 14}
# WNC
sex.main.PNC.WNC_lh_resi <- plot_cortex(sex.main.PNC.WNC, hemi = "left", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.PNC.WNC_rh_resi <- plot_cortex(sex.main.PNC.WNC, hemi = "right", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.HCPD.WNC_lh_resi <- plot_cortex(sex.main.HCPD.WNC, hemi = "left", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.HCPD.WNC_rh_resi <- plot_cortex(sex.main.HCPD.WNC, hemi = "right", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.NKI.WNC_lh_resi <- plot_cortex(sex.main.NKI.WNC, hemi = "left", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.NKI.WNC_rh_resi <- plot_cortex(sex.main.NKI.WNC, hemi = "right", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.HBN.WNC_lh_resi <- plot_cortex(sex.main.HBN.WNC, hemi = "left", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.HBN.WNC_rh_resi <- plot_cortex(sex.main.HBN.WNC, hemi = "right", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200") 
 
sex.main.all_datasets.WNC_lh_resi <- plot_cortex(sex.main.all_datasets.WNC, hemi = "left", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.WNC_rh_resi <- plot_cortex(sex.main.all_datasets.WNC, hemi = "right", measure = "RESI", ylim1 = -0.3, ylim2 = 0.26, atlas = "schaefer17_200", horizontal_layout = TRUE) 

 

# legend
ylim1 = -0.3
ylim2 = 0.26
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.WNC, atlas = schaefer17_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)

# PNC
WNC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.WNC_lh_resi, sex.main.PNC.WNC_rh_resi, ncol = 2),
  top = text_grob("PNC", size = 24)
)

# HCP-D
WNC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.WNC_lh_resi, sex.main.HCPD.WNC_rh_resi, ncol = 2),
  top = text_grob("HCP-D", size = 24)
)

# NKI
WNC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.WNC_lh_resi, sex.main.NKI.WNC_rh_resi, ncol = 2),
  top = text_grob("NKI", size = 24)
)

# HBN
WNC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.WNC_lh_resi, sex.main.HBN.WNC_rh_resi, ncol = 2),
  top = text_grob("HBN", size = 24)
)

# All Datasets
WNC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.WNC_lh_resi, sex.main.all_datasets.WNC_rh_resi, ncol = 2),
  top = text_grob("Pooled Dataset", size = 24)
)


WNC_plots <- annotate_figure(
  plot_grid(
    blank_space,
    plot_grid(WNC_PNC, WNC_HCPD, WNC_NKI, WNC_HBN, ncol = 2),
    WNC_all,
    legend,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.29, 0.2, 0.05)
  ),
  top = text_grob("Within Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 24, y = 2)
)
  
```

```{r make WNC overlapping effects plot with resi}
# overlap plots
df_list_WNC <- list(
  PNC  = sex.main.PNC.WNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.WNC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.WNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.WNC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.WNC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_WNC)
sex.main.overlap.WNC$signif_count <- rowSums(sex.main.overlap.WNC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.WNC$signif_count_factor <- factor(
  sex.main.overlap.WNC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.WNC <- sex.main.overlap.WNC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))
WNC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.WNC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
WNC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.WNC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

WNC_overlap <- annotate_figure(
  plot_grid(WNC_overlap.lh, WNC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 24)
)

overlap_WNC_plots <- annotate_figure(plot_grid(WNC_overlap, overlap_legend, nrow = 2, rel_heights = c(1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))
 

WNC_plots_final <- plot_grid(WNC_plots, overlap_WNC_plots, blank_space, nrow = 3, rel_heights = c(1, 0.3, 0.01), rel_widths = c(1, 0.9, 1))
```


```{r WNC and BNC plot with resi, fig.width = 17, fig.height = 15}
# final plot
plot_grid(BNC_plots_final, blank_space, WNC_plots_final, ncol = 3, rel_widths = c(1, 0.1, 1))

 
#ggsave(paste0("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/Conferences/OHBM 2026/", "fig1_BNC_WNC.svg"), plot_grid(BNC_plots_final, blank_space, WNC_plots_final, ncol = 3, rel_widths = c(1, 0.1, 1)), height = 17, width = 15, units = "in")

#ggsave(paste0("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/Conferences/SOBP2026/", "fig1_BNC_WNC.png"), plot_grid(BNC_plots_final, blank_space, WNC_plots_final, ncol = 3, rel_widths = c(1, 0.1, 1)), height = 17, width = 15, units = "in")

 
```

### RESI plots
```{r sanity check for RESI output}
resi.PNC.BNC.t2S <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/resi/BNC/PNC_t2S_sex_maineffects_schaefer200x17.csv")
cor.test(resi.PNC.BNC.t2S$RESI, resi.PNC.BNC$RESI)

resi.PNC.WNC.t2S <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/resi/WNC/PNC_t2S_sex_maineffects_schaefer200x17.csv")
cor.test(resi.PNC.WNC.t2S$RESI, resi.PNC.WNC$RESI)

resi.HBN.BNC.t2S <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/resi/BNC/HBN_t2S_sex_maineffects_schaefer200x17.csv")
cor.test(resi.HBN.BNC.t2S$RESI, resi.HBN.BNC$RESI)

resi.HBN.WNC.t2S <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/resi/WNC/HBN_t2S_sex_maineffects_schaefer200x17.csv")
cor.test(resi.HBN.WNC.t2S$RESI, resi.HBN.WNC$RESI)

print("RESI estimates from t2S (point-estimate only, very fast, uses the mgcv t-statistic directly) and resiPEse_Th1 (theory-based, fast CI, no bootstrap) methods are highly correlated")
```


## maybe look at network segregation and integration
1.1: supplementary figure - GBC?

```{r load GBC sex effect}
sex.main.PNC.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "GBC"))
sex.main.PNC.GBC$region <- paste0("17", sex.main.PNC.GBC$region)
sex.main.PNC.GBC <- sig.effects(sex.main.PNC.GBC, "GBC", "sex", "PNC")
resi.PNC.GBC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/resi/GBC/PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.PNC.GBC$region <- paste0("17", resi.PNC.GBC$region )
resi.PNC.GBC <- resi.PNC.GBC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.PNC.GBC <- merge(sex.main.PNC.GBC, resi.PNC.GBC)

sex.main.HCPD.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "GBC"))
sex.main.HCPD.GBC <- sig.effects(sex.main.HCPD.GBC, "GBC", "sex", "HCPD")
sex.main.HCPD.GBC$region <- paste0("17", sex.main.HCPD.GBC$region)
resi.HCPD.GBC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/resi/GBC/HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.HCPD.GBC$region <- paste0("17", resi.HCPD.GBC$region )
resi.HCPD.GBC <- resi.HCPD.GBC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HCPD.GBC <- merge(sex.main.HCPD.GBC, resi.HCPD.GBC)

sex.main.NKI.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "GBC"))
sex.main.NKI.GBC <- sig.effects(sex.main.NKI.GBC, "GBC", "sex", "NKI")
sex.main.NKI.GBC$region <- paste0("17", sex.main.NKI.GBC$region)
resi.NKI.GBC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/resi/GBC/NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.NKI.GBC$region <- paste0("17", resi.NKI.GBC$region )
resi.NKI.GBC <- resi.NKI.GBC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.NKI.GBC <- merge(sex.main.NKI.GBC, resi.NKI.GBC)

sex.main.HBN.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "GBC"))
sex.main.HBN.GBC <- sig.effects(sex.main.HBN.GBC, "GBC", "sex", "HBN")
sex.main.HBN.GBC$region <- paste0("17", sex.main.HBN.GBC$region)
resi.HBN.GBC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/resi/GBC/HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.HBN.GBC$region <- paste0("17", resi.HBN.GBC$region )
resi.HBN.GBC <- resi.HBN.GBC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.HBN.GBC <- merge(sex.main.HBN.GBC, resi.HBN.GBC)

sex.main.all_datasets.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "GBC"))
sex.main.all_datasets.GBC <- sig.effects(sex.main.all_datasets.GBC, "GBC", "sex", "all_datasets")
sex.main.all_datasets.GBC$region <- paste0("17", sex.main.all_datasets.GBC$region)
resi.all_datasets.GBC <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/resi/GBC/all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv")
resi.all_datasets.GBC$region <- paste0("17", resi.all_datasets.GBC$region )
resi.all_datasets.GBC <- resi.all_datasets.GBC %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
sex.main.all_datasets.GBC <- merge(sex.main.all_datasets.GBC, resi.all_datasets.GBC)


#range(sex.main.PNC.GBC$GAM.cov.tvalue)
#range(sex.main.HCPD.GBC$GAM.cov.tvalue)
#range(sex.main.HBN.GBC$GAM.cov.tvalue)
#range(sex.main.NKI.GBC$GAM.cov.tvalue)
#range(sex.main.all_datasets.GBC$GAM.cov.tvalue)
```

## Functional Connectivity Strength - sex effect with t-value
```{r make GBC plots across datasets, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 14}

sex.main.PNC.GBC_lh <- plot_cortex(sex.main.PNC.GBC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.PNC.GBC_rh <- plot_cortex(sex.main.PNC.GBC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 

sex.main.HCPD.GBC_lh <- plot_cortex(sex.main.HCPD.GBC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.HCPD.GBC_rh <- plot_cortex(sex.main.HCPD.GBC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 

sex.main.NKI.GBC_lh <- plot_cortex(sex.main.NKI.GBC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.NKI.GBC_rh <- plot_cortex(sex.main.NKI.GBC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 

sex.main.HBN.GBC_lh <- plot_cortex(sex.main.HBN.GBC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
sex.main.HBN.GBC_rh <- plot_cortex(sex.main.HBN.GBC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200") 
 
sex.main.all_datasets.GBC_lh <- plot_cortex(sex.main.all_datasets.GBC, hemi = "left", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.GBC_rh <- plot_cortex(sex.main.all_datasets.GBC, hemi = "right", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2 = 10, atlas = "schaefer17_200", horizontal_layout = TRUE) 


#####
# legend
ylim1 = -2
ylim2 = 10
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.GBC, atlas = schaefer17_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)

# arrange plots 
# PNC
GBC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.GBC_lh, sex.main.PNC.GBC_rh, ncol = 2),
  top = text_grob("PNC", size = 24)
)

# HCP-D
GBC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.GBC_lh, sex.main.HCPD.GBC_rh, ncol = 2),
  top = text_grob("HCP-D", size = 24)
)

# NKI
GBC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.GBC_lh, sex.main.NKI.GBC_rh, ncol = 2),
  top = text_grob("NKI", size = 24)
)

# HBN
GBC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.GBC_lh, sex.main.HBN.GBC_rh, ncol = 2),
  top = text_grob("HBN", size = 24)
)

# pooled dataset / all datasets
GBC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.GBC_lh, sex.main.all_datasets.GBC_rh, ncol = 2),
  top = text_grob("Pooled Dataset", size = 24)
)

# blank plot for formatting
blank_space <- ggplot() + theme_void()

GBC_plots <- annotate_figure(
  plot_grid(
    blank_space,
    plot_grid(GBC_PNC, GBC_HCPD, GBC_NKI, GBC_HBN, ncol = 2),
    GBC_all,
    legend,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.29, 0.2, 0.05)
  ),
  top = text_grob("Functional Connectivity Strength", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 2)
)
 
```


```{r make GBC overlapping effects plot, fig.height = 15, fig.width = 10}
# overlap plots
df_list_GBC <- list(
  PNC  = sex.main.PNC.GBC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.GBC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.GBC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.GBC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.GBC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_GBC)
sex.main.overlap.GBC$signif_count <- rowSums(sex.main.overlap.GBC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.GBC$signif_count_factor <- factor(
  sex.main.overlap.GBC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.GBC <- sex.main.overlap.GBC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))

count_colors <- c(
  "0" = "white",
  "1" = "white",
  "2" = "#fcdac0",
  "3" = "#e87b96",
  "4" = "#ad2a72"
)

GBC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.GBC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
GBC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.GBC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

GBC_overlap <- annotate_figure(
  plot_grid(GBC_overlap.lh, GBC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 24)
)
# legend for overlap
count_colors_legend <- c(
  "0–1" = "white",
  "2"   = "#fcdac0",
  "3"   = "#e87b96",
  "4"   = "#ad2a72"
)


legend_df <- data.frame(
  overlap = factor(names(count_colors_legend),
                   levels = names(count_colors_legend))
)

legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(
    values = count_colors_legend,
    guide = guide_legend(
      direction = "horizontal",
      label.position = "bottom",
      override.aes = list(
        colour = "black",   # outline boxes
        size = 1
      )
    )
  ) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 18),
    legend.key.size = unit(1.3, "cm"),
    legend.position = "bottom"
  )

# Extract the horizontal legend
overlap_legend <- get_legend(legend_plot)

overlap_GBC_plots <- annotate_figure(plot_grid(GBC_overlap, overlap_legend, nrow = 2, rel_heights = c(1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))
 
 
GBC_plots_final <- plot_grid(GBC_plots, overlap_GBC_plots, blank_space, nrow = 3, rel_heights = c(1, 0.3, 0.01), rel_widths = c(1, 0.9, 1))

GBC_plots_final
```


## Functional Connectivity Strength - sex effect with RESI
```{r make GBC plots across datasets with resi, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 14}

sex.main.PNC.GBC_lh_resi <- plot_cortex(sex.main.PNC.GBC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.PNC.GBC_rh_resi <- plot_cortex(sex.main.PNC.GBC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.HCPD.GBC_lh_resi <- plot_cortex(sex.main.HCPD.GBC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.HCPD.GBC_rh_resi <- plot_cortex(sex.main.HCPD.GBC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.NKI.GBC_lh_resi <- plot_cortex(sex.main.NKI.GBC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.NKI.GBC_rh_resi <- plot_cortex(sex.main.NKI.GBC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 

sex.main.HBN.GBC_lh_resi <- plot_cortex(sex.main.HBN.GBC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
sex.main.HBN.GBC_rh_resi <- plot_cortex(sex.main.HBN.GBC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200") 
 
sex.main.all_datasets.GBC_lh_resi <- plot_cortex(sex.main.all_datasets.GBC, hemi = "left", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200", horizontal_layout = TRUE) 
sex.main.all_datasets.GBC_rh_resi <- plot_cortex(sex.main.all_datasets.GBC, hemi = "right", measure = "RESI", ylim1 = -0.1, ylim2 = 0.26, atlas = "schaefer17_200", horizontal_layout = TRUE) 


#####
# legend
ylim1 = -0.1
ylim2 = 0.26
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.GBC, atlas = schaefer17_200, 
               mapping=aes(fill=RESI), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)

# arrange plots 
# PNC
GBC_PNC <- annotate_figure(
  plot_grid(sex.main.PNC.GBC_lh_resi, sex.main.PNC.GBC_rh_resi, ncol = 2),
  top = text_grob("PNC", size = 24)
)

# HCP-D
GBC_HCPD <- annotate_figure(
  plot_grid(sex.main.HCPD.GBC_lh_resi, sex.main.HCPD.GBC_rh_resi, ncol = 2),
  top = text_grob("HCP-D", size = 24)
)

# NKI
GBC_NKI <- annotate_figure(
  plot_grid(sex.main.NKI.GBC_lh_resi, sex.main.NKI.GBC_rh_resi, ncol = 2),
  top = text_grob("NKI", size = 24)
)

# HBN
GBC_HBN <- annotate_figure(
  plot_grid(sex.main.HBN.GBC_lh_resi, sex.main.HBN.GBC_rh_resi, ncol = 2),
  top = text_grob("HBN", size = 24)
)

# pooled dataset / all datasets
GBC_all <- annotate_figure(
  plot_grid(sex.main.all_datasets.GBC_lh_resi, sex.main.all_datasets.GBC_rh_resi, ncol = 2),
  top = text_grob("Pooled Dataset", size = 24)
)

# blank plot for formatting
blank_space <- ggplot() + theme_void()

GBC_plots <- annotate_figure(
  plot_grid(
    blank_space,
    plot_grid(GBC_PNC, GBC_HCPD, GBC_NKI, GBC_HBN, ncol = 2),
    GBC_all,
    legend,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.29, 0.2, 0.05)
  ),
  top = text_grob("Functional Connectivity Strength", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (RESI)", size = 24, y = 2)
)
 
```


```{r make GBC overlapping effects plot with resi, fig.height = 15, fig.width = 10}
# overlap plots
df_list_GBC <- list(
  PNC  = sex.main.PNC.GBC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.GBC[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.GBC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.GBC[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.GBC <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_GBC)
sex.main.overlap.GBC$signif_count <- rowSums(sex.main.overlap.GBC[, -1] < 0.05, na.rm = TRUE)
sex.main.overlap.GBC$signif_count_factor <- factor(
  sex.main.overlap.GBC$signif_count,
  levels = 0:4,
  labels = c("0", "1", "2", "3", "4")
)
sex.main.overlap.GBC <- sex.main.overlap.GBC %>% mutate(signif_greater_than_one = ifelse(signif_count > 1, "1", "0"))

count_colors <- c(
  "0" = "white",
  "1" = "white",
  "2" = "#fcdac0",
  "3" = "#e87b96",
  "4" = "#ad2a72"
)



GBC_overlap.lh <- plot_cortex_overlap(sex.main.overlap.GBC, hemi = "left", atlas = "schaefer17_200", horizontal_layout = T)
GBC_overlap.rh <- plot_cortex_overlap(sex.main.overlap.GBC, hemi = "right", atlas = "schaefer17_200", horizontal_layout = T)

GBC_overlap <- annotate_figure(
  plot_grid(GBC_overlap.lh, GBC_overlap.rh, ncol = 2),
  top = text_grob("Overlap of Significant Effects Across Datasets", size = 24)
)
# legend for overlap
count_colors_legend <- c(
  "0–1" = "white",
  "2"   = "#fcdac0",
  "3"   = "#e87b96",
  "4"   = "#ad2a72"
)

legend_df <- data.frame(
  overlap = factor(names(count_colors_legend),
                   levels = names(count_colors_legend))
)

legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(
    values = count_colors_legend,
    guide = guide_legend(
      direction = "horizontal",
      label.position = "bottom",
      override.aes = list(
        colour = "black",   # outline boxes
        size = 1
      )
    )
  ) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 18),
    legend.key.size = unit(1.3, "cm"),
    legend.position = "bottom"
  )

# Extract the horizontal legend
overlap_legend <- get_legend(legend_plot)

overlap_GBC_plots <- annotate_figure(plot_grid(GBC_overlap, overlap_legend, nrow = 2, rel_heights = c(1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))
 
 
GBC_plots_final <- plot_grid(GBC_plots, overlap_GBC_plots, blank_space, nrow = 3, rel_heights = c(1, 0.3, 0.01), rel_widths = c(1, 0.9, 1))

GBC_plots_final
```

1.2: supplement figure - null correlations with S-A axis?
1.3: age-by-sex - see below

# 2. parcels showing sex differences are involved in X cognitive functions via neurosynth -- may not include in final
Which Neurosynth terms show significant functional activation (z > 1.64) within the parcels where females have higher WNC? What about where males have higher BNC?
```{r load neurosynth}
# code adapted from Val Sydnor's https://github.com/PennLINC/thalamocortical_development/blob/main/results/developmental_effects/thalamocortical_connectivity_development.Rmd
#Neurosynth z-score maps generated by nimare. Nimare uses multilevel kernel density analysis- Chi-square analysis + FDR-correction to use the same procedure as Neurosynth
neurosynth.terms <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/input/neurosynth_annotations/schaefer200/schaefer200x17_neurosynth_125terms.csv") %>% select(-regionID) %>% rename(region = label)
neurosynth.termlist <- names(neurosynth.terms)[-1] #list of terms  
```


We examined the 10 most positively correlated Neurosynth terms with the BNC sex difference map, focusing on positive correlations because they indicate cognitive domains whose spatial patterns overlap with parcels showing greater BNC in males relative to females. In contrast, we examined the ten most negatively correlated Neurosynth terms with the WNC sex difference map, focusing on negatively correlations because they indicate cognitive domains whose spatial patterns overlap with parcels showing greater WNC in females relative to males.
```{r overlapping effects neurosynth decoding of sex differences, fig.height = 7, fig.width = 7}
# identify overlapping significant effects across datasets (2 or more datasets), and get avg t-value for each of those parcels
BNC_sexeffect_overlap <- identify_sexeffect_overlap_tvalues("BNC") %>% mutate(significant_status = ifelse(signif_2plus == 1, "Sig", "Nonsig"))
WNC_sexeffect_overlap <- identify_sexeffect_overlap_tvalues("WNC") %>% mutate(significant_status = ifelse(signif_2plus == 1, "Sig", "Nonsig"))
 
# fdr correction of neurosynth terms correlations with BNC and WNC sex effect maps
BNC_neurosynth <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/spin_test/neurosynth/BNC_neurosynth_spin_test_results_overlap.csv")
BNC_neurosynth$pvalue.fdr <- p.adjust(BNC_neurosynth$p_spin, method = c("fdr")) 
BNC_neurosynth_fdr <- BNC_neurosynth %>% filter(pvalue.fdr < 0.05)  
BNC_neurosynth_fdr %>% arrange(pvalue.fdr)
BNC_neurosynth_top10 <- rbind(slice_max(BNC_neurosynth_fdr, order_by = term.correlation, n = 10)) # 10 most positively correlated neurosynth terms with the sex diff map. Looking at positive correlations because they reflect cognitive terms that spatially align with regions showing higher BNC in males (male > female).
BNC_neurosynth_top10$term <- tools::toTitleCase(gsub("_", " ", BNC_neurosynth_top10$term))

WNC_neurosynth <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/spin_test/neurosynth/WNC_neurosynth_spin_test_results_overlap.csv")
WNC_neurosynth$pvalue.fdr <- p.adjust(WNC_neurosynth$p_spin, method = c("fdr")) 
WNC_neurosynth_fdr <- WNC_neurosynth %>% filter(pvalue.fdr < 0.05)  
WNC_neurosynth_top10 <- rbind(slice_min(WNC_neurosynth_fdr, order_by = term.correlation, n = 10)) # 10 most negatively correlated neurosynth terms with the sex diff map. Looking at NEGATIVE correlations because they reflect cognitive terms that spatially align with regions showing higher WNC in females (female > male).
WNC_neurosynth_top10$term <- tools::toTitleCase(gsub("_", " ", WNC_neurosynth_top10$term))
WNC_neurosynth_top10$term <- gsub("Autobiographical Memory", "Autobio. Memory", WNC_neurosynth_top10$term)

 
```

```{r overlap tvalue plots, fig.height = 6, fig.width = 14}
# plot avg t-value 
BNC_overlap_tvalue_plot_lh <- plot_cortex(BNC_sexeffect_overlap, hemi = "left", measure = "mean_t_sig2", ylim1 = -0.5, ylim2 = 5.5, atlas = "schaefer17_200") 
BNC_overlap_tvalue_plot_rh <- plot_cortex(BNC_sexeffect_overlap, hemi = "right", measure = "mean_t_sig2", ylim1 = -0.5, ylim2 = 5.5, atlas = "schaefer17_200") 
 
WNC_overlap_tvalue_plot_lh <- plot_cortex(WNC_sexeffect_overlap, hemi = "left", measure = "mean_t_sig2", ylim1 = -6, ylim2 = 5, atlas = "schaefer17_200") 
WNC_overlap_tvalue_plot_rh <- plot_cortex(WNC_sexeffect_overlap, hemi = "right", measure = "mean_t_sig2", ylim1 = -6, ylim2 = 5, atlas = "schaefer17_200") 
  
# legend for BNC overlap
ylim1 = -0.5
ylim2 = 5.5
p_BNC <- ggplot() + 
    geom_brain(data = BNC_sexeffect_overlap, atlas = schaefer17_200, 
               mapping=aes(fill=mean_t_sig2), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend_BNC_overlap <- get_legend(p_BNC)

# legend for WNC overlap
ylim1 = -6
ylim2 = 5
p_WNC <- ggplot() + 
    geom_brain(data = WNC_sexeffect_overlap, atlas = schaefer17_200, 
               mapping=aes(fill=mean_t_sig2), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend_WNC_overlap <- get_legend(p_WNC)


# arrange plots 
BNC_overlap_tvalue_plot <- annotate_figure(
  plot_grid(
    blank_space,
    annotate_figure(plot_grid(BNC_overlap_tvalue_plot_lh, BNC_overlap_tvalue_plot_rh, ncol = 2), 
                    top = text_grob("Overlap of Significant Effects Across Datasets \n (Average T-value)", size = 20)),
    blank_space,
    legend_BNC_overlap,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.1, 0.1, 0.1)
  ),
  top = text_grob("Between Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 1)
)



WNC_overlap_tvalue_plot <- annotate_figure(
  plot_grid(
    blank_space,
    annotate_figure(plot_grid(WNC_overlap_tvalue_plot_lh, WNC_overlap_tvalue_plot_rh, ncol = 2), 
                    top = text_grob("Overlap of Significant Effects Across Datasets \n (Average T-value)", size = 20)),
    blank_space,
    legend_WNC_overlap,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.1, 0.1, 0.1)
  ),
  top = text_grob("Within Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 1)
)
 
```

```{r overlap neurosynth plots}

 
# plot neurosynth terms
BNC_neurosynth_plot <- ggplot(BNC_neurosynth_top10, 
       aes(x = term.correlation, 
           y = reorder(term, abs(term.correlation)))) +
  geom_segment(aes(x = 0, xend = term.correlation, 
                   yend = reorder(term, abs(term.correlation))),
               color = "gray80", linewidth = 0.9) +
  geom_point(aes(color = term.correlation), size = 12) +
  scale_color_gradient(low = "#ad2a72", high = "#fcdac0") +
  scale_x_continuous(limits = c(0, 0.6), breaks = seq(0, 0.6, by = 0.2),
                     expand = c(0, 0)) +
  scale_y_discrete(position = "left") +   
  labs(
    x = "Spatial Correlation",
    y = "Neurosynth Term"
  ) +
  theme_classic() +
  coord_cartesian(clip = "off") + 
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_text(size = 20, color = "black"),
    axis.title.x = element_text(size = 20, color = "black"),
    axis.text.y = element_text(size = 20, color = "black"),
    axis.text.x = element_text(size = 20, color = "black"),
    plot.margin = unit(c(0, 1, 0, 0), "cm")    
  )

WNC_neurosynth_plot <- ggplot(WNC_neurosynth_top10, 
       aes(x = term.correlation, 
           y = reorder(term, abs(term.correlation)))) +
  geom_segment(aes(x = 0, xend = term.correlation, 
                   yend = reorder(term, -abs(term.correlation))),
               color = "gray80", linewidth = 0.9) +
  geom_point(aes(color = term.correlation), size = 12) +
  scale_color_gradient(low = "#fcdac0", high = "#ad2a72") +
  scale_x_continuous(limits = c(-0.6, 0), breaks = seq(-0.6, 0, by = 0.2), 
                     expand = c(0, 0)) +
  scale_y_discrete(position = "right") +
  labs(
    x = "Spatial Correlation") +
  theme_classic() +
  coord_cartesian(clip = "off") + 
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 20, color = "black"),
    axis.text.y = element_text(size = 20, color = "black"),
    axis.text.x = element_text(size = 20, color = "black"),
    plot.margin = unit(c(0, 0, 0, 1), "cm")
  )


```

## option 1: overlap between datasets (average t-value across datasets is spun against neurosynth term maps)
```{r overlap neurosynth figure, fig.height = 12, fig.width = 12}
neurosynth_plots_row1 <- plot_grid(BNC_overlap_tvalue_plot, WNC_overlap_tvalue_plot, ncol = 2)
neurosynth_plots_row2 <- plot_grid(blank_space, blank_space, ncol = 2)
neurosynth_plots_row3 <- BNC_neurosynth_plot + blank_space + WNC_neurosynth_plot +
  plot_layout(widths = c(1, 0.2,  1))  

plot_grid(neurosynth_plots_row1, neurosynth_plots_row2, neurosynth_plots_row3, nrow = 3, rel_heights = c(1, 0.1, 1))


#ggsave(paste0("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/Conferences/OHBM 2026/", "fig2_neurosynth.svg"), plot_grid(neurosynth_plots_row1, neurosynth_plots_row2, neurosynth_plots_row3, nrow = 3, rel_heights = c(1, 0.1, 1)), height = 12, width = 12, units = "in")
```
 
 
```{r pooled datasets neurosynth decoding of sex differences, fig.height = 7, fig.width = 7}

# fdr correction of neurosynth terms correlations with BNC and WNC sex effect maps
BNC_neurosynth_pooled <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/spin_test/neurosynth/BNC_neurosynth_spin_test_results_pooled.csv")
BNC_neurosynth_pooled$pvalue.fdr <- p.adjust(BNC_neurosynth_pooled$p_spin, method = c("fdr")) 
BNC_neurosynth_pooled_fdr <- BNC_neurosynth_pooled %>% filter(pvalue.fdr < 0.05)  
BNC_neurosynth_pooled_top10 <- rbind(slice_max(BNC_neurosynth_pooled_fdr, order_by = term.correlation, n = 10)) # 10 most positively correlated neurosynth terms with the sex diff map. Looking at positive correlations because they reflect cognitive terms that spatially align with regions showing higher BNC in males (male > female).
BNC_neurosynth_pooled_top10$term <- tools::toTitleCase(gsub("_", " ", BNC_neurosynth_pooled_top10$term))
BNC_neurosynth_pooled_top10$term <- gsub("Autobiographical Memory", "Autobio. Memory", BNC_neurosynth_pooled_top10$term)
BNC_neurosynth_pooled_top10 <- BNC_neurosynth_pooled_top10 %>% filter(term.correlation > 0)

WNC_neurosynth_pooled <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/spin_test/neurosynth/WNC_neurosynth_spin_test_results_pooled.csv")
WNC_neurosynth_pooled$pvalue.fdr <- p.adjust(WNC_neurosynth_pooled$p_spin, method = c("fdr")) 
WNC_neurosynth_pooled_fdr <- WNC_neurosynth_pooled %>% filter(pvalue.fdr < 0.05)  
WNC_neurosynth_pooled_top10 <- rbind(slice_min(WNC_neurosynth_pooled_fdr, order_by = term.correlation, n = 10)) # 10 most negatively correlated neurosynth terms with the sex diff map. Looking at NEGATIVE correlations because they reflect cognitive terms that spatially align with regions showing higher WNC in females (female > male).
WNC_neurosynth_pooled_top10$term <- tools::toTitleCase(gsub("_", " ", WNC_neurosynth_pooled_top10$term))
WNC_neurosynth_pooled_top10$term <- gsub("Autobiographical Memory", "Autobio. Memory", WNC_neurosynth_pooled_top10$term)
```

```{r pooled tvalue}
# plot avg t-value 
BNC_pooled_tvalue_plot_lh <- plot_cortex(sex.main.all_datasets.BNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -0.5, ylim2 = 11, atlas = "schaefer17_200") 
BNC_pooled_tvalue_plot_rh <- plot_cortex(sex.main.all_datasets.BNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -0.5, ylim2 = 11, atlas = "schaefer17_200") 
 
WNC_pooled_tvalue_plot_lh <- plot_cortex(sex.main.all_datasets.WNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -13, ylim2 = 10, atlas = "schaefer17_200") 
WNC_pooled_tvalue_plot_rh <- plot_cortex(sex.main.all_datasets.WNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -13, ylim2 = 10, atlas = "schaefer17_200") 
  
# legend for BNC pooled
ylim1 = -0.5
ylim2 = 11
p_BNC <- ggplot() + 
    geom_brain(data = sex.main.all_datasets.BNC, atlas = schaefer17_200, 
               mapping=aes(fill=cov_sig_effect), 
               show.legend=TRUE) +
         scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 

    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend_BNC_pooled <- get_legend(p_BNC)

# legend for WNC pooled
ylim1 = -13
ylim2 = 10
p_WNC <- ggplot() + 
    geom_brain(data = sex.main.all_datasets.WNC, atlas = schaefer17_200, 
               mapping=aes(fill=cov_sig_effect), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend_WNC_pooled <- get_legend(p_WNC)


# arrange plots 
BNC_pooled_tvalue_plot <- annotate_figure(
  plot_grid(
    blank_space,
    annotate_figure(plot_grid(BNC_pooled_tvalue_plot_lh, BNC_pooled_tvalue_plot_rh, ncol = 2), 
                    top = text_grob("Pooled Dataset", size = 20)),
    blank_space,
    legend_BNC_pooled,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.1, 0.1, 0.1)
  ),
  top = text_grob("Between Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 1)
)



WNC_pooled_tvalue_plot <- annotate_figure(
  plot_grid(
    blank_space,
    annotate_figure(plot_grid(WNC_pooled_tvalue_plot_lh, WNC_pooled_tvalue_plot_rh, ncol = 2), 
                    top = text_grob("Pooled Dataset", size = 20)),
    blank_space,
    legend_WNC_pooled,
    blank_space,
    nrow = 5,
    rel_heights = c(0.05, 1, 0.1, 0.1, 0.1)
  ),
  top = text_grob("Within Network Connectivity", size = 24, face = "bold"),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 1)
)
 
```


```{r pooled neurosynth plots}
# plot neurosynth terms
BNC_neurosynth_pooled_plot <- ggplot(BNC_neurosynth_pooled_top10, 
       aes(x = term.correlation, 
           y = reorder(term, abs(term.correlation)))) +
  geom_segment(aes(x = 0, xend = term.correlation, 
                   yend = reorder(term, abs(term.correlation))),
               color = "gray80", linewidth = 0.9) +
  geom_point(aes(color = term.correlation), size = 12) +
  scale_color_gradient(low = "#fcdac0", high = "#ad2a72") +
  scale_x_continuous(limits = c(0, 0.6), breaks = seq(0, 0.6, by = 0.2),
                     expand = c(0, 0)) +
  scale_y_discrete(position = "left") +   
  labs(
    x = "Spatial Correlation",
    y = "Neurosynth Term"
  ) +
  theme_classic() +
  coord_cartesian(clip = "off") + 
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_text(size = 20, color = "black"),
    axis.title.x = element_text(size = 20, color = "black"),
    axis.text.y = element_text(size = 20, color = "black"),
    axis.text.x = element_text(size = 20, color = "black"),
    plot.margin = unit(c(0, 1, 0, 0), "cm")    
  )

WNC_neurosynth_pooled_plot <- ggplot(WNC_neurosynth_pooled_top10, 
       aes(x = term.correlation, 
           y = reorder(term, abs(term.correlation)))) +
  geom_segment(aes(x = 0, xend = term.correlation, 
                   yend = reorder(term, -abs(term.correlation))),
               color = "gray80", linewidth = 0.9) +
  geom_point(aes(color = term.correlation), size = 12) +
  scale_color_gradient(low = "#ad2a72", high = "#fcdac0") +
  scale_x_continuous(limits = c(-0.6, 0), breaks = seq(-0.6, 0, by = 0.2), 
                     expand = c(0, 0)) +
  scale_y_discrete(position = "right") +
  labs(
    x = "Spatial Correlation") +
  theme_classic() +
  coord_cartesian(clip = "off") + 
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 20, color = "black"),
    axis.text.y = element_text(size = 20, color = "black"),
    axis.text.x = element_text(size = 20, color = "black"),
    plot.margin = unit(c(0, 0, 0, 1), "cm")
  )
```

## option 2: pooled between datasets (average t-value across datasets is spun against neurosynth term maps)
```{r pooled neurosynth figure, fig.height = 12, fig.width = 12}
neurosynth_plots_row1 <- plot_grid(BNC_pooled_tvalue_plot, WNC_pooled_tvalue_plot, ncol = 2)
neurosynth_plots_row2 <- plot_grid(blank_space, blank_space, ncol = 2)
neurosynth_plots_row3 <- BNC_neurosynth_pooled_plot + blank_space + WNC_neurosynth_pooled_plot +
  plot_layout(widths = c(1, 0.2,  1))  

plot_grid(neurosynth_plots_row1, neurosynth_plots_row2, neurosynth_plots_row3, nrow = 3, rel_heights = c(1, 0.1, 1))
```
 

# 3. Sex differences in network-level connectivity
Given that males exhibit greater between-network connectivity across nearly all brain regions, and females exhibit greater within-network connectivity in select regions that appear to be a part of the DMN, we examined sex differences in connectivity between and within networks. 
```{r load networkpair sex for 17 networks}
num_networks = 17
sex.main.PNC.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "PNC", "networkpair", num_networks))
sex.main.HCPD.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HCPD", "networkpair", num_networks))
sex.main.NKI.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "NKI", "networkpair", num_networks))
sex.main.HBN.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HBN", "networkpair", num_networks))
sex.main.all_datasets.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "all_datasets", "networkpair", num_networks))


# make two new columns identifying network 1 and network 2
sex.main.PNC.networkpair.17<- sex.main.PNC.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HCPD.networkpair.17<- sex.main.HCPD.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.NKI.networkpair.17<- sex.main.NKI.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HBN.networkpair.17<- sex.main.HBN.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.all_datasets.networkpair.17<- sex.main.all_datasets.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))

# fdr correction on non-duplicated pairs only and sorts pairs
sex.main.PNC.networkpair.17<- prep_networkpair_df(sex.main.PNC.networkpair.17, "networkpair", "sex", "PNC")
sex.main.HCPD.networkpair.17<- prep_networkpair_df(sex.main.HCPD.networkpair.17,  "networkpair", "sex", "HCPD")
sex.main.NKI.networkpair.17<- prep_networkpair_df(sex.main.NKI.networkpair.17,  "networkpair", "sex", "NKI")
sex.main.HBN.networkpair.17<- prep_networkpair_df(sex.main.HBN.networkpair.17,  "networkpair", "sex", "HBN")
sex.main.all_datasets.networkpair.17<- prep_networkpair_df(sex.main.all_datasets.networkpair.17,  "networkpair", "sex", "All datasets")

resi.PNC.networkpair <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/resi/networkpair/PNC_resiPEse_Th1_sex_maineffects_schaefer200x17.csv") %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.HCPD.networkpair <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/resi/networkpair/HCPD_resiPEse_Th1_sex_maineffects_schaefer200x17.csv") %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.NKI.networkpair <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/resi/networkpair/NKI_resiPEse_Th1_sex_maineffects_schaefer200x17.csv") %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.HBN.networkpair <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/resi/networkpair/HBN_resiPEse_Th1_sex_maineffects_schaefer200x17.csv") %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)
resi.all_datasets.networkpair <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/resi/networkpair/all_datasets_resiPEse_Th1_sex_maineffects_schaefer200x17.csv") %>% rename(RESI = RESI_Xinyu) %>% select(region, RESI)

sex.main.PNC.networkpair.17 <- merge(sex.main.PNC.networkpair.17, resi.PNC.networkpair)
sex.main.NKI.networkpair.17 <- merge(sex.main.NKI.networkpair.17, resi.NKI.networkpair)
sex.main.HCPD.networkpair.17 <- merge(sex.main.HCPD.networkpair.17, resi.HCPD.networkpair)
sex.main.HBN.networkpair.17 <- merge(sex.main.HBN.networkpair.17, resi.HBN.networkpair)
sex.main.all_datasets.networkpair.17 <- merge(sex.main.all_datasets.networkpair.17, resi.all_datasets.networkpair)


#range(sex.main.PNC.networkpair.17$GAM.cov.tvalue)
#range(sex.main.HCPD.networkpair.17$GAM.cov.tvalue)
#range(sex.main.NKI.networkpair.17$GAM.cov.tvalue)
#range(sex.main.HBN.networkpair.17$GAM.cov.tvalue)
#range(sex.main.all_datasets.networkpair.17$GAM.cov.tvalue)
 
```

## sex effect with t-values
```{r plot networkpair sex for 17 networks, fig.width = 25, fig.height = 15}

# plot each dataset
networkpair_PNC <- annotate_figure(
  make_networkpair17_plot(sex.main.PNC.networkpair.17, dataset = "PNC", ylim1 = -10, ylim2 = 10, fontsize = 12, fontsize_label = 4, measure = "GAM.cov.tvalue"))

networkpair_HCPD <- annotate_figure(
  make_networkpair17_plot(sex.main.HCPD.networkpair.17, dataset = "HCP-D", ylim1 = -10, ylim2 = 10, fontsize = 12, fontsize_label = 4, measure = "GAM.cov.tvalue"))

networkpair_NKI <- annotate_figure(
  make_networkpair17_plot(sex.main.NKI.networkpair.17, dataset = "NKI", ylim1 = -10, ylim2 = 10, fontsize = 12, fontsize_label = 4, measure = "GAM.cov.tvalue"))

networkpair_HBN <- annotate_figure(
  make_networkpair17_plot(sex.main.HBN.networkpair.17, dataset = "HBN", ylim1 = -10, ylim2 = 10, fontsize = 12, fontsize_label = 4, measure = "GAM.cov.tvalue"))

networkpair_all_datasets_plot <- annotate_figure(
  make_networkpair17_plot(sex.main.all_datasets.networkpair.17, dataset = "Pooled Dataset", ylim1 = -10, ylim2 = 10, fontsize = 12, fontsize_label = 4, measure = "GAM.cov.tvalue"))

combined_networkpair_temp_plots <- plot_grid(
  networkpair_PNC,
  networkpair_HCPD,
  networkpair_NKI,
  networkpair_HBN,
  ncol = 2
)


# legend
ylim1 = -10
ylim2 = 10
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.BNC, atlas = schaefer17_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(3, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)
 
```

```{r plot networkpair overlap}

# overlap of datasets:
df_list_networkpair <- list(
  PNC  = sex.main.PNC.networkpair.17[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.networkpair.17[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.networkpair.17[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.networkpair.17[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.networkpair <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_networkpair)

sex.main.overlap.networkpair <- sex.main.overlap.networkpair %>%
  mutate(
    signif_count = rowSums(across(starts_with("p_")) < 0.05, na.rm = TRUE),
    signif_count_factor = factor(
      signif_count,
      levels = 0:4,
      labels = c("0", "1", "2", "3", "4")
    ),
    signif_greater_than_one = ifelse(signif_count > 1, "1", "0")
  )

sex.main.overlap.networkpair <- sex.main.overlap.networkpair %>%
  mutate(
    network1 = str_extract(region, "^[[:alpha:]]+"),
    network2 = str_extract(region, "(?<=_).*")
  )


# overlap legend
legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(values = count_colors_legend,
                    guide = guide_legend(direction = "horizontal",
                                         label.position = "bottom",
                                         override.aes = list(colour = "black", size = 1))) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 18),
    legend.key.size = unit(1.3, "cm"),
    legend.position = "bottom"
  )

overlap_legend <- get_legend(legend_plot)
networkpair_overlap_plot <-  annotate_figure(plot_networkpair_overlap(sex.main.overlap.networkpair), top = text_grob("Overlap of Significant Effects Across Datasets", size = 24, x = 0.55))
 
```


```{r plot networkpair, fig.height = 12, fig.width = 20}
networkpair_col1 <- annotate_figure(
  plot_grid(
    combined_networkpair_temp_plots,
    legend,
    nrow = 2, rel_heights = c(1, 0.1)  ),
  bottom = text_grob("Sex Effect (t-value)", size = 24, y = 1)
)



networkpair_col2 <- annotate_figure(plot_grid(networkpair_all_datasets_plot, networkpair_overlap_plot, overlap_legend, nrow = 3, rel_heights = c(1, 1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))



networkpair_col2 <- plot_grid(networkpair_all_datasets_plot, networkpair_overlap_plot, nrow = 2)
overlap_legend_layout <- plot_grid(blank_space, overlap_legend, ncol = 2, rel_widths = c(0.08, 1))
overlap_legend_layout <- plot_grid(overlap_legend_layout, blank_space, nrow = 2, rel_heights = c(1, 0.1))

networkpair_col2 <- annotate_figure(plot_grid(networkpair_col2, overlap_legend_layout, nrow = 2, rel_heights = c(1, 0.1)),  bottom = text_grob("Number of Datasets", size = 24, y = 0.9, x = 0.54))

plot_grid(networkpair_col1, blank_space, networkpair_col2, blank_space, ncol = 4, rel_widths = c(2,0.1, 1, 0.1))
 
```


## sex effect with RESI
```{r plot networkpair sex for 17 networks with resi, fig.width = 25, fig.height = 15}

# plot each dataset
networkpair_resi_PNC <- annotate_figure(
  make_networkpair17_plot(sex.main.PNC.networkpair.17, dataset = "PNC", ylim1 = -0.3, ylim2 = 0.3, fontsize = 12, fontsize_label = 4, measure = "RESI"))
 
networkpair_resi_HCPD <- annotate_figure(
  make_networkpair17_plot(sex.main.HCPD.networkpair.17, dataset = "HCP-D", ylim1 = -0.3, ylim2 = 0.3, fontsize = 12, fontsize_label = 4, measure = "RESI"))

networkpair_resi_NKI <- annotate_figure(
  make_networkpair17_plot(sex.main.NKI.networkpair.17, dataset = "NKI", ylim1 = -0.3, ylim2 = 0.3, fontsize = 12, fontsize_label = 4, measure = "RESI"))

networkpair_resi_HBN <- annotate_figure(
  make_networkpair17_plot(sex.main.HBN.networkpair.17, dataset = "HBN", ylim1 = -0.3, ylim2 = 0.3, fontsize = 12, fontsize_label = 4, measure = "RESI"))

networkpair_resi_all_datasets_plot <- annotate_figure(
  make_networkpair17_plot(sex.main.all_datasets.networkpair.17, dataset = "Pooled Dataset", ylim1 = -0.3, ylim2 = 0.3, fontsize = 12, fontsize_label = 4, measure = "RESI"))

combined_networkpair_resi_temp_plots <- plot_grid(
  networkpair_resi_PNC,
  networkpair_resi_HCPD,
  networkpair_resi_NKI,
  networkpair_resi_HBN,
  ncol = 2
)


# legend
ylim1 = -0.3
ylim2 = 0.3
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.BNC, atlas = schaefer17_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(3, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)
 
```


```{r plot networkpair overlap with resi}

# overlap of datasets:
df_list_networkpair <- list(
  PNC  = sex.main.PNC.networkpair.17[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_PNC = Anova.cov.pvalue.fdr),
  HCPD = sex.main.HCPD.networkpair.17[, c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HCPD = Anova.cov.pvalue.fdr),
  NKI  = sex.main.NKI.networkpair.17[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_NKI = Anova.cov.pvalue.fdr),
  HBN  = sex.main.HBN.networkpair.17[,  c("region", "Anova.cov.pvalue.fdr")] |> rename(p_HBN = Anova.cov.pvalue.fdr)
)

sex.main.overlap.networkpair <- Reduce(function(x, y) full_join(x, y, by = "region"), df_list_networkpair)

sex.main.overlap.networkpair <- sex.main.overlap.networkpair %>%
  mutate(
    signif_count = rowSums(across(starts_with("p_")) < 0.05, na.rm = TRUE),
    signif_count_factor = factor(
      signif_count,
      levels = 0:4,
      labels = c("0", "1", "2", "3", "4")
    ),
    signif_greater_than_one = ifelse(signif_count > 1, "1", "0")
  )

sex.main.overlap.networkpair <- sex.main.overlap.networkpair %>%
  mutate(
    network1 = str_extract(region, "^[[:alpha:]]+"),
    network2 = str_extract(region, "(?<=_).*")
  )


# overlap legend
legend_plot <- ggplot(data.frame(overlap = factor(names(count_colors_legend),
                                                  levels = names(count_colors_legend))),
                      aes(x = overlap, fill = overlap)) +
  geom_bar() +
  scale_fill_manual(values = count_colors_legend,
                    guide = guide_legend(direction = "horizontal",
                                         label.position = "bottom",
                                         override.aes = list(colour = "black", size = 1))) +
  theme_void() +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 18),
    legend.key.size = unit(1.3, "cm"),
    legend.position = "bottom"
  )

overlap_legend <- get_legend(legend_plot)
networkpair_resi_overlap_plot <-  annotate_figure(plot_networkpair_overlap(sex.main.overlap.networkpair), top = text_grob("Overlap of Significant Effects Across Datasets", size = 24, x = 0.55))
 
```


```{r plot networkpair with resi, fig.height = 12, fig.width = 20}
networkpair_resi_col1 <- annotate_figure(
  plot_grid(
    combined_networkpair_resi_temp_plots,
    legend,
    nrow = 2, rel_heights = c(1, 0.1)  ),
  bottom = text_grob("Sex Effect (RESI)", size = 24, y = 1)
)



networkpair_resi_col2 <- annotate_figure(plot_grid(networkpair_resi_all_datasets_plot, networkpair_resi_overlap_plot, overlap_legend, nrow = 3, rel_heights = c(1, 1, 0.2)), 
                                     bottom = text_grob("Number of Datasets", size = 24, y = 0.1))



networkpair_resi_col2 <- plot_grid(networkpair_resi_all_datasets_plot, networkpair_resi_overlap_plot, nrow = 2)
overlap_legend_layout <- plot_grid(blank_space, overlap_legend, ncol = 2, rel_widths = c(0.08, 1))
overlap_legend_layout <- plot_grid(overlap_legend_layout, blank_space, nrow = 2, rel_heights = c(1, 0.1))

networkpair_resi_col2 <- annotate_figure(plot_grid(networkpair_resi_col2, overlap_legend_layout, nrow = 2, rel_heights = c(1, 0.1)),  bottom = text_grob("Number of Datasets", size = 24, y = 0.9, x = 0.54))

plot_grid(networkpair_resi_col1, blank_space, networkpair_resi_col2, blank_space, ncol = 4, rel_widths = c(2,0.1, 1, 0.1))
 
ggsave(
  paste0("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/Conferences/SOBP2026/", "fig_networkpair.png"),
  plot_grid(networkpair_resi_col1, blank_space, networkpair_resi_col2, blank_space,
            ncol = 4, rel_widths = c(2, 0.1, 1, 0.1)),
  height = 12, width = 20, units = "in", 
  bg = "white"
)

 

```
 
Network enrichment significance testing showed that default mode subnetwork A within-network connectivity is indeed more enriched in females than in males in all 4 datasets.  
- may need to run this for all datasets

```{r NEST DMN A table}
PNC_NEST_DMNA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/NEST/WNC/NEST_DefaultA_WNC.RData")
HCPD_NEST_DMNA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/NEST/WNC/NEST_DefaultA_WNC.RData")
NKI_NEST_DMNA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/NEST/WNC/NEST_DefaultA_WNC.RData")
HBN_NEST_DMNA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/NEST/WNC/NEST_DefaultA_WNC.RData")

NEST_results <- data.frame(
  Dataset = c("PNC", "HCP-D", "NKI", "HBN"),
  `NEST p-value` = c(
    as.numeric(PNC_NEST_DMNA$pval),
    as.numeric(HCPD_NEST_DMNA$pval),
    as.numeric(NKI_NEST_DMNA$pval),
    as.numeric(HBN_NEST_DMNA$pval)
  )
)

NEST_results %>%
  kbl(format = "html", align = "lcccc", digits = 4,
      caption = "Network enrichment significance testing for Default Mode Subnetwork A (female > male).") %>%
  add_header_above(c(" " = 1, "Default Mode Subnetwork A" = 1), bold = TRUE) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  kable_classic(full_width = FALSE, html_font = "Arial") %>%
  row_spec(0:nrow(NEST_results), extra_css = "line-height: 0.7;") %>%
  column_spec(2, background = "gray90", include_thead = TRUE)

```

```{r NEST Limbic A table, echo=FALSE, include=FALSE}
#Network enrichment significance testing showed that limbic subnetwork A within-network connectivity is indeed more enriched in male than in females in all 4 datasets.  

#PNC_NEST_LimbA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/NEST/WNC/NEST_LimbicA_TempPole_WNC.RData")
#HCPD_NEST_LimbA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/NEST/WNC/NEST_LimbicA_TempPole_WNC.RData")
#NKI_NEST_LimbA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/NEST/WNC/NEST_LimbicA_TempPole_WNC.RData")
#HBN_NEST_LimbA <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/NEST/WNC/NEST_LimbicA_TempPole_WNC.RData")

#NEST_results <- data.frame(
#  Dataset = c("PNC", "HCP-D", "NKI", "HBN"),
#  `NEST p-value` = c(
#    as.numeric(PNC_NEST_LimbA$pval),
#    as.numeric(HCPD_NEST_LimbA$pval),
#    as.numeric(NKI_NEST_LimbA$pval),
#    NA
    #as.numeric(HBN_NEST_LimbA$pval)
#  )
#)

#NEST_results %>%
#  kbl(format = "html", align = "lcccc", digits = 4,
#      caption = "Network enrichment significance testing for LimbicA Temporal Pole (male > female).") %>%
#  add_header_above(c(" " = 1, "Limbic Subnetwork A" = 1), bold = TRUE) %>%
#  kable_styling(full_width = FALSE, position = "center") %>%
#  kable_classic(full_width = FALSE, html_font = "Arial") %>%
#  row_spec(0:nrow(NEST_results), extra_css = "line-height: 0.7;") %>%
#  column_spec(2, background = "gray90", include_thead = TRUE)

```



# 4. Sex differences in edge-level connectivity vary with hierarchical span of functional connections
```{r load edge sex main effect}
# edge gam output
sex.main.PNC.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "PNC", "edge"))
sex.main.HCPD.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HCPD", "edge"))
sex.main.NKI.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "NKI", "edge"))
sex.main.HBN.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "HBN", "edge"))
sex.main.all_datasets.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x17.csv", output_root, "all_datasets", "edge"))

# resi
resi.PNC.edge <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/resi/edge/PNC_t2S_sex_maineffects_schaefer200x17.csv")
resi.HCPD.edge <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/resi/edge/HCPD_t2S_sex_maineffects_schaefer200x17.csv")
resi.NKI.edge <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/resi/edge/NKI_t2S_sex_maineffects_schaefer200x17.csv")
resi.HBN.edge <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/resi/edge/HBN_t2S_sex_maineffects_schaefer200x17.csv")
resi.all_datasets.edge <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/resi/edge/all_datasets_t2S_sex_maineffects_schaefer200x17.csv")

# merge resi
sex.main.PNC.edge <- merge(sex.main.PNC.edge, resi.PNC.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.HCPD.edge <- merge(sex.main.HCPD.edge, resi.HCPD.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.NKI.edge <- merge(sex.main.NKI.edge, resi.NKI.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.HBN.edge <- merge(sex.main.HBN.edge, resi.HBN.edge, by = "region", all.x = TRUE, sort = FALSE)
sex.main.all_datasets.edge <- merge(sex.main.all_datasets.edge, resi.all_datasets.edge, by = "region", all.x = TRUE, sort = FALSE)

# load vector of differences in S-A rank between the 2 regions connecting each edge
SA.diff <- read.csv("/cbica/projects/network_replication/atlases/edge/SA.diff_schaefer200x17.csv")

# make df for plotting (and do FDR correction)
double.PNC <- make_double_df(sex.main.PNC.edge, "edge", "sex", "PNC")  
double.HCPD <- make_double_df(sex.main.HCPD.edge, "edge", "sex", "HCPD")  
double.NKI <- make_double_df(sex.main.NKI.edge, "edge", "sex", "NKI")  
double.HBN <- make_double_df(sex.main.HBN.edge, "edge", "sex", "HBN")  
double.all_datasets <- make_double_df(sex.main.all_datasets.edge, "edge", "sex", "All datasets")  


# load spin test results
PNC_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "PNC"))
HCPD_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "HCPD"))
NKI_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "NKI"))
HBN_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "HBN"))
all_datasets_edges_spin <- readRDS(sprintf("%1$s/%2$s/spin_test/edge/SA_edges_schaefer200x17_spin_test_results.RData", output_root, "all_datasets"))

```

We modeled the sex-effect map (t-values) across edges using tensor product smooth:

$$
edge.sex.effect \sim te(SArank_{parcel1}, SArank_{parcel2})
$$

We assessed significance with a spin test that preserves spatial autocorrelation by rotating the S-A axis and recomputing model fit statistics (R2). The spin test evaluates whether the 2D tensor smooth linking sex effects to S–A axis ranks is stronger than expected given spatial autocorrelation.

We found that sex differences in edge-level connectivity are systematically organized along the cortical hierarchy. We observed stronger connectivity between regions connecting high- to low-ranking 

```{r plot edge sex, fig.height = 14, fig.width = 20}

# plot surfaces
PNC_surf_plot <- make_surface_plot(double.PNC, dataset = "PNC", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
HCPD_surf_plot <-  make_surface_plot(double.HCPD, dataset = "HCP-D", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
NKI_surf_plot <-  make_surface_plot(double.NKI, dataset = "NKI", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
HBN_surf_plot <-  make_surface_plot(double.HBN, dataset = "HBN", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = NULL)
row1 <- plot_grid(PNC_surf_plot, blank_space, HCPD_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
row2 <- plot_grid(NKI_surf_plot, blank_space, HBN_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
combined_surf_plots <- plot_grid(row1, blank_space, row2, ncol = 1, nrow = 3, rel_heights = c(1, 0.1, 1))
combined_surf_plots <- annotate_figure(combined_surf_plots, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))

all_datasets_surf_plot <-  make_surface_plot(double.all_datasets, dataset = "All Datasets", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = bquote(italic(p[spin]) == .(format(round(all_datasets_edges_spin$p_values$R2, 4), scientific = FALSE))))  
all_datasets_surf_plot <- annotate_figure(all_datasets_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))
# make legend
ylim1 = -3
ylim2 = 3
g2 <- gam(GAM.cov.tvalue ~ te(parcel2_SA,parcel1_SA,k=3), data = double.PNC)
  
surface.plot.fig <- gg_tensor(g2) + theme_classic() +
    theme(
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.line = element_line(color = "black"),
      axis.text=element_text(size=24, color = "black")) + 
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") +     geom_vline(xintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    geom_hline(yintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    theme(legend.position='bottom',
          legend.key.height = unit(1, 'cm'),
          legend.key.width = unit(3, 'cm'),
          legend.title = element_blank(),
          legend.text = element_text(size=24),
          strip.background = element_blank(),
          plot.margin = margin(0, 0, 0, 0, "cm"),
          plot.title = element_text(size=24, hjust=0.5))  
  
legend <- get_legend(surface.plot.fig)
blank_space <- ggplot() + theme_void()

# combine plots
combined_surf_plots <- plot_grid(combined_surf_plots, blank_space, all_datasets_surf_plot, ncol = 3, rel_widths = (c(1, 0.05, 1)))

final_surf_plots <- plot_grid(blank_space, combined_surf_plots, legend, nrow = 3, rel_heights = c(0.05, 1, 0.2))
annotate_figure(final_surf_plots, 
                bottom = text_grob("Sex Effect (t-value)", size = 20, x = 0.5, y = 2))



```



```{r plot edge sex effect with resi, fig.height = 14, fig.width = 20}
# plot surfaces
PNC_surf_plot <- make_surface_plot(double.PNC, dataset = "PNC", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
HCPD_surf_plot <-  make_surface_plot(double.HCPD, dataset = "HCP-D", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
NKI_surf_plot <-  make_surface_plot(double.NKI, dataset = "NKI", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
HBN_surf_plot <-  make_surface_plot(double.HBN, dataset = "HBN", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL)
row1 <- plot_grid(PNC_surf_plot, blank_space, HCPD_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
row2 <- plot_grid(NKI_surf_plot, blank_space, HBN_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
combined_surf_plots <- plot_grid(row1, blank_space, row2, ncol = 1, nrow = 3, rel_heights = c(1, 0.1, 1))
combined_surf_plots <- annotate_figure(combined_surf_plots, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))

all_datasets_surf_plot <-  make_surface_plot(double.all_datasets, dataset = "All Datasets", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = bquote(italic(p[spin]) == .(format(round(all_datasets_edges_spin$p_values$R2, 4), scientific = FALSE))))  
all_datasets_surf_plot <- annotate_figure(all_datasets_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))
# make legend
ylim1 = -0.1
ylim2 = 0.1
g2 <- gam(RESI ~ te(parcel2_SA,parcel1_SA,k=3), data = double.PNC)
  
surface.plot.fig <- gg_tensor(g2) + theme_classic() +
    theme(
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.line = element_line(color = "black"),
      axis.text=element_text(size=24, color = "black")) + 
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") +     
  geom_vline(xintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    geom_hline(yintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    theme(legend.position='bottom',
          legend.key.height = unit(1, 'cm'),
          legend.key.width = unit(3, 'cm'),
          legend.title = element_blank(),
          legend.text = element_text(size=24),
          strip.background = element_blank(),
          plot.margin = margin(0, 0, 0, 0, "cm"),
          plot.title = element_text(size=24, hjust=0.5))  
  
legend <- get_legend(surface.plot.fig)


# combine plots
combined_surf_plots <- plot_grid(combined_surf_plots, blank_space, all_datasets_surf_plot, ncol = 3, rel_widths = (c(1, 0.05, 1)))

final_surf_plots <- plot_grid(blank_space, combined_surf_plots, legend, nrow = 3, rel_heights = c(0.05, 1, 0.2))
annotate_figure(final_surf_plots, 
                bottom = text_grob("Sex Effect (RESI)", size = 20, x = 0.5, y = 2))


#ggsave(paste0("/Users/audluo/Library/CloudStorage/Box-Box/Box_PhD_Land/PennLINC/sex_diff/Conferences/SOBP2026/", "fig3_edge.png"), annotate_figure(final_surf_plots, 
               # bottom = text_grob("Sex Effect (RESI)", size = 20, x = 0.5, y = 2)), height = 14, width = 20, units = "in", bg = "white")
 
```

## edge plot colored by RESI of edges surviving FDR correction only
```{r plot edge fdr sig sex effect with resi, fig.height = 14, fig.width = 20}
# plot surfaces
PNC_sigonly_surf_plot <- make_surface_plot(double.PNC, dataset = "PNC", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
HCPD_sigonly_surf_plot <-  make_surface_plot(double.HCPD, dataset = "HCP-D", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
NKI_sigonly_surf_plot <-  make_surface_plot(double.NKI, dataset = "NKI", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
HBN_sigonly_surf_plot <-  make_surface_plot(double.HBN, dataset = "HBN", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = NULL, significant_only = TRUE)
row1 <- plot_grid(PNC_sigonly_surf_plot, blank_space, HCPD_sigonly_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
row2 <- plot_grid(NKI_sigonly_surf_plot, blank_space, HBN_sigonly_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
combined_sigonly_surf_plots <- plot_grid(row1, blank_space, row2, ncol = 1, nrow = 3, rel_heights = c(1, 0.1, 1))
combined_sigonly_surf_plots <- annotate_figure(combined_sigonly_surf_plots, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))

all_datasets_sigonly_surf_plot <-  make_surface_plot(double.all_datasets, dataset = "All Datasets", measure = "RESI", ylim1 = -0.1, ylim2  = 0.1, 
                                   p_label = bquote(italic(p[spin]) == .(format(round(all_datasets_edges_spin$p_values$R2, 4), scientific = FALSE))), significant_only = TRUE)  
all_datasets_sigonly_surf_plot <- annotate_figure(all_datasets_sigonly_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.53, y = -0.5))
# make legend
ylim1 = -0.1
ylim2 = 0.1
g2 <- gam(RESI ~ te(parcel2_SA,parcel1_SA,k=3), data = double.PNC)
  
surface.plot.fig <- gg_tensor(g2) + theme_classic() +
    theme(
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.line = element_line(color = "black"),
      axis.text=element_text(size=24, color = "black")) + 
     scale_fill_gradientn(colours = red_teal_white(256), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") +     
  geom_vline(xintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    geom_hline(yintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    theme(legend.position='bottom',
          legend.key.height = unit(1, 'cm'),
          legend.key.width = unit(3, 'cm'),
          legend.title = element_blank(),
          legend.text = element_text(size=24),
          strip.background = element_blank(),
          plot.margin = margin(0, 0, 0, 0, "cm"),
          plot.title = element_text(size=24, hjust=0.5))  
  
legend <- get_legend(surface.plot.fig)


# combine plots
combined_sigonly_surf_plots <- plot_grid(combined_sigonly_surf_plots, blank_space, all_datasets_sigonly_surf_plot, ncol = 3, rel_widths = (c(1, 0.05, 1)))

final_sigonly_surf_plots <- plot_grid(blank_space, combined_sigonly_surf_plots, legend, nrow = 3, rel_heights = c(0.05, 1, 0.2))
annotate_figure(final_sigonly_surf_plots, 
                bottom = text_grob("Sex Effect (RESI)", size = 20, x = 0.5, y = 2))

 
```

Sex effects at the edge-level appear to be distributed hierarchically, with males showing stronger connectivity in edges connecting regions across the S-A axis and in the middle of the axis (i.e. association-sensorimotor and middle-middle ranking regions) and females showing higher connectivity between similarly ranked regions (i.e. association-association and sensorimotor-sensorimotor regions). Connectivity in males appear to be more integrative, whereas females exhibit greater segregation.

 
```{r resi rain cloud plot}

RESI_all_datasets <- rbind(sex.main.PNC.edge %>% mutate(Dataset="PNC"), sex.main.HCPD.edge %>% mutate(Dataset="HCP-D"), sex.main.NKI.edge %>% mutate(Dataset="NKI"), sex.main.HBN.edge %>% mutate(Dataset="HBN"), sex.main.all_datasets.edge %>% mutate(Dataset="All datasets"))
RESI_all_datasets$Dataset <- factor(RESI_all_datasets$Dataset, levels = c("PNC", "HCP-D", "NKI", "HBN", "All datasets"))


# raincloud of RESI edge distribution of data
ggplot(RESI_all_datasets, aes(Dataset, RESI, fill = Dataset, color = Dataset)) +
  
  ggdist::stat_halfeye(
    adjust = .5, 
    width = .6, 
    .width = 0,
    justification = -.3,
    alpha = 0.9,        
    size = 0.6        
  ) +
  
  geom_boxplot(
    width = .25,
    outlier.shape = NA,
    alpha = 0.7,
    linewidth = 0.7
  ) +
  
  geom_hline(
    yintercept = 0,
    linetype = "dashed",
    color = "black",
    linewidth = 0.5
  ) +
  
  paletteer::scale_fill_paletteer_d("PNWColors::Shuksan") +
  paletteer::scale_color_paletteer_d("PNWColors::Shuksan") +
  
  theme_classic() + 
  
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    plot.margin = margin(0, 0, -0.1, 0.5, "cm"),
    axis.text.y = element_text(size = 20),
    axis.text.x = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.line = element_line(color = "black"),
    axis.text = element_text(size = 24, color = "black")
  )


```
Raincloud distribution of RESI sex effect sizes of edges show comparable distributions across datasets. Median effect size appears to be above zero, indicating a shift toward greater connectivity in males across connections, though magnitude of effects at individual edges was small. 
 
  
  
# 5. Gradients Analysis
global dispersion is consistently greater in females (small to medium effect). females show greater within-network dispersion too, with FPN and limbic OFC showing up the most often (i.e. parcels within a network are more 'different' from each other in females).  between-network dispersion has greatest effects, with greater dispersion in females across the board with really pronounced effects at DMN A, B, and C with somatomotor and visual networks (so those networks are way more different from each other in females than males; i.e. a these two networks' centroids on PC1 are way more far apart in females).

also HBN is very much the problem child in this analysis. this isn't the best measure of data quality, but one of the things i looked at earlier was comparing PC1 (for the group average connectivity matrix) in thresholded (keep top 10% edges) vs unthresholded matrices. and the correlation in HBN was 0.05 :face_with_spiral_eyes:

For reference, PNC was 0.72, NKI: 0.26, HCPD: 0.25, pooled dataset: 0.49
```{r global dispersion, fig.height = 9, fig.width = 15}
blank_space <- ggplot() + theme_void()
global_disp_row1 <- plot_grid(plot_global_dispersion("PNC", "PNC"), blank_space, plot_global_dispersion("HCPD", "HCP-D"), ncol = 3, rel_widths = c(1, 0.1, 1))
global_disp_row2 <- plot_grid(plot_global_dispersion("NKI", "NKI"), blank_space, plot_global_dispersion("HBN", "HBN"), ncol = 3, rel_widths = c(1, 0.1, 1))
global_disp_p1 <- plot_grid(global_disp_row1, blank_space, global_disp_row2, nrow = 3, rel_heights = c(1, 0.05, 1))


global_disp_p2 <- plot_grid(global_disp_p1, blank_space, plot_global_dispersion("all_datasets", "Pooled Dataset"), ncol = 3, rel_widths = c(1, 0.1, 1))
global_disp_p3 <- plot_grid(blank_space, global_disp_p2, nrow = 2, rel_heights = c(0.05, 1))


annotate_figure(global_disp_p3,
      top = text_grob("Global Dispersion", size = 30), 
      left = text_grob("Dispersion", size = 24, rot = 90))
```

```{r within network dispersion, fig.height = 12, fig.width = 20}
blank_space <- ggplot() + theme_void()
within_disp_row1 <- plot_grid(plot_within_dispersion("PNC", "PNC"), blank_space, plot_within_dispersion("HCPD", "HCP-D"), ncol = 3, rel_widths = c(1, 0.02, 1))
within_disp_row2 <- plot_grid(plot_within_dispersion("NKI", "NKI"), blank_space, plot_within_dispersion("HBN", "HBN"), ncol = 3, rel_widths = c(1, 0.02, 1))
within_disp_p1 <- plot_grid(within_disp_row1, blank_space, within_disp_row2, nrow = 3, rel_heights = c(1, 0.02, 1))
within_disp_datasets <- annotate_figure(within_disp_p1, bottom = text_grob("Sex Effect (RESI)", size = 20))
      
within_disp_p2 <- plot_grid(plot_within_dispersion("all_datasets", "Pooled Dataset"), blank_space, plot_within_overlap(), nrow = 3, rel_heights = c(1, 0.05, 1))
 
within_disp_final <- plot_grid(within_disp_p1, blank_space,  within_disp_p2, blank_space, ncol = 4, rel_widths = c(1, 0.01, 0.5, 0.05))
 

annotate_figure(within_disp_final,
      top = text_grob("Within-Network Dispersion", size = 30))
 
```
 

```{r between network dispersion,  fig.height = 12, fig.width = 18}
 
# plots
between_PNC <- plot_between_dispersion("PNC", "PNC")
between_HCPD <- plot_between_dispersion("HCPD", "HCP-D")
between_NKI <- plot_between_dispersion("NKI", "NKI")
between_HBN <- plot_between_dispersion("HBN", "HBN")
between_all <- plot_between_dispersion("all_datasets", "Pooled Dataset")
between_overlap <- plot_between_overlap()

# RESI legend
resi_legend_plot <- ggplot(data.frame(x = 1, y = 1, z = 0), aes(x, y, fill = z)) +
  geom_tile() +
  scale_fill_gradientn(colours = red_teal_white(256), values = scales::rescale(c(-0.2, 0, 0.2)),
                       limits = c(-0.23, 0.2), oob = squish, name = NULL) +
  theme_void() +
  theme(legend.position = "bottom", legend.text = element_text(size = 18),
        legend.key.height = unit(0.8, "cm"), legend.key.width = unit(3, "cm"))

resi_legend <- get_legend(resi_legend_plot)

# overlap legend
count_colors <- c("0-1" = "white", "2" = "#F6D0B5", "3" = "#D95F8D", "4" = "#AD2A72")

overlap_legend_plot <- ggplot(
  data.frame(overlap = factor(c("0-1", "2", "3", "4"), levels = c("0-1", "2", "3", "4"))),
  aes(x = overlap, fill = overlap)
) +
  geom_bar() +
  scale_fill_manual(values = count_colors, drop = FALSE,
                    guide = guide_legend(direction = "horizontal", label.position = "bottom",
                                         override.aes = list(colour = "black", linewidth = 0.5))) +
  theme_void() +
  theme(legend.title = element_blank(), legend.text = element_text(size = 18),
        legend.key.size = unit(1.3, "cm"), legend.position = "bottom")

overlap_legend <- get_legend(overlap_legend_plot)

# left column: 4 datasets + RESI legend
between_four <- plot_grid(between_PNC, between_HCPD, between_NKI, between_HBN, ncol = 2)

between_col1 <- annotate_figure(
  plot_grid(between_four, resi_legend, nrow = 2, rel_heights = c(1, 0.08)),
  bottom = text_grob("Sex Effect (RESI)", size = 20, y = 0.5)
)

# right column: pooled + overlap + overlap legend
between_col2_plots <- plot_grid(between_all, between_overlap, nrow = 2)

overlap_legend_layout <- plot_grid(blank_space, overlap_legend, ncol = 2, rel_widths = c(0.08, 1))
overlap_legend_layout <- plot_grid(overlap_legend_layout, blank_space, nrow = 2, rel_heights = c(1, 0.1))

between_col2 <- annotate_figure(
  plot_grid(between_col2_plots, overlap_legend_layout, nrow = 2, rel_heights = c(1, 0.1)),
  bottom = text_grob("Number of Datasets", size = 20, y = 0.9, x = 0.5)
)

# final layout
between_dispersion_figure <- plot_grid(blank_space, plot_grid(between_col1, between_col2, blank_space,
                                       ncol = 3, rel_widths = c(2, 1, 0.1)), nrow = 2, rel_heights = c(0.01, 1))

annotate_figure(between_dispersion_figure,
                top = text_grob("Between-Network Dispersion", size = 24))

```

 
## Distribution of PC1
Interestingly, the overall male/female PC1 distributions and mean cortical PC1 maps look quite similar. so the dispersion sex effects above don’t seem to reflect a simple overall difference in PC1... and i think the key is that dispersion is looking within subjects (i.e. in a given subject, how spread out are their 200 parcel loadings around that subject’s own PC1 median?). So even though females and males have a very similar average PC1 spatial organization, within individuals, females tend to have parcels/networks that are more spread out along PC1. And looking at average PC1 loadings ends up obscuring these within-individual difference between males/females

```{r distribution of PC1, fig.height = 7, fig.width = 15}
sex_colors <- c(Female = "#C53121", Male = "#0B8CACFF")

root <- "/cbica/projects/network_replication/covariate_analyses/sex_diff"
datasets <- c("PNC", "NKI", "HCPD", "HBN", "all_datasets")

 
pc1_long <- map_dfr(datasets, function(dataset) {
  df <- read.csv(sprintf("%s/output/%s/gradient_dispersion/pc1_loadings_long_%s.csv", root, dataset, dataset))
  if(dataset == "all_datasets") df$dataset <- "all_datasets"
  df
})

pc1_long$sex <- factor(pc1_long$sex, levels = c("Female", "Male"))

plot_pc1_density <- function(dataset, title) {
  df <- pc1_long %>% filter(dataset == !!dataset)
  
  ggplot(df, aes(x = pc1, fill = sex, color = sex)) +
    geom_density(alpha = 0.25, linewidth = 1) +
    scale_fill_manual(values = sex_colors) +
    scale_color_manual(values = sex_colors) +
    coord_cartesian(xlim = c(-4, 6)) +
    labs(title = title, x = NULL, y = NULL) +
    theme_classic(base_size = 20) +
    theme(legend.position = "none",
          plot.title = element_text(size = 20, hjust = 0.5),
          axis.text = element_text(size = 20, color = "black"))
}

pc1_density_PNC <- plot_pc1_density("PNC", "PNC")
pc1_density_HCPD <- plot_pc1_density("HCPD", "HCP-D")
pc1_density_NKI <- plot_pc1_density("NKI", "NKI")
pc1_density_HBN <- plot_pc1_density("HBN", "HBN")
pc1_density_all <- plot_pc1_density("all_datasets", "Pooled Dataset")

sex_legend_plot <- ggplot(data.frame(sex = factor(c("Female", "Male"), levels = c("Female", "Male")), x = 1:2, y = 1),
                          aes(x, y, fill = sex, color = sex)) +
  geom_point(shape = 21, size = 6) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  guides(fill = guide_legend(direction = "horizontal", override.aes = list(size = 6, alpha = 0.5)), color = "none") +
  theme_void() +
  theme(legend.position = "bottom", legend.title = element_blank(),
        legend.text = element_text(size = 20), legend.key.size = unit(1.1, "cm"))

sex_legend <- get_legend(sex_legend_plot)

blank_space <- ggplot() + theme_void()

pc1_density_row1 <- plot_grid(pc1_density_PNC, blank_space, pc1_density_HCPD, ncol = 3, rel_widths = c(1, 0.1, 1))
pc1_density_row2 <- plot_grid(pc1_density_NKI, blank_space, pc1_density_HBN, ncol = 3, rel_widths = c(1, 0.1, 1))
pc1_density_p1 <- plot_grid(pc1_density_row1, blank_space, pc1_density_row2, nrow = 3, rel_heights = c(1, 0.05, 1))
pc1_density_p2 <- plot_grid(pc1_density_p1, blank_space, pc1_density_all, ncol = 3, rel_widths = c(1, 0.1, 1))

pc1_density_figure <- plot_grid(pc1_density_p2, sex_legend, nrow = 2, rel_heights = c(1, 0.08))

pc1_density_figure <- annotate_figure(pc1_density_figure,
                                      top = text_grob("PC1 Distribution", size = 30),
                                      left = text_grob("Density", size = 24, rot = 90),
                                      bottom = text_grob("PC1 Loading", size = 24))

pc1_density_figure

```


## PC1 loadings in males vs females
```{r PC1 in males and females, fig.height = 10, fig.width = 15}

library(tidyverse)
library(ggseg)
library(ggsegSchaefer)
library(cowplot)
library(scales)
library(paletteer)

root <- "/cbica/projects/network_replication/covariate_analyses/sex_diff"
datasets <- c("PNC", "NKI", "HCPD", "HBN", "all_datasets")

pc1_brain <- map_dfr(datasets, function(dataset) {
  if(dataset == "all_datasets") {
    df <- read.csv(sprintf("%s/output/%s/gradient_dispersion/pc1_loadings_long_%s.csv", root, dataset, dataset)) %>%
      group_by(sex, parcel, parcel_label, hemisphere, network) %>%
      summarise(pc1_mean = mean(pc1, na.rm = TRUE), # fyi: pc1_mean at parcel 1 = mean(PC1 at parcel 1 for every female subject across PNC + NKI + HCPD + HBN)
                pc1_median = median(pc1, na.rm = TRUE),
                pc1_sd = sd(pc1, na.rm = TRUE),
                n = sum(!is.na(pc1)),
                pc1_se = pc1_sd / sqrt(n), .groups = "drop") %>%
      mutate(dataset = "all_datasets")
  } else {
    df <- read.csv(sprintf("%s/output/%s/gradient_dispersion/pc1_parcel_by_sex_%s.csv", root, dataset, dataset))
  }
  
  df <- df %>% rename(region = parcel_label) %>% mutate(region = paste0("17", region))
  df
})




# common symmetric PC1 scale across all datasets and both sexes
pc1_lim <- max(abs(pc1_brain$pc1_mean), na.rm = TRUE)
ylim1 <- -pc1_lim
ylim2 <- pc1_lim

# adapted from your existing plot_cortex() function
plot_cortex_pc1 <- function(df, hemi, sex_name, ylim1, ylim2, horizontal_layout = NULL) {
  df <- df %>% filter(sex == sex_name)

  if(hemi == "left") {
    cortical_pos1 <- "left lateral"
    cortical_pos2 <- "left medial"
  } else {
    cortical_pos1 <- "right lateral"
    cortical_pos2 <- "right medial"
  }

  plot_lateral <- ggplot() +
    geom_brain(data = df, atlas = schaefer17_200, mapping = aes(fill = pc1_mean),
               show.legend = TRUE, hemi = hemi, position = position_brain(cortical_pos1)) +
    paletteer::scale_fill_paletteer_c("pals::ocean.curl",
                                      limits = c(ylim1, ylim2), oob = squish, na.value = "white") +
    theme_void() +
    theme(legend.position = "none",
          legend.title = element_blank(),
          plot.margin = unit(c(0.1, -1, 0.1, -1), "cm"),
          plot.title = element_blank())

  plot_medial <- ggplot() +
    geom_brain(data = df, atlas = schaefer17_200, mapping = aes(fill = pc1_mean),
               show.legend = TRUE, hemi = hemi, position = position_brain(cortical_pos2)) +
    paletteer::scale_fill_paletteer_c("pals::ocean.curl",
                                      limits = c(ylim1, ylim2), oob = squish, na.value = "white") +
    theme_void() +
    theme(legend.position = "none",
          legend.title = element_blank(),
          plot.margin = unit(c(0.1, -1, 0.1, -1), "cm"),
          plot.title = element_blank())

  if(is.null(horizontal_layout)) {
    return(plot_grid(plot_lateral, plot_medial, ncol = 1, rel_heights = c(1, 1), align = "v", axis = "lr"))
  } else {
    return(plot_grid(plot_lateral, plot_medial, ncol = 2, align = "v", axis = "lr"))
  }
}

# individual datasets: female and male side-by-side;
# each sex has left/right hemispheres, each shown lateral + medial vertically
plot_pc1_dataset <- function(dataset, title) {
  df <- pc1_brain %>% filter(dataset == !!dataset)

  female_left <- plot_cortex_pc1(df, "left", "Female", ylim1, ylim2)
  female_right <- plot_cortex_pc1(df, "right", "Female", ylim1, ylim2)
  male_left <- plot_cortex_pc1(df, "left", "Male", ylim1, ylim2)
  male_right <- plot_cortex_pc1(df, "right", "Male", ylim1, ylim2)

  female <- plot_grid(female_left, female_right, ncol = 2)
  male <- plot_grid(male_left, male_right, ncol = 2)

  female <- plot_grid(ggdraw() + draw_label("Female", size = 18),
                      female, ncol = 1, rel_heights = c(0.08, 1))
  male <- plot_grid(ggdraw() + draw_label("Male", size = 18),
                    male, ncol = 1, rel_heights = c(0.08, 1))

  brains <- plot_grid(female, male, ncol = 2)

  plot_grid(ggdraw() + draw_label(title, size = 20),
            brains, ncol = 1, rel_heights = c(0.08, 1))
}

# pooled dataset: all 8 views in one row
plot_pc1_pooled <- function() {
  df <- pc1_brain %>% filter(dataset == "all_datasets")

  female_left <- plot_cortex_pc1(df, "left", "Female", ylim1, ylim2, horizontal_layout = TRUE)
  female_right <- plot_cortex_pc1(df, "right", "Female", ylim1, ylim2, horizontal_layout = TRUE)
  male_left <- plot_cortex_pc1(df, "left", "Male", ylim1, ylim2, horizontal_layout = TRUE)
  male_right <- plot_cortex_pc1(df, "right", "Male", ylim1, ylim2, horizontal_layout = TRUE)

  female <- plot_grid(female_left, female_right, ncol = 2)
  male <- plot_grid(male_left, male_right, ncol = 2)

  female <- plot_grid(ggdraw() + draw_label("Female", size = 18),
                      female, ncol = 1, rel_heights = c(0.10, 1))
  male <- plot_grid(ggdraw() + draw_label("Male", size = 18),
                    male, ncol = 1, rel_heights = c(0.10, 1))

  blank_space <- ggplot() + theme_void()

  brains <- plot_grid(female, blank_space, male, ncol = 3, rel_widths = c(1, 0.08, 1))

  plot_grid(ggdraw() + draw_label("Pooled Dataset", size = 20),
            brains, ncol = 1, rel_heights = c(0.10, 1))
}
# dataset plots
pc1_brain_PNC <- plot_pc1_dataset("PNC", "PNC")
pc1_brain_HCPD <- plot_pc1_dataset("HCPD", "HCP-D")
pc1_brain_NKI <- plot_pc1_dataset("NKI", "NKI")
pc1_brain_HBN <- plot_pc1_dataset("HBN", "HBN")
pc1_brain_pooled <- plot_pc1_pooled()

# shared PC1 legend
pc1_legend_plot <- ggplot(data.frame(x = 1, y = 1, pc1 = 0), aes(x, y, fill = pc1)) +
  geom_tile() +
  paletteer::scale_fill_paletteer_c("pals::ocean.curl",
                                    limits = c(ylim1, ylim2), oob = squish, name = NULL) +
  theme_void() +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 18),
        legend.key.height = unit(0.8, "cm"),
        legend.key.width = unit(3, "cm"))

pc1_legend <- get_legend(pc1_legend_plot)
blank_space <- ggplot() + theme_void()

# four individual datasets
pc1_brain_row1 <- plot_grid(pc1_brain_PNC, blank_space, pc1_brain_HCPD,
                            ncol = 3, rel_widths = c(1, 0.1, 1))

pc1_brain_row2 <- plot_grid(pc1_brain_NKI, blank_space, pc1_brain_HBN,
                            ncol = 3, rel_widths = c(1, 0.1, 1))

pc1_brain_four <- plot_grid(pc1_brain_row1, blank_space, pc1_brain_row2,
                            nrow = 3, rel_heights = c(1, 0.1, 1))

# pooled dataset underneath
pc1_brain_main <- plot_grid(pc1_brain_four, blank_space, pc1_brain_pooled,
                            nrow = 3, rel_heights = c(2, 0.1, 0.55))

# legend underneath everything
pc1_brain_with_legend <- plot_grid(pc1_brain_main, blank_space, pc1_legend, blank_space, 
                                   nrow = 4, rel_heights = c(1, 0.06, 0.06, 0.06))

pc1_brain_figure <- annotate_figure(
  pc1_brain_with_legend,
  bottom = text_grob("Mean PC1 Loading", size = 20, vjust = 0.05)
)

pc1_brain_figure
```



# Supplementary analyses

## Histogram of WNC and BNC

```{r BNC and WNC histograms, fig.height = 8, fig.width = 20}
# load subject levels BNC and WNC
PNC_BNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/BNC/BNC_subxparcel_matrix_schaefer200x17.csv")
HCPD_BNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/BNC/BNC_subxparcel_matrix_schaefer200x17.csv")
NKI_BNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/BNC/BNC_subxparcel_matrix_schaefer200x17.csv")
HBN_BNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/BNC/BNC_subxparcel_matrix_schaefer200x17.csv")

PNC_WNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/WNC/WNC_subxparcel_matrix_schaefer200x17.csv")
HCPD_WNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/WNC/WNC_subxparcel_matrix_schaefer200x17.csv")
NKI_WNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/WNC/WNC_subxparcel_matrix_schaefer200x17.csv")
HBN_WNC_subxparcel <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/WNC/WNC_subxparcel_matrix_schaefer200x17.csv")

# hist function
make_hist_plot <- function(subxparcel_df, dataset, xlim1, xlim2, color) {
  long_df <- subxparcel_df %>%
    pivot_longer(cols = -subject, names_to = "region", values_to = "value") %>%
    filter(!is.na(value))
  
  p <- ggplot(long_df, aes(x = value)) +
    geom_histogram(bins = 20, color = color, fill = color, linewidth = 0.7, alpha = 0.7) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "#33271EFF", linewidth = 0.7) +
    theme_classic() +
    labs(x = "", y = "") + ggtitle(dataset) +
    theme(axis.text = element_text(size = 20, color = "#33271EFF"),
          axis.title = element_text(size = 20),
          plot.title = element_text(size = 20, hjust = 0.5)) + xlim(xlim1, xlim2)
  
  return(p)
}


# make histograms
BNC_hist <- plot_grid(blank_space, plot_grid(make_hist_plot(PNC_BNC_subxparcel, "PNC", -0.5, 0.5, color = "#B7E6A5FF"), make_hist_plot(HCPD_BNC_subxparcel, "HCP-D", -0.5, 0.5, color = "#B7E6A5FF"),
                                 make_hist_plot(NKI_BNC_subxparcel,"NKI", -0.5, 0.5, color = "#B7E6A5FF"), make_hist_plot(HBN_BNC_subxparcel,"HBN", -0.5, 0.5, color = "#B7E6A5FF")), 
                      nrow = 2, rel_heights = c(0.03, 1))


WNC_hist <- plot_grid(blank_space, plot_grid(make_hist_plot(PNC_WNC_subxparcel, "PNC", -0.7, 1, color = "#64A8A8FF"), make_hist_plot(HCPD_WNC_subxparcel, "HCP-D", -0.7, 1, color = "#64A8A8FF"),
                                 make_hist_plot(NKI_WNC_subxparcel,"NKI", -0.7, 1, color = "#64A8A8FF"), make_hist_plot(HBN_WNC_subxparcel,"HBN", -0.7, 1, color = "#64A8A8FF")), 
                      nrow = 2, rel_heights = c(0.03, 1))


BNC_hist_plots <- annotate_figure(BNC_hist, bottom = text_grob("Between-Network Connectivity", size = 24),
                left = text_grob("Count", size = 24, rot = 90),
                top = text_grob("Distribution of BNC", size = 24))



WNC_hist_plots <- annotate_figure(WNC_hist, bottom = text_grob("Within-Network Connectivity", size = 24),
                left = text_grob("Count", size = 24, rot = 90),
                top = text_grob("Distribution of WNC", size = 24))


plot_grid(BNC_hist_plots, blank_space, WNC_hist_plots, ncol = 3, rel_widths = c(1, 0.1, 1))
```

## Age-by-sex interaction across ALL datasets

-   WNC in 11 regions (5%; schaefer200x7) and 22 regions (11%; schafer200x17) has some age-by-sex effects when datasets are pooled.
-   network-pair connectivity also has some significant age-by-sex interactions

```{r load age by sex interaction across datasets}
GBC_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
GBC_schaefer7 <- sig.effects.all_datasets(GBC_schaefer7, "GBC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
GBC_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
GBC_schaefer17 <- sig.effects.all_datasets(GBC_schaefer17, "GBC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")

BNC_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
BNC_schaefer7 <- sig.effects.all_datasets(BNC_schaefer7, "BNC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
BNC_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
BNC_schaefer17 <- sig.effects.all_datasets(BNC_schaefer17, "BNC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")

WNC_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
WNC_schaefer7 <- sig.effects.all_datasets(WNC_schaefer7, "WNC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
WNC_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
WNC_schaefer17 <- sig.effects.all_datasets(WNC_schaefer17, "WNC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
#WNC_schaefer17 %>% arrange(desc(int_sig_effect))

netpair_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
netpair_schaefer7 <- sig.effects.all_datasets(netpair_schaefer7, "netpair", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
netpair_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
netpair_schaefer17 <- sig.effects.all_datasets(netpair_schaefer17, "netpair", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
#netpair_schaefer17 %>% arrange(desc(int_sig_effect))
```

 
```{r plot WNC age by sex regions, fig.height = 10, fig.width = 10}
WNC_schaefer17 <- WNC_schaefer17 %>% mutate(region = if_else(startsWith(region, "17"), region, paste0("17", region)))
sex.int.all_dataset.WNC_lh <- plot_cortex_int(WNC_schaefer17, hemi = "left", measure = "int_sig_effect", ylim1 = 1, ylim2 = 9, atlas = "schaefer17_200") 
sex.int.all_dataset.WNC_rh <- plot_cortex_int(WNC_schaefer17, hemi = "right", measure = "int_sig_effect", ylim1 = 1, ylim2 = 9, atlas = "schaefer17_200")

ylim1 = 1
ylim2 = 9
p <- ggplot() + 
    geom_brain(data = WNC_schaefer17, atlas = schaefer17_200, 
               mapping=aes(fill=int_sig_effect, colour=significant_status, size=I(0.7)), 
               show.legend=TRUE) +
    scale_fill_paletteer_c("ggthemes::Blue-Green Sequential", na.value = "white") + 
    scale_colour_manual(values = c("Sig" = "black", "Nonsig" = "grey50")) + 
    theme_void() +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm")) + guides(color = "none")
  
  
legend <- get_legend(p)
blank_space <- ggplot() + theme_void()

annotate_figure(
  plot_grid(
    annotate_figure(
      plot_grid(
        sex.int.all_dataset.WNC_lh,
        sex.int.all_dataset.WNC_rh,
        ncol = 2
      ),
      top = text_grob("WNC age-by-sex all datasets (Schaefer 200x17)", size = 24)
    ),
    legend,
    ncol = 1,
    rel_heights = c(1, 0.2)
  ),
  bottom = text_grob("Interaction (F-value)", size = 24)
)

 print(WNC_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))
```

```{r print networkpair age by sex pairs}
 print(netpair_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))

 print(WNC_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))

```
 
 
 
 
```{r load WNC age by sex dev trajectories}
agebysex.all_datasets.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_fitted_%4$s.csv", output_root, "all_datasets", "WNC", "schaefer200x17"))
agebysex.all_datasets.WNC$region <- paste0("17", agebysex.all_datasets.WNC$region)
agebysex.all_datasets.WNC <- agebysex.all_datasets.WNC %>% rename(age=smooth_var)

```

```{r WNC dev trajectories vis, fig.height = 20, fig.width = 20}
WNC_interaction_regions <- WNC_schaefer17 %>% filter(significant.fdr == 1) %>% pull(region) #%>% paste0('17', .)
agebysex.all_datasets.WNC.interaction <- agebysex.all_datasets.WNC %>% filter(region %in% WNC_interaction_regions)

colorF = "#e67239"
colorM = "#0B8CACFF"
WNC.interaction.all_datasets.plots <- lapply(WNC_interaction_regions, plot_trajectories_bycov, df = agebysex.all_datasets.WNC, covariate = "sex", y.limits = range(agebysex.all_datasets.WNC$fitted), colorF, colorM, margin = 0)
names(WNC.interaction.all_datasets.plots) <- WNC_interaction_regions 
 
 
# get legend
y.limits = range(agebysex.all_datasets.WNC$fitted)
df_plot <- agebysex.all_datasets.WNC %>% filter(region %in% "17Networks_LH_VisCent_ExStr_3")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(aes(color = sex), linewidth = 3) +
    theme_classic() +
    scale_y_continuous(limits = y.limits) +
    scale_color_manual(values = c("Female" = colorF, "Male" = colorM)) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"))  
dev_traj_legend <- get_legend(plot)


WNC.interaction.all_datasets.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.interaction.all_datasets.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.interaction.all_datasets.plots.text <- annotate_figure(WNC.interaction.all_datasets.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("Developmental Patterns of Within Network Connectivity by Sex", size = 24))


plot_grid(WNC.interaction.all_datasets.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

 
```{r load netpair age by sex dev trajectories}
agebysex.all_datasets.netpair <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_fitted_%4$s.csv", output_root, "all_datasets", "networkpair", "schaefer200x17"))
agebysex.all_datasets.netpair <- agebysex.all_datasets.netpair %>% rename(age=smooth_var)

```

```{r netpair dev trajectories vis, fig.height = 25, fig.width = 15}
netpair_interaction_regions <- netpair_schaefer17 %>% filter(significant.fdr == 1) %>% pull(region) %>% gsub("_", " - ", .)
agebysex.all_datasets.netpair$region <- gsub("_", " - ", agebysex.all_datasets.netpair$region)
agebysex.all_datasets.netpair.interaction <- agebysex.all_datasets.netpair %>% filter(region %in% netpair_interaction_regions)

colorF = "#A51122FF"
colorM = "#0B8CACFF"
netpair.interaction.all_datasets.plots <- lapply(netpair_interaction_regions, plot_trajectories_bycov, df = agebysex.all_datasets.netpair, covariate = "sex", y.limits = range(agebysex.all_datasets.netpair$fitted), colorF, colorM, margin = 2)
names(netpair.interaction.all_datasets.plots) <- netpair_interaction_regions 

 
# get legend
y.limits = range(agebysex.all_datasets.netpair$fitted)
df_plot <- agebysex.all_datasets.netpair %>% filter(region %in% "defaultA - defaultA")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(aes(color = sex), linewidth = 3) +
    theme_classic() +
    scale_y_continuous(limits = y.limits) +
    scale_color_manual(values = c("Female" = colorF, "Male" = colorM)) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"))  

dev_traj_legend <- get_legend(plot)


netpair.interaction.all_datasets.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = netpair.interaction.all_datasets.plots, ncol = 2), nrow = 2, rel_heights = c(0.03, 1))
netpair.interaction.all_datasets.plots.text <- annotate_figure(netpair.interaction.all_datasets.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Connectivity between Pairs of Networks", size = 24, rot = 90),
                top = text_grob("Developmental Patterns of Within Network Connectivity by Sex", size = 24))


plot_grid(plot_grid(netpair.interaction.all_datasets.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05)), blank_space, ncol = 2, rel_widths = c(1, 0.05))

```
 
# Clinical measures exploration - just fyi
 
- To quantify whether pfactor and sex affect similar edges/networks: topographical overlap of effects
- To test whether one map statistically predicts another: spatial covariance structure

- Goal: Does the pattern of connections that differ by pfactor resemble the pattern that differs by sex?
```{r load edge sex, fig.height = 10, fig.width = 9}
# edge gam output
clinical.main.all_datasets.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_clinical_maineffects_schaefer200x17.csv", output_root, "all_datasets", "edge"))
clinical.main.all_datasets.edge_pfactor <- clinical.main.all_datasets.edge %>% filter(covariate == "p_factor_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
clinical.main.all_datasets.edge_int <- clinical.main.all_datasets.edge %>% filter(covariate == "internalizing_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
clinical.main.all_datasets.edge_ext <- clinical.main.all_datasets.edge %>% filter(covariate == "externalizing_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
clinical.main.all_datasets.edge_att <- clinical.main.all_datasets.edge %>% filter(covariate == "attention_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)

clinical.main.all_datasets.edge_sex <- clinical.main.all_datasets.edge %>% filter(covariate == "sex") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
 

# make df for plotting (and do FDR correction)
double.pfactor <- make_double_df(clinical.main.all_datasets.edge_pfactor, "edge", "pfactor", "All datasets")
double.int <- make_double_df(clinical.main.all_datasets.edge_int, "edge", "internalizing", "All datasets")
double.ext <- make_double_df(clinical.main.all_datasets.edge_ext, "edge", "externalizing", "All datasets")
double.att <- make_double_df(clinical.main.all_datasets.edge_att, "edge", "attention", "All datasets")
double.sex <- make_double_df(clinical.main.all_datasets.edge_sex, "edge", "sex", "All datasets")

pfactor_surf <- make_surface_plot(double.pfactor, dataset = "P-factor", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")

int_surf <- make_surface_plot(double.int, dataset = "Internalizing", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")
 
ext_surf <- make_surface_plot(double.ext, dataset = "Externalizing", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")
att_surf <- make_surface_plot(double.att, dataset = "Attention", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "")

row1_clinical <- plot_grid(pfactor_surf, int_surf, ncol=2)
row2_clinical <- plot_grid(ext_surf, att_surf, ncol=2)
plot_grid(row1_clinical, blank_space, row2_clinical, nrow = 3, rel_heights = c(1, 0.2, 1))
  
```


```{r pfactor explore, fig.height = 10, fig.width = 10}
 

PNC_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "PNC"))
HCPD_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "HCPD"))
NKI_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "NKI"))
HBN_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "HBN"))

################### 
# Define functions 
###################
# load pfactor data and merge with demographics
load_pfactor_data <- function(file_path) {
  pfactor <- fread(file_path)
  pfactor <- pfactor %>% rename(sub = participant_id)
  pfactor$sub <- paste0("sub-", pfactor$sub)
  pfactor <- pfactor %>% select(sub, p_factor_mcelroy_harmonized_all_samples, internalizing_mcelroy_harmonized_all_samples, externalizing_mcelroy_harmonized_all_samples, attention_mcelroy_harmonized_all_samples)
  pfactor <- pfactor[!duplicated(pfactor), ]
  pfactor <- pfactor[complete.cases(pfactor), ]
  return(pfactor)
}

# load demographics for all datasets and combine
PNC_demographics <- read.csv(PNC_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "PNC") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
NKI_demographics <- read.csv(NKI_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "NKI") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
HBN_demographics <- read.csv(HBN_config_data$demographics, stringsAsFactors = TRUE) %>% rename(site = ses) %>% mutate(dataset_site = paste0("HBN_", site)) %>% select(sub, age, sex, meanFD_avgSes, dataset_site)

#load clinical measures
PNC_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/PNC/sample_info/study-PNC_desc-participants.tsv")
NKI_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/NKI/sample_info/study-NKI_desc-participants.tsv")
NKI_pfactor$sub <- gsub("sub-", "", NKI_pfactor$sub)
HBN_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/HBN/sample_info/study-HBN_desc-participants.tsv")

PNC_demographics <- inner_join(PNC_pfactor, PNC_demographics,by = "sub")
NKI_demographics <- inner_join(NKI_pfactor, NKI_demographics,by = "sub")
HBN_demographics <- inner_join(HBN_pfactor, HBN_demographics,by = "sub")

demographics <- rbind(PNC_demographics, NKI_demographics, HBN_demographics)
# load demographics for all datasets and combine
PNC_demographics <- read.csv(PNC_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "PNC") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
NKI_demographics <- read.csv(NKI_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "NKI") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
HBN_demographics <- read.csv(HBN_config_data$demographics, stringsAsFactors = TRUE) %>% rename(site = ses) %>% mutate(dataset_site = paste0("HBN_", site)) %>% select(sub, age, sex, meanFD_avgSes, dataset_site)

#load clinical measures
PNC_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/PNC/sample_info/study-PNC_desc-participants.tsv")
NKI_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/NKI/sample_info/study-NKI_desc-participants.tsv")
NKI_pfactor$sub <- gsub("sub-", "", NKI_pfactor$sub)
HBN_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/HBN/sample_info/study-HBN_desc-participants.tsv")

PNC_demographics <- inner_join(PNC_pfactor, PNC_demographics,by = "sub")
NKI_demographics <- inner_join(NKI_pfactor, NKI_demographics,by = "sub")
HBN_demographics <- inner_join(HBN_pfactor, HBN_demographics,by = "sub")

demographics <- rbind(PNC_demographics, NKI_demographics, HBN_demographics)



pfactor_plot <- ggplot(demographics, aes(x = sex, y = p_factor_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "P-factor by Sex",
       x = "Sex", y = "P-factor (McElroy Harmonized)") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))



int_plot <- ggplot(demographics, aes(x = sex, y = internalizing_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Internalizing by Sex",
       x = "Sex", y = "Internalizing") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))


ext_plot <- ggplot(demographics, aes(x = sex, y = externalizing_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Externalizing by Sex",
       x = "Sex", y = "Externalizing") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))

att_plot <- ggplot(demographics, aes(x = sex, y = attention_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Attention by Sex",
       x = "Sex", y = "Attention") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))

plot_grid(pfactor_plot, int_plot, ext_plot, att_plot, ncol=2)

```
 

```{r}
library(ggpubr)
library(dplyr)
library(effsize)

 
# Compute t-test and effect size
t_out <- t.test(p_factor_mcelroy_harmonized_all_samples ~ sex, data = demographics)
cohen_d <- effsize::cohen.d(p_factor_mcelroy_harmonized_all_samples ~ sex, data = demographics)$estimate
 

p_str <- ifelse(t_out$p.value < 0.0001, "< 0.0001",
                sprintf("%.3f", t_out$p.value))

stat_label <- sprintf(
  "t(%.0f) = %.2f, p %s, Cohen's d = %.2f",
  t_out$parameter,
  t_out$statistic,
  p_str,
  cohen_d
)
 
 
```

