---
title: "Sex differences in functional connectivity development"
author: "Audrey Luo"
output: 
  html_document:
    highlight: haddock
    code_folding: hide
    number_sections: no
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    number_sections: no
    toc: yes
    toc_depth: '4'
  word_document:
    toc: yes
    toc_depth: '4'
urlcolor: blue
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
# install pacman if not already installed
if (!require("pacman")) {
  install.packages("pacman")
}

# not sure why, but cifti tools needs to be called this way in order for commands to work (and not part of pacman) - *shrug*
library(ciftiTools)
#ciftiTools.setOption('wb_path', '/Applications/workbench/')
library(cifti)

# use pacman to load/install required packages
pacman::p_load(
  cowplot, data.table, dplyr, ggplot2, ggrepel, ggpubr, ggseg, ggsegSchaefer, 
  glue, grid, gridExtra, gratia, knitr, kableExtra, mgcv, RColorBrewer, paletteer, pammtools, reshape2, scales, 
  stringr, rjson, tidyr
)
 
source("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/results/sex_diff_dev_figures_exploratory.R")
source("/cbica/projects/network_replication/software/perm.sphere.p.R")

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, include = TRUE) 


proj_root <- "/cbica/projects/network_replication/covariate_analyses/sex_diff/"
input_root <- paste0(proj_root, "input")
output_root <- paste0(proj_root, "output")
 
```

```{r load SAaxis and labels and spin test}
# load S-A axis
schaefer200_SAaxis <- read.csv("/cbica/projects/network_replication/SAaxis/schaefer200x7_SAaxis.csv")
schaefer200_SAaxis <- schaefer200_SAaxis %>% rename(region=label)

schaefer200x17_SAaxis <- read.csv("/cbica/projects/network_replication/SAaxis/schaefer200x17_SAaxis.csv")
schaefer200x17_SAaxis <- schaefer200x17_SAaxis %>% rename(region=label)

# load parcel labels (schaefer 200x7 labels are in the same ordering as schaefer 200x17)
schaefer200.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_regionlist_final.csv")
schaefer200.labels <- schaefer200.labels$label
  
# load edge labels 
schaefer200.edge.labels <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer200x7_edge.csv")
schaefer200.edge.labels <- schaefer200.edge.labels[,2] 
schaefer200.edge.labels <- gsub("7Networks", "Networks", schaefer200.edge.labels)
  
# load network-pair labels
schaefer200.networkpair.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_netpair_labels.csv")
schaefer200.networkpair.labels <- schaefer200.networkpair.labels[,1]

# load permuted schaefer200
perm.id.full_schaefer200 <- readRDS("/cbica/projects/network_replication/software/rotate_parcellation/schaefer200x7.coords_sphericalrotations_N10k_seed10.rds")

 
```


# 1. Mean connectivity matrices for males and females 
```{r load mean matrices}
PNC_mean_matrix_female <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/PNC_mean_connmatrix_female.rds', "PNC"))
PNC_mean_matrix_male <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/PNC_mean_connmatrix_male.rds', "PNC"))

HCPD_mean_matrix_female <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/HCPD_mean_connmatrix_female.rds', "HCPD"))
HCPD_mean_matrix_male <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/HCPD_mean_connmatrix_male.rds', "HCPD"))

NKI_mean_matrix_female <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/NKI_mean_connmatrix_female.rds', "NKI"))
NKI_mean_matrix_male <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/NKI_mean_connmatrix_male.rds', "NKI"))

HBN_mean_matrix_female <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/HBN_mean_connmatrix_female.rds', "HBN"))
HBN_mean_matrix_male <- readRDS(sprintf('/cbica/projects/network_replication/covariate_analyses/sex_diff/input/%s/mean_matrices/HBN_mean_connmatrix_male.rds', "HBN"))
```


```{r format mean matrices}
PNC_mean_matrix_female <- format_mean_matrix(PNC_mean_matrix_female)
PNC_mean_matrix_male <- format_mean_matrix(PNC_mean_matrix_male)

HCPD_mean_matrix_female <- format_mean_matrix(HCPD_mean_matrix_female)
HCPD_mean_matrix_male <- format_mean_matrix(HCPD_mean_matrix_male)

NKI_mean_matrix_female <- format_mean_matrix(NKI_mean_matrix_female)
NKI_mean_matrix_male <- format_mean_matrix(NKI_mean_matrix_male)

HBN_mean_matrix_female <- format_mean_matrix(HBN_mean_matrix_female)
HBN_mean_matrix_male <- format_mean_matrix(HBN_mean_matrix_male)

```


 
## Mean heatmaps for males and females
- females tend to have more negative connectivity between networks (more blue) than males.
```{r plot mean matrices heatmaps, fig.height = 12, fig.width = 17}
ylim1 = -0.5
ylim2 = 1
 
# plot female and male plots for each dataset
PNC_heatmaps <- annotate_figure(plot_grid(plot_mean_matrix(PNC_mean_matrix_female, ylim1 = ylim1, ylim2 = ylim2, "Female"), 
          plot_mean_matrix(PNC_mean_matrix_male, ylim1 = ylim1, ylim2 = ylim2, "Male"), ncol = 2), 
          top = text_grob("PNC", size = 20, face = "bold"))

HCPD_heatmaps <- annotate_figure(plot_grid(plot_mean_matrix(HCPD_mean_matrix_female, ylim1 = ylim1, ylim2 = ylim2, "Female"), 
          plot_mean_matrix(HCPD_mean_matrix_male, ylim1 = ylim1, ylim2 = ylim2, "Male"), ncol = 2), 
          top = text_grob("HCPD", size = 20, face = "bold"))

NKI_heatmaps <- annotate_figure(plot_grid(plot_mean_matrix(NKI_mean_matrix_female, ylim1 = ylim1, ylim2 = ylim2, "Female"), 
          plot_mean_matrix(NKI_mean_matrix_male, ylim1 = ylim1, ylim2 = ylim2, "Male"), ncol = 2), 
          top = text_grob("NKI", size = 20, face = "bold"))

HBN_heatmaps <- annotate_figure(plot_grid(plot_mean_matrix(HBN_mean_matrix_female, ylim1 = ylim1, ylim2 = ylim2, "Female"), 
          plot_mean_matrix(HBN_mean_matrix_male, ylim1 = ylim1, ylim2 = ylim2, "Male"), ncol = 2), 
          top = text_grob("HBN", size = 20, face = "bold"))

# put the plots together
blank_space <- ggplot() + theme_void()

all_mean_heatmaps <- plot_grid(PNC_heatmaps, blank_space, HCPD_heatmaps, NKI_heatmaps, blank_space, HBN_heatmaps,  nrow = 2, rel_widths = c(1, 0.05, 1))


# get common legend
mat = HBN_mean_matrix_female
orig_rows <- rownames(mat)
orig_cols <- colnames(mat)
row_net <- map_network7(orig_rows)
col_net <- map_network7(orig_cols)    
net_order <- c("Visual","SomMot","DorsAttn","SalVentAttn", "Frontoparietal","Default", "Limbic")
row_order <- order(factor(row_net, levels = net_order), seq_along(row_net))
col_order <- order(factor(col_net, levels = net_order), seq_along(col_net))
mat_ord <- mat[row_order, col_order]
row_net_o <- row_net[row_order]
col_net_o <- col_net[col_order]
r_rows <- runs_info(row_net_o)
r_cols <- runs_info(col_net_o)
y_bounds <- r_rows$ends + 0.5
x_bounds <- r_cols$ends + 0.5

df <- expand.grid(Col = seq_len(ncol(mat_ord)), Row = seq_len(nrow(mat_ord)))
df$Value <- as.vector(mat_ord)

plot <- ggplot(df, aes(x = Col, y = Row, fill = Value)) +
  geom_tile() +
  scale_fill_gradientn(
    colours = c("#6200D9", "white", "#FF681C"),
    values  = rescale(c(ylim1, 0, ylim2)),
    limits  = c(ylim1, ylim2),
    oob     = squish,
    na.value = "white",
    name = "Correlation",                        
    breaks = c(ylim1, 0, ylim2),                  
    labels = c(round(ylim1, 2), "0", round(ylim2, 2))   
  ) +
  coord_equal() +
  theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))

legend <- get_legend(plot)

annotate_figure(plot_grid(all_mean_heatmaps, legend, blank_space, nrow = 3, rel_heights = c(1, 0.05, 0.04)), 
                  bottom = text_grob("Correlation", size = 24))
```

## Difference heatmaps between males and females
```{r compute and plot difference heatmaps, fig.height = 10, fig.width = 10}
# compute difference matrices
diff_matrix_PNC <- PNC_mean_matrix_female - PNC_mean_matrix_male
diff_matrix_HCPD <- HCPD_mean_matrix_female - HCPD_mean_matrix_male
diff_matrix_NKI <- NKI_mean_matrix_female - NKI_mean_matrix_male
diff_matrix_HBN <- HBN_mean_matrix_female - HBN_mean_matrix_male

# plot each diff heatmap
PNC_diff_heatmap <- plot_mean_matrix(diff_matrix_PNC, ylim1 = -0.12, ylim2 = 0.12, "PNC") 
HCPD_diff_heatmap <- plot_mean_matrix(diff_matrix_HCPD, ylim1 = -0.12, ylim2 = 0.12, "HCP-D") 
NKI_diff_heatmap <- plot_mean_matrix(diff_matrix_NKI, ylim1 = -0.12, ylim2 = 0.12, "NKI") 
HBN_diff_heatmap <- plot_mean_matrix(diff_matrix_HBN, ylim1 = -0.12, ylim2 = 0.12, "HBN") 

# get legend
plot <- ggplot(df, aes(x = Col, y = Row, fill = Value)) +
  geom_tile() +
  scale_fill_gradientn(
    colours = c("#6200D9", "white", "#FF681C"),
    values  = rescale(c(-0.12, 0, 0.12)),
    limits  = c(-0.12, 0.12),
    oob     = squish,
    na.value = "white",
    name = "Correlation",                        
    breaks = c(-0.12, 0, 0.12),                  
    labels = c(round(-0.12, 2), "0", round(0.12, 2))   
  ) +
  coord_equal() +
  theme(legend.title = element_blank(),
          legend.text = element_text(size = 20),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(0.75, 'cm'),
        legend.key.width = unit(1.5, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))

legend <- get_legend(plot)

all_diff_heatmaps <- plot_grid(PNC_diff_heatmap, blank_space, HCPD_diff_heatmap, NKI_diff_heatmap, blank_space, HBN_diff_heatmap, nrow = 2, rel_widths = c(1, 0.05, 1))

annotate_figure(plot_grid(all_diff_heatmaps, legend, blank_space, nrow = 3, rel_heights = c(1, 0.02, 0.04)),
                 bottom = text_grob("Females < Males             Female > Males", size = 20))
```

## Difference heatmap for specific pairs of networks
- DMN is consistently higher in females 
```{r compute and plot difference heatmaps for networkpairs, fig.height = 10, fig.width = 10}
PNC_diff_heatmap_networkpairs <- plot_network_diff(PNC_mean_matrix_female, PNC_mean_matrix_male, map_network7, triangle = "upper", limits = c(-0.02, 0.01), title = "PNC")
 
HCPD_diff_heatmap_networkpairs <- plot_network_diff(HCPD_mean_matrix_female, HCPD_mean_matrix_male, map_network7, triangle = "upper", limits = c(-0.02, 0.01), title = "HCP-D")

NKI_diff_heatmap_networkpairs <- plot_network_diff(NKI_mean_matrix_female, NKI_mean_matrix_male, map_network7, triangle = "upper", limits = c(-0.02, 0.01), title = "NKI")

HBN_diff_heatmap_networkpairs <- plot_network_diff(HBN_mean_matrix_female, HBN_mean_matrix_male, map_network7, triangle = "upper", limits = c(-0.02, 0.01), title = "HBN")

# get legend
ylim1 = -0.02
ylim2 = 0.01
df <- data.frame(x = 1, y = 1, val = 0)

p <- ggplot(df, aes(x, y, fill = val)) +
  geom_tile() +
  scale_fill_gradientn(
    colours = c("#02B0DB","white","#FF8D6E"),
    values  = rescale(c(ylim1, 0, ylim2)),
    limits  = c(ylim1, ylim2),
    oob     = squish,
    na.value = "white",
    name = ""
  ) +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.width = unit(2, "cm"),
    legend.key.height = unit(0.6, "cm"),
    legend.title = element_blank(),
    legend.text  = element_text(size = 20)
  )

legend <- get_legend(p)

all_diff_heatmaps_networkpairs <- plot_grid(PNC_diff_heatmap_networkpairs, 
                                            blank_space,
                                            HCPD_diff_heatmap_networkpairs, 
                                            NKI_diff_heatmap_networkpairs, 
                                            blank_space, HBN_diff_heatmap_networkpairs, 
                                            nrow = 2, rel_widths = c(1, 0.05, 1))

annotate_figure(plot_grid(blank_space, all_diff_heatmaps_networkpairs, legend, blank_space, nrow = 4, rel_heights = c(0.03, 1, 0.02, 0.04)), bottom = text_grob("Females < Males             Female > Males", size = 20), top = text_grob("Difference between Females and Males", size = 20, hjust = 0.4, face = "bold"))
```
  

# 2. Sex effect (t-value) across cortex (PNC, HCPD, NKI, HBN)

## 2.1 Functional connectivity strength (or global brain connectivity/GBC)
```{r load GBC sex}
sex.main.PNC.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "PNC", "GBC"))
sex.main.PNC.GBC$region <- paste0("7", sex.main.PNC.GBC$region)
sex.main.PNC.GBC <- sig.effects(sex.main.PNC.GBC, "GBC", "sex", "PNC")

sex.main.HCPD.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HCPD", "GBC"))
sex.main.HCPD.GBC <- sig.effects(sex.main.HCPD.GBC, "GBC", "sex", "HCPD")
sex.main.HCPD.GBC$region <- paste0("7", sex.main.HCPD.GBC$region)

sex.main.HBN.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HBN", "GBC"))
sex.main.HBN.GBC <- sig.effects(sex.main.HBN.GBC, "GBC", "sex", "HBN")
sex.main.HBN.GBC$region <- paste0("7", sex.main.HBN.GBC$region)

sex.main.NKI.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "NKI", "GBC"))
sex.main.NKI.GBC <- sig.effects(sex.main.NKI.GBC, "GBC", "sex", "NKI")
sex.main.NKI.GBC$region <- paste0("7", sex.main.NKI.GBC$region)

 
```

```{r plot GBC sex, fig.width = 15, fig.height = 15}

sex.main.PNC.GBC_lh <- plot_cortex(sex.main.PNC.GBC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 
sex.main.PNC.GBC_rh <- plot_cortex(sex.main.PNC.GBC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 

sex.main.HCPD.GBC_lh <- plot_cortex(sex.main.HCPD.GBC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 
sex.main.HCPD.GBC_rh <- plot_cortex(sex.main.HCPD.GBC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 

sex.main.NKI.GBC_lh <- plot_cortex(sex.main.NKI.GBC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 
sex.main.NKI.GBC_rh <- plot_cortex(sex.main.NKI.GBC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 

sex.main.HBN.GBC_lh <- plot_cortex(sex.main.HBN.GBC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 
sex.main.HBN.GBC_rh <- plot_cortex(sex.main.HBN.GBC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 8, atlas = "schaefer7_200") 
 
# legend
ylim1 = -2
ylim2 = 8
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.GBC, atlas = schaefer7_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = c("#FF8D6E", "white", "#02B0DB"), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)
blank_space <- ggplot() + theme_void()



annotate_figure(plot_grid(blank_space, plot_grid(
  annotate_figure(plot_grid(sex.main.PNC.GBC_lh, sex.main.PNC.GBC_rh, ncol = 2), 
                  top = text_grob("PNC", size = 24)),
  annotate_figure(plot_grid(sex.main.HCPD.GBC_lh, sex.main.HCPD.GBC_rh, ncol = 2), 
                  top = text_grob("HCP-D", size = 24)),
  annotate_figure(plot_grid(sex.main.NKI.GBC_lh, sex.main.NKI.GBC_rh, ncol = 2), 
                  top = text_grob("NKI", size = 24)),
  annotate_figure(plot_grid(sex.main.HBN.GBC_lh, sex.main.HBN.GBC_rh, ncol = 2), 
                  top = text_grob("HBN", size = 24)),
  ncol = 2), 
  legend, 
  blank_space, 
  nrow = 4, 
  rel_heights = c(0.05, 1, 0.2, 0.05)), 
  bottom = text_grob("Sex Effect (t-value)", size = 24), 
  top = text_grob("Functional Connectivity Strength", size = 24, face = "bold"))
```


## 2.2 Between-network connectivity
```{r load BNC sex}
sex.main.PNC.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "PNC", "BNC"))
sex.main.PNC.BNC$region <- paste0("7", sex.main.PNC.BNC$region)
sex.main.PNC.BNC <- sig.effects(sex.main.PNC.BNC, "BNC", "sex", "PNC")

sex.main.HCPD.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HCPD", "BNC"))
sex.main.HCPD.BNC <- sig.effects(sex.main.HCPD.BNC, "BNC", "sex", "HCPD")
sex.main.HCPD.BNC$region <- paste0("7", sex.main.HCPD.BNC$region)

sex.main.HBN.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HBN", "BNC"))
sex.main.HBN.BNC <- sig.effects(sex.main.HBN.BNC, "BNC", "sex", "HBN")
sex.main.HBN.BNC$region <- paste0("7", sex.main.HBN.BNC$region)

sex.main.NKI.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "NKI", "BNC"))
sex.main.NKI.BNC <- sig.effects(sex.main.NKI.BNC, "BNC", "sex", "NKI")
sex.main.NKI.BNC$region <- paste0("7", sex.main.NKI.BNC$region)

range(sex.main.PNC.BNC$GAM.cov.tvalue)
range(sex.main.HCPD.BNC$GAM.cov.tvalue)
range(sex.main.HBN.BNC$GAM.cov.tvalue)
range(sex.main.NKI.BNC$GAM.cov.tvalue)
```

```{r plot BNC sex, fig.width = 15, fig.height = 15}

sex.main.PNC.BNC_lh <- plot_cortex(sex.main.PNC.BNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 
sex.main.PNC.BNC_rh <- plot_cortex(sex.main.PNC.BNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 

sex.main.HCPD.BNC_lh <- plot_cortex(sex.main.HCPD.BNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 
sex.main.HCPD.BNC_rh <- plot_cortex(sex.main.HCPD.BNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 

sex.main.NKI.BNC_lh <- plot_cortex(sex.main.NKI.BNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 
sex.main.NKI.BNC_rh <- plot_cortex(sex.main.NKI.BNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 

sex.main.HBN.BNC_lh <- plot_cortex(sex.main.HBN.BNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 
sex.main.HBN.BNC_rh <- plot_cortex(sex.main.HBN.BNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -2, ylim2 = 9, atlas = "schaefer7_200") 
 
# legend
ylim1 = -2
ylim2 = 9
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.GBC, atlas = schaefer7_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = c("#FF8D6E", "white", "#02B0DB"), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)
blank_space <- ggplot() + theme_void()



annotate_figure(plot_grid(blank_space, plot_grid(
  annotate_figure(plot_grid(sex.main.PNC.BNC_lh, sex.main.PNC.BNC_rh, ncol = 2), 
                  top = text_grob("PNC", size = 24)),
  annotate_figure(plot_grid(sex.main.HCPD.BNC_lh, sex.main.HCPD.BNC_rh, ncol = 2), 
                  top = text_grob("HCP-D", size = 24)),
  annotate_figure(plot_grid(sex.main.NKI.BNC_lh, sex.main.NKI.BNC_rh, ncol = 2), 
                  top = text_grob("NKI", size = 24)),
  annotate_figure(plot_grid(sex.main.HBN.BNC_lh, sex.main.HBN.BNC_rh, ncol = 2), 
                  top = text_grob("HBN", size = 24)),
  ncol = 2), 
  legend, 
  blank_space, 
  nrow = 4, 
  rel_heights = c(0.05, 1, 0.2, 0.05)), 
  bottom = text_grob("Sex Effect (t-value)", size = 24), 
  top = text_grob("Between Network Connectivity", size = 24, face = "bold"))
```


## 2.3 Within-network connectivity
```{r load WNC sex}
sex.main.PNC.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "PNC", "WNC"))
sex.main.PNC.WNC$region <- paste0("7", sex.main.PNC.WNC$region)
sex.main.PNC.WNC <- sig.effects(sex.main.PNC.WNC, "WNC", "sex", "PNC")


sex.main.HCPD.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HCPD", "WNC"))
sex.main.HCPD.WNC <- sig.effects(sex.main.HCPD.WNC, "WNC", "sex", "HCPD")
sex.main.HCPD.WNC$region <- paste0("7", sex.main.HCPD.WNC$region)

sex.main.HBN.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HBN", "WNC"))
sex.main.HBN.WNC <- sig.effects(sex.main.HBN.WNC, "WNC", "sex", "HBN")
sex.main.HBN.WNC$region <- paste0("7", sex.main.HBN.WNC$region)

sex.main.NKI.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "NKI", "WNC"))
sex.main.NKI.WNC <- sig.effects(sex.main.NKI.WNC, "WNC", "sex", "NKI")
sex.main.NKI.WNC$region <- paste0("7", sex.main.NKI.WNC$region)

range(sex.main.PNC.WNC$GAM.cov.tvalue)
range(sex.main.HCPD.WNC$GAM.cov.tvalue)
range(sex.main.HBN.WNC$GAM.cov.tvalue)
range(sex.main.NKI.WNC$GAM.cov.tvalue)

```

```{r plot WNC sex, fig.width = 15, fig.height = 15}

sex.main.PNC.WNC_lh <- plot_cortex(sex.main.PNC.WNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 
sex.main.PNC.WNC_rh <- plot_cortex(sex.main.PNC.WNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 

sex.main.HCPD.WNC_lh <- plot_cortex(sex.main.HCPD.WNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 
sex.main.HCPD.WNC_rh <- plot_cortex(sex.main.HCPD.WNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 

sex.main.NKI.WNC_lh <- plot_cortex(sex.main.NKI.WNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 
sex.main.NKI.WNC_rh <- plot_cortex(sex.main.NKI.WNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 

sex.main.HBN.WNC_lh <- plot_cortex(sex.main.HBN.WNC, hemi = "left", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 
sex.main.HBN.WNC_rh <- plot_cortex(sex.main.HBN.WNC, hemi = "right", measure = "cov_sig_effect", ylim1 = -9, ylim2 = 7, atlas = "schaefer7_200") 
 
# legend
ylim1 = -9
ylim2 = 7
p <- ggplot() + 
    geom_brain(data = sex.main.HBN.GBC, atlas = schaefer7_200, 
               mapping=aes(fill=GAM.cov.tvalue), 
               show.legend=TRUE) +
     scale_fill_gradientn(colours = c("#FF8D6E", "white", "#02B0DB"), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") + 
    theme_void()  +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm"))
  
legend <- get_legend(p)
blank_space <- ggplot() + theme_void()



annotate_figure(plot_grid(blank_space, plot_grid(
  annotate_figure(plot_grid(sex.main.PNC.WNC_lh, sex.main.PNC.WNC_rh, ncol = 2), 
                  top = text_grob("PNC", size = 24)),
  annotate_figure(plot_grid(sex.main.HCPD.WNC_lh, sex.main.HCPD.WNC_rh, ncol = 2), 
                  top = text_grob("HCP-D", size = 24)),
  annotate_figure(plot_grid(sex.main.NKI.WNC_lh, sex.main.NKI.WNC_rh, ncol = 2), 
                  top = text_grob("NKI", size = 24)),
  annotate_figure(plot_grid(sex.main.HBN.WNC_lh, sex.main.HBN.WNC_rh, ncol = 2), 
                  top = text_grob("HBN", size = 24)),
  ncol = 2), 
  legend, 
  blank_space, 
  nrow = 4, 
  rel_heights = c(0.05, 1, 0.2, 0.05)), 
  bottom = text_grob("Sex Effect (t-value)", size = 24), 
  top = text_grob("Within Network Connectivity", size = 24, face = "bold"))
```
- rob bragas: subnetworks of DMN -- 17 network


## 2.4 Between specific pairs of networks
```{r load networkpair sex for 7 networks}
num_networks = 7
sex.main.PNC.networkpair.7 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "PNC", "networkpair", num_networks))
sex.main.HCPD.networkpair.7 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HCPD", "networkpair", num_networks))
sex.main.NKI.networkpair.7 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "NKI", "networkpair", num_networks))
sex.main.HBN.networkpair.7 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HBN", "networkpair", num_networks))

# make two new columns identifying network 1 and network 2
sex.main.PNC.networkpair.7<- sex.main.PNC.networkpair.7%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HCPD.networkpair.7<- sex.main.HCPD.networkpair.7%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.NKI.networkpair.7<- sex.main.NKI.networkpair.7%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HBN.networkpair.7<- sex.main.HBN.networkpair.7%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))

# fdr correction on non-duplicated pairs only and sorts pairs
sex.main.PNC.networkpair.7<- prep_networkpair_df(sex.main.PNC.networkpair.7, "networkpair", "sex", "PNC")
sex.main.HCPD.networkpair.7<- prep_networkpair_df(sex.main.HCPD.networkpair.7,  "networkpair", "sex", "HCPD")
sex.main.NKI.networkpair.7<- prep_networkpair_df(sex.main.NKI.networkpair.7,  "networkpair", "sex", "NKI")
sex.main.HBN.networkpair.7<- prep_networkpair_df(sex.main.HBN.networkpair.7,  "networkpair", "sex", "HBN")


range(sex.main.PNC.networkpair.7$GAM.cov.tvalue)
range(sex.main.HCPD.networkpair.7$GAM.cov.tvalue)
range(sex.main.NKI.networkpair.7$GAM.cov.tvalue)
range(sex.main.HBN.networkpair.7$GAM.cov.tvalue)

```


```{r plot networkpair sex for 7 networks, fig.width = 17, fig.height = 20}
combined_networkpair_plots <- plot_grid(
    annotate_figure(make_networkpair7_plot(sex.main.PNC.networkpair.7, dataset = "PNC", ylim1 = -6, ylim2 = 7), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)),
    annotate_figure(make_networkpair7_plot(sex.main.HCPD.networkpair.7, dataset = "HCP-D", ylim1 = -6, ylim2 = 7), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)),
    annotate_figure(make_networkpair7_plot(sex.main.NKI.networkpair.7, dataset = "NKI", ylim1 = -6, ylim2 = 7), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)),
  annotate_figure(make_networkpair7_plot(sex.main.HBN.networkpair.7, dataset = "HBN", ylim1 = -6, ylim2 = 7), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)), ncol = 2)


annotate_figure(plot_grid(blank_space, combined_networkpair_plots, nrow = 2, rel_heights = c(0.05, 1)), top = text_grob("Connectivity Between Specific 7 Network Pairs", size = 30, face = "bold", x = 0.6))

```

 
 
```{r load networkpair sex for 17 networks}
num_networks = 17
sex.main.PNC.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "PNC", "networkpair", num_networks))
sex.main.HCPD.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HCPD", "networkpair", num_networks))
sex.main.NKI.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "NKI", "networkpair", num_networks))
sex.main.HBN.networkpair.17 <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects_schaefer200x%4$s.csv", output_root, "HBN", "networkpair", num_networks))

# make two new columns identifying network 1 and network 2
sex.main.PNC.networkpair.17<- sex.main.PNC.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HCPD.networkpair.17<- sex.main.HCPD.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.NKI.networkpair.17<- sex.main.NKI.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))
sex.main.HBN.networkpair.17<- sex.main.HBN.networkpair.17%>% 
  mutate(network1 = str_extract(region, "[[:alpha:]]+"), network2=str_extract(region, "(?<=_).*"))

# fdr correction on non-duplicated pairs only and sorts pairs
sex.main.PNC.networkpair.17<- prep_networkpair_df(sex.main.PNC.networkpair.17, "networkpair", "sex", "PNC")
sex.main.HCPD.networkpair.17<- prep_networkpair_df(sex.main.HCPD.networkpair.17,  "networkpair", "sex", "HCPD")
sex.main.NKI.networkpair.17<- prep_networkpair_df(sex.main.NKI.networkpair.17,  "networkpair", "sex", "NKI")
sex.main.HBN.networkpair.17<- prep_networkpair_df(sex.main.HBN.networkpair.17,  "networkpair", "sex", "HBN")


range(sex.main.PNC.networkpair.17$GAM.cov.tvalue)
range(sex.main.HCPD.networkpair.17$GAM.cov.tvalue)
range(sex.main.NKI.networkpair.17$GAM.cov.tvalue)
range(sex.main.HBN.networkpair.17$GAM.cov.tvalue)

```


```{r plot networkpair sex for 17 networks, fig.width = 17, fig.height = 20}
combined_networkpair_plots <- plot_grid(
    annotate_figure(make_networkpair17_plot(sex.main.PNC.networkpair.17, dataset = "PNC", ylim1 = -11, ylim2 = 10), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)),
    annotate_figure(make_networkpair17_plot(sex.main.HCPD.networkpair.17, dataset = "HCP-D", ylim1 = -11, ylim2 = 10), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)),
    annotate_figure(make_networkpair17_plot(sex.main.NKI.networkpair.17, dataset = "NKI", ylim1 = -11, ylim2 = 10), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)),
  annotate_figure(make_networkpair17_plot(sex.main.HBN.networkpair.17, dataset = "HBN", ylim1 = -11, ylim2 = 10), bottom = text_grob("Sex Effect (t-value)", x = 0.62, size = 24)), ncol = 2)


annotate_figure(plot_grid(blank_space, combined_networkpair_plots, nrow = 2, rel_heights = c(0.05, 1)), top = text_grob("Connectivity Between Specific 17 Network Pairs", size = 30, face = "bold", x = 0.6))

```
- within network connectivity for DMN A is higher in females across all datasets. DMN B and C trend in the same direction but not consistently significant.  
- within network connectivity for Limbic temporopolar is higher in males across all datasets. 
- connectivity between DMN A and salience vent attn A and B is higher in males across all datasets. 
- connectivity between DMN A and dors vent attn A and B is higher in males in 3 of 4 datasets (trends in same direction in NKI). 
- connectivity between DMN A and visual peripheral is also higher in males across all datasets (DMN A - visual central is sig for 3/4 datasets).  
- NKI is not well powered but trends generally in the same direction as the other datasets. 


### Visualizing each of the networks of interest
```{r visualze networks, fig.height = 20, fig.width = 20}
schaefer200x17.labels <- read.csv(sprintf("/cbica/projects/network_replication/atlases/parcellations/schaefer200x%s_regionlist_final.csv", 17))
schaefer200x17.labels <- data.frame(cbind(map_network17(schaefer200x17.labels$label), schaefer200x17.labels$label)) %>% setNames(c("network", "region"))
schaefer200x17.labels$region <- paste0("17", schaefer200x17.labels$region)
 

plot_grid(
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "defaultA", color1 = "#C73000FF"),  
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "defaultB", color1 = "#C73000FF"), 
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "defaultC", color1 = "#C73000FF"), 
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "limbicTemporopolar", color1 = "#C73000FF"),
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "frontoparietalControlB", color1 = "#C73000FF"),
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "salienceVentralAttentionA", color1 = "#EEAC32FF"), 
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "salienceVentralAttentionB", color1 = "#EEAC32FF"), 
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "dorsalAttentionA", color1 = "#EEAC32FF"), 
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "dorsalAttentionB", color1 = "#EEAC32FF"), 
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "visualCentral", color1 = "#24A6A8FF"), 
visualize_schaefer17_network(schaefer200x17.labels, network_to_plot = "visualPeripheral", color1 = "#24A6A8FF"), nrow = 4) 


```


## Seed-based analysis: sex differences in connectivity between specific region to all others regions
- plot a few common regions that were significant across datasets

```{r load files for WNC DMN seed based analysis}
sex.main.PNC.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "PNC", "edge"))
sex.main.HCPD.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HCPD", "edge"))
sex.main.NKI.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "NKI", "edge"))
sex.main.HBN.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HBN", "edge"))


gam.edge.PNC <- prep_edge_dfs(sex.main.PNC.edge, fc_measure = "Edge", covariate = "sex", dataset = "PNC") 
gam.edge.HCPD <- prep_edge_dfs(sex.main.HCPD.edge, fc_measure = "Edge", covariate = "sex", dataset = "HCPD") 
gam.edge.NKI <- prep_edge_dfs(sex.main.NKI.edge, fc_measure = "Edge", covariate = "sex", dataset = "NKI") 
gam.edge.HBN <- prep_edge_dfs(sex.main.HBN.edge, fc_measure = "Edge", covariate = "sex", dataset = "HBN") 
```

```{r WNC DMN seed based analysis, fig.height= 6, fig.width= 10}
# note that i'm back to working with 7 networks here
PNC_dmn <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Default")) %>% pull(region)
HCPD_dmn <- sex.main.HCPD.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Default")) %>% pull(region)
NKI_dmn <- sex.main.NKI.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Default")) %>% pull(region)
HBN_dmn <- sex.main.HBN.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Default")) %>% pull(region)

overlap_dmn <- Reduce(intersect, list(PNC_dmn, HCPD_dmn, NKI_dmn, HBN_dmn))
overlap_dmn <- gsub("7Network", "Network", overlap_dmn)
 
default1_PNC <- view_age_effect(df = gam.edge.PNC, parcel=overlap_dmn[1], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "PNC")
default1_NKI <- view_age_effect(df = gam.edge.NKI, parcel=overlap_dmn[1], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "NKI")
default1_HCPD <- view_age_effect(df = gam.edge.HCPD, parcel=overlap_dmn[1], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "HCP-D")
default1_HBN <- view_age_effect(df = gam.edge.HBN, parcel=overlap_dmn[1], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "HBN")

 
default2_PNC <- view_age_effect(df = gam.edge.PNC, parcel=overlap_dmn[2], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "PNC")
default2_NKI <- view_age_effect(df = gam.edge.NKI, parcel=overlap_dmn[2], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "NKI")
default2_HCPD <- view_age_effect(df = gam.edge.HCPD, parcel=overlap_dmn[2], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "HCP-D")
default2_HBN <- view_age_effect(df = gam.edge.HBN, parcel=overlap_dmn[2], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "HBN")


default3_PNC <- view_age_effect(df = gam.edge.PNC, parcel=overlap_dmn[3], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "PNC")
default3_NKI <- view_age_effect(df = gam.edge.NKI, parcel=overlap_dmn[3], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "NKI")
default3_HCPD <- view_age_effect(df = gam.edge.HCPD, parcel=overlap_dmn[3], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "HCP-D")
default3_HBN <- view_age_effect(df = gam.edge.HBN, parcel=overlap_dmn[3], measure = "GAM.cov.tvalue", legend_title = "Sex Effect (t-value)", dataset = "HBN")

 
plot_grid(default1_PNC, default1_HCPD, default1_NKI, default1_HBN, nrow = 2)
plot_grid(default2_PNC, default2_HCPD, default2_NKI, default2_HBN, nrow = 2)
plot_grid(default3_PNC, default3_HCPD, default3_NKI, default3_HBN, nrow = 2)

 
```
## 2.5 Between specific connections
```{r load edge sex}

sex.main.PNC.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "PNC", "edge"))
sex.main.HCPD.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HCPD", "edge"))
sex.main.NKI.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "NKI", "edge"))
sex.main.HBN.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_sex_maineffects.csv", output_root, "HBN", "edge"))

SA.diff <- read.csv("/cbica/projects/network_replication/atlases/edge/SA.diff_schaefer200x17.csv")

double.PNC <- make_double_df(sex.main.PNC.edge, "edge", "sex", "PNC")
double.HCPD <- make_double_df(sex.main.HCPD.edge, "edge", "sex", "HCPD")
double.NKI <- make_double_df(sex.main.NKI.edge, "edge", "sex", "NKI")
double.HBN <- make_double_df(sex.main.HBN.edge, "edge", "sex", "HBN")


#range(sex.main.PNC.edge$GAM.cov.tvalue)
#range(sex.main.HCPD.edge$GAM.cov.tvalue)
#range(sex.main.NKI.edge$GAM.cov.tvalue)
#range(sex.main.HBN.edge$GAM.cov.tvalue)

```

```{r plot edge sex, fig.height = 15, fig.width = 14}

# plot surfaces
PNC_surf_plot <- make_surface_plot(double.PNC, dataset = "PNC", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3)
PNC_surf_plot <- annotate_figure(PNC_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.57))
                   
HCPD_surf_plot <-  make_surface_plot(double.HCPD, dataset = "HCPD", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3)
HCPD_surf_plot <- annotate_figure(HCPD_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.57))

NKI_surf_plot <-  make_surface_plot(double.NKI, dataset = "NKI", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3)
NKI_surf_plot <- annotate_figure(NKI_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.57))

HBN_surf_plot <-  make_surface_plot(double.HBN, dataset = "HBN", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3)
HBN_surf_plot <- annotate_figure(HBN_surf_plot, 
                                 left = text_grob("S-A Axis Rank", size = 20, x = 0.5, rot = 90),
                                 bottom = text_grob("S-A Axis Rank", size = 20, x = 0.57))
# make legend
ylim1 = -3
ylim2 = 3
g2 <- gam(GAM.cov.tvalue ~ te(parcel2.SA.vec,parcel1.SA.vec,k=3), data = double.PNC)
  
surface.plot.fig <- gg_tensor(g2) + theme_classic() +
    theme(
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.line = element_line(color = "black"),
      axis.text=element_text(size=24, color = "black")) + 
     scale_fill_gradientn(colours = c("#FF8D6E", "white", "#02B0DB"), 
                          values = scales::rescale(c(ylim1, 0, ylim2)), limits = c(ylim1, ylim2), oob = squish, na.value = "white") +     geom_vline(xintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    geom_hline(yintercept = mean(range(double.PNC$parcel1.SA.vec)),
               linetype='dashed',size=1) + 
    theme(legend.position='bottom',
          legend.key.height = unit(1, 'cm'),
          legend.key.width = unit(3, 'cm'),
          legend.title = element_blank(),
          legend.text = element_text(size=24),
          strip.background = element_blank(),
          plot.margin = margin(1, 1, 1, 1, "cm"),
          plot.title = element_text(size=24, hjust=0.5))  
  
legend <- get_legend(surface.plot.fig)
  

# combine plots
row1 <- plot_grid(PNC_surf_plot, blank_space, HCPD_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))
row2 <- plot_grid(NKI_surf_plot, blank_space, HBN_surf_plot, ncol = 3, rel_widths = c(1, 0.1, 1))

combined_surf_plots <- plot_grid(row1, blank_space, row2, ncol = 1, nrow = 3, rel_heights = c(1, 0.1, 1))

combined_surf_plots <- plot_grid(blank_space, combined_surf_plots, blank_space, legend, nrow = 4, rel_heights = c(0.05, 1, 0.03, 0.2))

annotate_figure(combined_surf_plots, 
                top = text_grob("Connectivity Between Specific Regional Pairs", size = 20, face = "bold", x = 0.5),
                bottom = text_grob("Sex Effect (t-value)", size = 20, x = 0.5))
```
 
  
How much of the variance in edgewise sex effects is captured by that smooth hierarchical organization -- or how strongly the S–A axis explains the spatial distribution of sex differences in edge-level connectivity
```{r edge spin test}
PNC_edge_spin <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/spin_test/edge/")

```

 
# 3. Sex effect along S-A axis  
## 3.1 Functional connectivity strength (or global brain connectivity/GBC)
```{r GBC sex effect vs SA axis}
sex.main.PNC.GBC.axis <- merge(sex.main.PNC.GBC, schaefer200_SAaxis, by = "region")
sex.main.HBN.GBC.axis <- merge(sex.main.HBN.GBC, schaefer200_SAaxis, by = "region")

cat(glue("
-  PNC: GBC Sex Effect vs. S-A Axis Rank
  r = {round(get_corr(sex.main.PNC.GBC.axis$GAM.cov.tvalue, sex.main.PNC.GBC.axis$SA.axis_rank), 3)}

-  HBN: GBC Sex Effect vs. S-A Axis Rank
  r = {round(get_corr(sex.main.HBN.GBC.axis$GAM.cov.tvalue, sex.main.HBN.GBC.axis$SA.axis_rank), 3)}

")) 
```
## 3.2 Between-network connectivity

```{r BNC sex effect vs SA axis}
sex.main.PNC.BNC.axis <- merge(sex.main.PNC.BNC, schaefer200_SAaxis, by = "region")
sex.main.HBN.BNC.axis <- merge(sex.main.HBN.BNC, schaefer200_SAaxis, by = "region")

cat(glue_collapse(glue("
- PNC: BNC Sex Effect vs. S-A Axis Rank
  r = {round(get_corr(sex.main.PNC.BNC.axis$GAM.cov.tvalue, sex.main.PNC.BNC.axis$SA.axis_rank), 3)}
  p_spin = {perm.sphere.p(sex.main.PNC.BNC.axis$GAM.cov.tvalue, sex.main.PNC.BNC.axis$SA.axis_rank, perm.id = perm.id.full_schaefer200, corr.type='spearman')}  

- HBN: BNC Sex Effect vs. S-A Axis Rank
  r = {round(get_corr(sex.main.HBN.BNC.axis$GAM.cov.tvalue, sex.main.HBN.BNC.axis$SA.axis_rank), 3)}
  p_spin = {perm.sphere.p(sex.main.HBN.BNC.axis$GAM.cov.tvalue, sex.main.HBN.BNC.axis$SA.axis_rank, perm.id = perm.id.full_schaefer200, corr.type='spearman')}  
"), sep = "\n"))

```
- grayed parcels = nonsignificant sexal effect
```{r BNC sex effect vs SA axis plot, fig.height = 5, fig.width = 10}

BNC_PNC_corr <- get_corr(sex.main.PNC.BNC.axis$GAM.cov.tvalue, sex.main.PNC.BNC.axis$SA.axis_rank)
annot_text_BNC_PNC <- bquote(paste(italic("r"), " = ", .(round(BNC_PNC_corr, 2)), ", ", italic("p"[spin]), " = N.S."))


BNC_HBN_corr <- get_corr(sex.main.HBN.BNC.axis$GAM.cov.tvalue, sex.main.HBN.BNC.axis$SA.axis_rank)
BNC_HBN_pspin <- perm.sphere.p(sex.main.HBN.BNC.axis$GAM.cov.tvalue, sex.main.HBN.BNC.axis$SA.axis_rank, perm.id = perm.id.full_schaefer200, corr.type='spearman')
annot_text_BNC_HBN <- bquote(paste(italic("r"), " = ", .(round(BNC_HBN_corr, 2)), ", ", italic(p[spin]) == .(format(round(BNC_HBN_pspin, 4), scientific = FALSE))))

 
sex.main.PNC.BNC.axis <- sex.main.PNC.BNC.axis %>% mutate(SA.axis_rank_sig = ifelse(!is.na(cov_sig_effect), SA.axis_rank, NA))
sex.main.PNC.BNC.axis$SA.axis_rank_sig <- as.numeric(sex.main.PNC.BNC.axis$SA.axis_rank_sig)
sex.main.HBN.BNC.axis <- sex.main.HBN.BNC.axis %>% mutate(SA.axis_rank_sig = ifelse(!is.na(cov_sig_effect), SA.axis_rank, NA))
sex.main.HBN.BNC.axis$SA.axis_rank_sig <- as.numeric(sex.main.HBN.BNC.axis$SA.axis_rank_sig)

BNC_PNC_corr_plot <- plot_corr_SA(sex.main.PNC.BNC.axis, measure = "GAM.cov.tvalue", annot_text_BNC_PNC, title = "PNC", ylim1 = -6, ylim2 = 11, y_label = 9) 
BNC_HBN_corr_plot <- plot_corr_SA(sex.main.HBN.BNC.axis, measure = "GAM.cov.tvalue", annot_text_BNC_HBN, title = "HBN", ylim1 = -4, ylim2 = 3, y_label = 3)

BNC_combined <- plot_grid(BNC_PNC_corr_plot, blank_space, BNC_HBN_corr_plot, ncol = 3, rel_widths = c(1, 0.05, 1))
BNC_combined <- plot_grid(blank_space, BNC_combined, nrow = 2, rel_heights = c(0.05, 1))
annotate_figure(BNC_combined, top = text_grob("Between-Network Connectivity", size = 24),
                bottom = text_grob("S-A Axis Rank", size = 24),
                left = text_grob("Sex Effect (t-value)", size = 24, rot = 90))
```


## 3.3 Within-network connectivity
```{r WNC sex effect vs SA axis}
sex.main.PNC.WNC.axis <- merge(sex.main.PNC.WNC, schaefer200_SAaxis, by = "region")
sex.main.HBN.WNC.axis <- merge(sex.main.HBN.WNC, schaefer200_SAaxis, by = "region")

cat(glue_collapse(glue("
- PNC: WNC Sex Effect vs. S-A Axis Rank
  r = {round(get_corr(sex.main.PNC.WNC.axis$GAM.cov.tvalue, sex.main.PNC.WNC.axis$SA.axis_rank), 3)}
  p_spin = {perm.sphere.p(sex.main.PNC.WNC.axis$GAM.cov.tvalue, sex.main.PNC.WNC.axis$SA.axis_rank, perm.id = perm.id.full_schaefer200, corr.type='spearman')}  

- HBN: WNC Sex Effect vs. S-A Axis Rank
  r = {round(get_corr(sex.main.HBN.WNC.axis$GAM.cov.tvalue, sex.main.HBN.WNC.axis$SA.axis_rank), 3)}
  p_spin = {perm.sphere.p(sex.main.HBN.WNC.axis$GAM.cov.tvalue, sex.main.HBN.WNC.axis$SA.axis_rank, perm.id = perm.id.full_schaefer200, corr.type='spearman')}  
"), sep = "\n"))
```
- grayed parcels = nonsignificant sex effect
```{r WNC sex effect vs SA axis plot, fig.height = 5, fig.width = 10}

WNC_PNC_corr <- get_corr(sex.main.PNC.WNC.axis$GAM.cov.tvalue, sex.main.PNC.WNC.axis$SA.axis_rank)
WNC_PNC_pspin <- perm.sphere.p(sex.main.PNC.WNC.axis$GAM.cov.tvalue, sex.main.PNC.WNC.axis$SA.axis_rank, perm.id = perm.id.full_schaefer200, corr.type='spearman')

annot_text_WNC_PNC <- bquote(paste(italic("r"), " = ", .(round(WNC_PNC_corr, 2)), ", ", italic(p[spin]) == .(format(round(WNC_PNC_pspin, 4), scientific = FALSE))))


WNC_HBN_corr <- get_corr(sex.main.HBN.WNC.axis$GAM.cov.tvalue, sex.main.HBN.WNC.axis$SA.axis_rank)
WNC_HBN_pspin <- perm.sphere.p(sex.main.HBN.WNC.axis$GAM.cov.tvalue, sex.main.HBN.WNC.axis$SA.axis_rank, perm.id = perm.id.full_schaefer200, corr.type='spearman')
annot_text_WNC_HBN <- bquote(paste(italic("r"), " = ", .(round(WNC_HBN_corr, 2)), ", ", italic(p[spin]) == .(format(round(WNC_HBN_pspin, 4), scientific = FALSE))))

sex.main.PNC.WNC.axis <- sex.main.PNC.WNC.axis %>% mutate(SA.axis_rank_sig = ifelse(!is.na(cov_sig_effect), SA.axis_rank, NA))
sex.main.PNC.WNC.axis$SA.axis_rank_sig <- as.numeric(sex.main.PNC.WNC.axis$SA.axis_rank_sig)
sex.main.HBN.WNC.axis <- sex.main.HBN.WNC.axis %>% mutate(SA.axis_rank_sig = ifelse(!is.na(cov_sig_effect), SA.axis_rank, NA))
sex.main.HBN.WNC.axis$SA.axis_rank_sig <- as.numeric(sex.main.HBN.WNC.axis$SA.axis_rank_sig)

WNC_PNC_corr_plot <- plot_corr_SA(sex.main.PNC.WNC.axis, measure = "GAM.cov.tvalue", annot_text_WNC_PNC, title = "PNC", ylim1 = -9, ylim2 = 12, y_label = 11) 
WNC_HBN_corr_plot <- plot_corr_SA(sex.main.HBN.WNC.axis, measure = "GAM.cov.tvalue", annot_text_WNC_HBN, title = "HBN", ylim1 = -4, ylim2 = 6, y_label = 5)

WNC_combined <- plot_grid(WNC_PNC_corr_plot, blank_space, WNC_HBN_corr_plot, ncol = 3, rel_widths = c(1, 0.05, 1))
WNC_combined <- plot_grid(blank_space, WNC_combined, nrow = 2, rel_heights = c(0.05, 1))
annotate_figure(WNC_combined, top = text_grob("Within-Network Connectivity", size = 24),
                bottom = text_grob("S-A Axis Rank", size = 24),
                left = text_grob("Sex Effect (t-value)", size = 24, rot = 90))
```

# 4. Developmental trajectories for each sex
- plot by networks  

## 4.1 Functional connectivity strength 
```{r load gbc age by sex interaction}
agebysexint.PNC.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "PNC", "GBC"))
agebysexint.PNC.GBC$region <- paste0("7", agebysexint.PNC.GBC$region)
agebysexint.PNC.GBC <- sig.effects.interaction(agebysexint.PNC.GBC, "age", "sex", "PNC")
print(paste("PNC regions with sig interaction:", agebysexint.PNC.GBC %>% filter(significant.fdr == 1) %>% pull(region), ""))

agebysexint.HCPD.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "HCPD", "GBC"))
agebysexint.HCPD.GBC$region <- paste0("7", agebysexint.HCPD.GBC$region)
agebysexint.HCPD.GBC <- sig.effects.interaction(agebysexint.HCPD.GBC, "age", "sex", "HCPD")

agebysexint.NKI.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "NKI", "GBC"))
agebysexint.NKI.GBC$region <- paste0("7", agebysexint.NKI.GBC$region)
agebysexint.NKI.GBC <- sig.effects.interaction(agebysexint.NKI.GBC, "age", "sex", "NKI")

agebysexint.HBN.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "HBN", "GBC"))
agebysexint.HBN.GBC$region <- paste0("7", agebysexint.HBN.GBC$region)
agebysexint.HBN.GBC <- sig.effects.interaction(agebysexint.HBN.GBC, "age", "sex", "HBN")
```

```{r load gbc dev trajectories}
agebysex.PNC.GBC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_fitted.csv", output_root, "PNC", "GBC"))
agebysex.PNC.GBC$region <- paste0("7", agebysex.PNC.GBC$region)
agebysex.PNC.GBC <- agebysex.PNC.GBC %>% rename(age=smooth_var)
```

```{r gbc dev trajectories vis, fig.height = 15, fig.width = 20}
GBC_vis_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Vis")) %>% pull(region)
agebysex.PNC.GBC.vis <- agebysex.PNC.GBC %>% filter(region %in% GBC_vis_regions)

GBC.vis.PNC.plots <- lapply(GBC_vis_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#24A6A8FF")
names(GBC.vis.PNC.plots) <- GBC_vis_regions 

 
# get legend
color = "#24A6A8FF"
y.limits = range(agebysex.PNC.GBC$fitted)
df_plot <- agebysex.PNC.GBC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = color, linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)


GBC.vis.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.vis.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
GBC.vis.PNC.plots.text <- annotate_figure(GBC.vis.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - Visual Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.vis.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r gbc dev trajectories LH SomMot, fig.height = 15, fig.width = 15}
GBC_LH_SomMot_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "LH_SomMot")) %>% pull(region)

GBC.LH_SomMot.PNC.plots <- lapply(GBC_LH_SomMot_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#24A6A8FF")
names(GBC.LH_SomMot.PNC.plots) <- GBC_LH_SomMot_regions 


GBC.LH_SomMot.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.LH_SomMot.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
GBC.LH_SomMot.PNC.plots.text <- annotate_figure(GBC.LH_SomMot.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - LH Somatomotor Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.LH_SomMot.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```


```{r gbc dev trajectories RH SomMot, fig.height = 15, fig.width = 15}
GBC_RH_SomMot_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "RH_SomMot")) %>% pull(region)

GBC.RH_SomMot.PNC.plots <- lapply(GBC_RH_SomMot_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#24A6A8FF")
names(GBC.RH_SomMot.PNC.plots) <- GBC_RH_SomMot_regions 


# get legend
df_plot <- agebysex.PNC.GBC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#24A6A8FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)

GBC.RH_SomMot.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.RH_SomMot.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
GBC.RH_SomMot.PNC.plots.text <- annotate_figure(GBC.RH_SomMot.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - RH Somatomotor Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.RH_SomMot.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r gbc dev trajectories SalVentAttn, fig.height = 15, fig.width = 15}
GBC_SalVentAttn_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "SalVentAttn")) %>% pull(region)

GBC.SalVentAttn.PNC.plots <- lapply(GBC_SalVentAttn_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#EEAC32FF")
names(GBC.SalVentAttn.PNC.plots) <- GBC_SalVentAttn_regions 


# get legend
df_plot <- agebysex.PNC.GBC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#EEAC32FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)



GBC.SalVentAttn.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.SalVentAttn.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
GBC.SalVentAttn.PNC.plots.text <- annotate_figure(GBC.SalVentAttn.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - Salience/Ventral Attention Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.SalVentAttn.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r gbc dev trajectories DorsAttn, fig.height = 15, fig.width = 15}
GBC_DorsAttn_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "DorsAttn")) %>% pull(region)

GBC.DorsAttn.PNC.plots <- lapply(GBC_DorsAttn_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#EEAC32FF")
names(GBC.DorsAttn.PNC.plots) <- GBC_DorsAttn_regions 

GBC.DorsAttn.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.DorsAttn.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
GBC.DorsAttn.PNC.plots.text <- annotate_figure(GBC.DorsAttn.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - Dorsal Attention Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.DorsAttn.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```


```{r gbc dev trajectories Limbic, fig.height = 6, fig.width = 10}
GBC_Limbic_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Limbic")) %>% pull(region)

GBC.Limbic.PNC.plots <- lapply(GBC_Limbic_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#C73000FF")
names(GBC.Limbic.PNC.plots) <- GBC_Limbic_regions 


# get legend
df_plot <- agebysex.PNC.GBC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#C73000FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)



GBC.Limbic.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.Limbic.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
GBC.Limbic.PNC.plots.text <- annotate_figure(GBC.Limbic.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - Limbic Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.Limbic.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r gbc dev trajectories FPN, fig.height = 15, fig.width = 15}
GBC_Cont_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Cont")) %>% pull(region)

GBC.Cont.PNC.plots <- lapply(GBC_Cont_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#C73000FF")
names(GBC.Cont.PNC.plots) <- GBC_Cont_regions 

GBC.Cont.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.Cont.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
GBC.Cont.PNC.plots.text <- annotate_figure(GBC.Cont.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - Frontoparietal Control Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.Cont.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r gbc dev trajectories lh Default, fig.height = 15, fig.width = 15}
GBC_Default_regions <- sex.main.PNC.GBC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Default")) %>% pull(region)

GBC.Default.PNC.plots <- lapply(GBC_Default_regions, plot_trajectories_bycov, df = agebysex.PNC.GBC, covariate = "sex", y.limits = range(agebysex.PNC.GBC$fitted), color = "#C73000FF")
names(GBC.Default.PNC.plots) <- GBC_Default_regions 

GBC.Default.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.Default.PNC.plots[1:20]), nrow = 2, rel_heights = c(0.03, 1))
GBC.Default.PNC.plots.text <- annotate_figure(GBC.Default.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - Default Mode Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.Default.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r gbc dev trajectories rh Default, fig.height = 15, fig.width = 15}

GBC.Default.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = GBC.Default.PNC.plots[21:40]), nrow = 2, rel_heights = c(0.03, 1))
GBC.Default.PNC.plots.text <- annotate_figure(GBC.Default.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Functional Connectivity Strength", size = 24, rot = 90),
                top = text_grob("PNC - Default Mode Regions - Functional Connectivity Strength", size = 24))


plot_grid(GBC.Default.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

## 4.2 Between-network connectivity 

```{r load BNC age by sex interaction}
agebysexint.PNC.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "PNC", "BNC"))
agebysexint.PNC.BNC$region <- paste0("7", agebysexint.PNC.BNC$region)
agebysexint.PNC.BNC <- sig.effects.interaction(agebysexint.PNC.BNC, "age", "sex", "PNC")
print(paste("PNC regions with sig interaction:", agebysexint.PNC.BNC %>% filter(significant.fdr == 1) %>% pull(region)))


agebysexint.HCPD.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "HCPD", "BNC"))
agebysexint.HCPD.BNC$region <- paste0("7", agebysexint.HCPD.BNC$region)
agebysexint.HCPD.BNC <- sig.effects.interaction(agebysexint.HCPD.BNC, "age", "sex", "HCPD")

agebysexint.NKI.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "NKI", "BNC"))
agebysexint.NKI.BNC$region <- paste0("7", agebysexint.NKI.BNC$region)
agebysexint.NKI.BNC <- sig.effects.interaction(agebysexint.NKI.BNC, "age", "sex", "NKI")

agebysexint.HBN.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "HBN", "BNC"))
agebysexint.HBN.BNC$region <- paste0("7", agebysexint.HBN.BNC$region)
agebysexint.HBN.BNC <- sig.effects.interaction(agebysexint.HBN.BNC, "age", "sex", "HBN")
```

```{r load BNC dev trajectories}
agebysex.PNC.BNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_fitted.csv", output_root, "PNC", "BNC"))
agebysex.PNC.BNC$region <- paste0("7", agebysex.PNC.BNC$region)
agebysex.PNC.BNC <- agebysex.PNC.BNC %>% rename(age=smooth_var)
```

```{r BNC dev trajectories vis, fig.height = 15, fig.width = 20}
BNC_vis_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Vis")) %>% pull(region)
agebysex.PNC.BNC.vis <- agebysex.PNC.BNC %>% filter(region %in% BNC_vis_regions)

BNC.vis.PNC.plots <- lapply(BNC_vis_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#24A6A8FF")
names(BNC.vis.PNC.plots) <- BNC_vis_regions 

 
# get legend
color = "#24A6A8FF"
y.limits = range(agebysex.PNC.BNC$fitted)
df_plot <- agebysex.PNC.BNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = color, linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)


BNC.vis.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.vis.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
BNC.vis.PNC.plots.text <- annotate_figure(BNC.vis.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Visual Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.vis.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r BNC dev trajectories LH SomMot, fig.height = 15, fig.width = 15}
BNC_LH_SomMot_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "LH_SomMot")) %>% pull(region)

BNC.LH_SomMot.PNC.plots <- lapply(BNC_LH_SomMot_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#24A6A8FF")
names(BNC.LH_SomMot.PNC.plots) <- BNC_LH_SomMot_regions 


BNC.LH_SomMot.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.LH_SomMot.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
BNC.LH_SomMot.PNC.plots.text <- annotate_figure(BNC.LH_SomMot.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - LH Somatomotor Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.LH_SomMot.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```


```{r BNC dev trajectories RH SomMot, fig.height = 15, fig.width = 15}
BNC_RH_SomMot_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "RH_SomMot")) %>% pull(region)

BNC.RH_SomMot.PNC.plots <- lapply(BNC_RH_SomMot_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#24A6A8FF")
names(BNC.RH_SomMot.PNC.plots) <- BNC_RH_SomMot_regions 


# get legend
df_plot <- agebysex.PNC.BNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#24A6A8FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)

BNC.RH_SomMot.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.RH_SomMot.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
BNC.RH_SomMot.PNC.plots.text <- annotate_figure(BNC.RH_SomMot.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - RH Somatomotor Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.RH_SomMot.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r BNC dev trajectories SalVentAttn, fig.height = 15, fig.width = 15}
BNC_SalVentAttn_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "SalVentAttn")) %>% pull(region)

BNC.SalVentAttn.PNC.plots <- lapply(BNC_SalVentAttn_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#EEAC32FF")
names(BNC.SalVentAttn.PNC.plots) <- BNC_SalVentAttn_regions 


# get legend
df_plot <- agebysex.PNC.BNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#EEAC32FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)



BNC.SalVentAttn.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.SalVentAttn.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
BNC.SalVentAttn.PNC.plots.text <- annotate_figure(BNC.SalVentAttn.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Salience/Ventral Attention Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.SalVentAttn.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r BNC dev trajectories DorsAttn, fig.height = 15, fig.width = 15}
BNC_DorsAttn_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "DorsAttn")) %>% pull(region)

BNC.DorsAttn.PNC.plots <- lapply(BNC_DorsAttn_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#EEAC32FF")
names(BNC.DorsAttn.PNC.plots) <- BNC_DorsAttn_regions 

BNC.DorsAttn.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.DorsAttn.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
BNC.DorsAttn.PNC.plots.text <- annotate_figure(BNC.DorsAttn.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Dorsal Attention Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.DorsAttn.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```


```{r BNC dev trajectories Limbic, fig.height = 6, fig.width = 10}
BNC_Limbic_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Limbic")) %>% pull(region)

BNC.Limbic.PNC.plots <- lapply(BNC_Limbic_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#C73000FF")
names(BNC.Limbic.PNC.plots) <- BNC_Limbic_regions 


# get legend
df_plot <- agebysex.PNC.BNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#C73000FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)



BNC.Limbic.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.Limbic.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
BNC.Limbic.PNC.plots.text <- annotate_figure(BNC.Limbic.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Limbic Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.Limbic.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r BNC dev trajectories FPN, fig.height = 15, fig.width = 15}
BNC_Cont_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Cont")) %>% pull(region)

BNC.Cont.PNC.plots <- lapply(BNC_Cont_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#C73000FF")
names(BNC.Cont.PNC.plots) <- BNC_Cont_regions 

BNC.Cont.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.Cont.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
BNC.Cont.PNC.plots.text <- annotate_figure(BNC.Cont.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Frontoparietal Control Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.Cont.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r BNC dev trajectories lh Default, fig.height = 15, fig.width = 15}
BNC_Default_regions <- sex.main.PNC.BNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Default")) %>% pull(region)

BNC.Default.PNC.plots <- lapply(BNC_Default_regions, plot_trajectories_bycov, df = agebysex.PNC.BNC, covariate = "sex", y.limits = range(agebysex.PNC.BNC$fitted), color = "#C73000FF")
names(BNC.Default.PNC.plots) <- BNC_Default_regions 

BNC.Default.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.Default.PNC.plots[1:20]), nrow = 2, rel_heights = c(0.03, 1))
BNC.Default.PNC.plots.text <- annotate_figure(BNC.Default.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Default Mode Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.Default.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r BNC dev trajectories rh Default, fig.height = 15, fig.width = 15}

BNC.Default.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = BNC.Default.PNC.plots[21:40]), nrow = 2, rel_heights = c(0.03, 1))
BNC.Default.PNC.plots.text <- annotate_figure(BNC.Default.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Between Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Default Mode Regions - Between Network Connectivity", size = 24))


plot_grid(BNC.Default.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```


## 4.3 Within-network connectivity
```{r load WNC age by sex interaction}
agebysexint.PNC.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "PNC", "WNC"))
agebysexint.PNC.WNC$region <- paste0("7", agebysexint.PNC.WNC$region)
agebysexint.PNC.WNC <- sig.effects.interaction(agebysexint.PNC.WNC, "age", "sex", "PNC")

agebysexint.HCPD.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "HCPD", "WNC"))
agebysexint.HCPD.WNC$region <- paste0("7", agebysexint.HCPD.WNC$region)
agebysexint.HCPD.WNC <- sig.effects.interaction(agebysexint.HCPD.WNC, "age", "sex", "HCPD")
print(paste("HCPD regions with sig interaction:", agebysexint.HCPD.WNC %>% filter(significant.fdr == 1) %>% pull(region), ""))

agebysexint.NKI.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "NKI", "WNC"))
agebysexint.NKI.WNC$region <- paste0("7", agebysexint.NKI.WNC$region)
agebysexint.NKI.WNC <- sig.effects.interaction(agebysexint.NKI.WNC, "age", "sex", "NKI")

agebysexint.HBN.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction.csv", output_root, "HBN", "WNC"))
agebysexint.HBN.WNC$region <- paste0("7", agebysexint.HBN.WNC$region)
agebysexint.HBN.WNC <- sig.effects.interaction(agebysexint.HBN.WNC, "age", "sex", "HBN")
```

```{r load WNC dev trajectories}
agebysex.PNC.WNC <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_fitted.csv", output_root, "PNC", "WNC"))
agebysex.PNC.WNC$region <- paste0("7", agebysex.PNC.WNC$region)
agebysex.PNC.WNC <- agebysex.PNC.WNC %>% rename(age=smooth_var)
```

```{r WNC dev trajectories vis, fig.height = 15, fig.width = 20}
WNC_vis_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Vis")) %>% pull(region)
agebysex.PNC.WNC.vis <- agebysex.PNC.WNC %>% filter(region %in% WNC_vis_regions)

WNC.vis.PNC.plots <- lapply(WNC_vis_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#24A6A8FF")
names(WNC.vis.PNC.plots) <- WNC_vis_regions 

 
# get legend
color = "#24A6A8FF"
y.limits = range(agebysex.PNC.WNC$fitted)
df_plot <- agebysex.PNC.WNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = color, linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)


WNC.vis.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.vis.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.vis.PNC.plots.text <- annotate_figure(WNC.vis.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Visual Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.vis.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r WNC dev trajectories LH SomMot, fig.height = 15, fig.width = 15}
WNC_LH_SomMot_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "LH_SomMot")) %>% pull(region)

WNC.LH_SomMot.PNC.plots <- lapply(WNC_LH_SomMot_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#24A6A8FF")
names(WNC.LH_SomMot.PNC.plots) <- WNC_LH_SomMot_regions 


WNC.LH_SomMot.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.LH_SomMot.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.LH_SomMot.PNC.plots.text <- annotate_figure(WNC.LH_SomMot.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - LH Somatomotor Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.LH_SomMot.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```


```{r WNC dev trajectories RH SomMot, fig.height = 15, fig.width = 15}
WNC_RH_SomMot_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "RH_SomMot")) %>% pull(region)

WNC.RH_SomMot.PNC.plots <- lapply(WNC_RH_SomMot_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#24A6A8FF")
names(WNC.RH_SomMot.PNC.plots) <- WNC_RH_SomMot_regions 


# get legend
df_plot <- agebysex.PNC.WNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#24A6A8FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)

WNC.RH_SomMot.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.RH_SomMot.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.RH_SomMot.PNC.plots.text <- annotate_figure(WNC.RH_SomMot.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - RH Somatomotor Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.RH_SomMot.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r WNC dev trajectories SalVentAttn, fig.height = 15, fig.width = 15}
WNC_SalVentAttn_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "SalVentAttn")) %>% pull(region)

WNC.SalVentAttn.PNC.plots <- lapply(WNC_SalVentAttn_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#EEAC32FF")
names(WNC.SalVentAttn.PNC.plots) <- WNC_SalVentAttn_regions 


# get legend
df_plot <- agebysex.PNC.WNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#EEAC32FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)



WNC.SalVentAttn.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.SalVentAttn.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.SalVentAttn.PNC.plots.text <- annotate_figure(WNC.SalVentAttn.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Salience/Ventral Attention Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.SalVentAttn.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r WNC dev trajectories DorsAttn, fig.height = 15, fig.width = 15}
WNC_DorsAttn_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "DorsAttn")) %>% pull(region)

WNC.DorsAttn.PNC.plots <- lapply(WNC_DorsAttn_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#EEAC32FF")
names(WNC.DorsAttn.PNC.plots) <- WNC_DorsAttn_regions 

WNC.DorsAttn.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.DorsAttn.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.DorsAttn.PNC.plots.text <- annotate_figure(WNC.DorsAttn.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Dorsal Attention Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.DorsAttn.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```


```{r WNC dev trajectories Limbic, fig.height = 10, fig.width = 10}
WNC_Limbic_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Limbic")) %>% pull(region)

WNC.Limbic.PNC.plots <- lapply(WNC_Limbic_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#C73000FF")
names(WNC.Limbic.PNC.plots) <- WNC_Limbic_regions 


# get legend
df_plot <- agebysex.PNC.WNC %>% filter(region %in% "7Networks_LH_Vis_2")

plot <- ggplot(df_plot, aes(x = age, y = fitted, group = interaction(sex, region))) + 
  geom_line(color = "#C73000FF", linewidth = 1, aes(linetype = sex)) +
  theme_classic() +
  scale_y_continuous(limits = y.limits) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.position = "bottom",
        legend.title = element_text(size=20),
        legend.text = element_text(size=20),
        axis.title = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black")) + ggtitle(gsub("7Networks ", "", gsub("_", " ", "7Networks_LH_Vis_2")))

dev_traj_legend <- get_legend(plot)



WNC.Limbic.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.Limbic.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.Limbic.PNC.plots.text <- annotate_figure(WNC.Limbic.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Limbic Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.Limbic.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r WNC dev trajectories FPN, fig.height = 15, fig.width = 15}
WNC_Cont_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Cont")) %>% pull(region)

WNC.Cont.PNC.plots <- lapply(WNC_Cont_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#C73000FF")
names(WNC.Cont.PNC.plots) <- WNC_Cont_regions 

WNC.Cont.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.Cont.PNC.plots), nrow = 2, rel_heights = c(0.03, 1))
WNC.Cont.PNC.plots.text <- annotate_figure(WNC.Cont.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Frontoparietal Control Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.Cont.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r WNC dev trajectories lh Default, fig.height = 15, fig.width = 15}
WNC_Default_regions <- sex.main.PNC.WNC %>% filter(significant.fdr == 1) %>% filter(str_detect(region, "Default")) %>% pull(region)

WNC.Default.PNC.plots <- lapply(WNC_Default_regions, plot_trajectories_bycov, df = agebysex.PNC.WNC, covariate = "sex", y.limits = range(agebysex.PNC.WNC$fitted), color = "#C73000FF")
names(WNC.Default.PNC.plots) <- WNC_Default_regions 

WNC.Default.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.Default.PNC.plots[1:20]), nrow = 2, rel_heights = c(0.03, 1))
WNC.Default.PNC.plots.text <- annotate_figure(WNC.Default.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Default Mode Regions - Within Network Connectivity", size = 24))


plot_grid(WNC.Default.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))

```

```{r WNC dev trajectories rh Default, fig.height = 15, fig.width = 15}

WNC.Default.PNC.plots.combined <- plot_grid(blank_space, plot_grid(plotlist = WNC.Default.PNC.plots[21:40]), nrow = 2, rel_heights = c(0.03, 1))
WNC.Default.PNC.plots.text <- annotate_figure(WNC.Default.PNC.plots.combined, bottom = text_grob("Age (years)", size = 24),
                left = text_grob("Within Network Connectivity", size = 24, rot = 90),
                top = text_grob("PNC - Default Mode Regions - Within Network Connectivity", size = 24))

plot_grid(WNC.Default.PNC.plots.text, dev_traj_legend, nrow = 2, rel_heights = c(1, 0.05))
```

## 4.4 Between specific pairs of networks
```{r load networkpair age by sex interaction}
agebysexint.PNC.networkpair <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction_schaefer200x7.csv", output_root, "PNC", "networkpair"))
agebysexint.PNC.networkpair$region <- paste0("7", agebysexint.PNC.networkpair$region)
agebysexint.PNC.networkpair <- sig.effects.interaction(agebysexint.PNC.networkpair, "age", "sex", "PNC")
print(paste("PNC network pair with sig interaction:", agebysexint.PNC.networkpair %>% filter(significant.fdr == 1) %>% pull(region), ""))

agebysexint.HCPD.networkpair <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction_schaefer200x7.csv", output_root, "HCPD", "networkpair"))
agebysexint.HCPD.networkpair$region <- paste0("7", agebysexint.HCPD.networkpair$region)
agebysexint.HCPD.networkpair <- sig.effects.interaction(agebysexint.HCPD.networkpair, "age", "sex", "HCPD")

agebysexint.NKI.networkpair <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction_schaefer200x7.csv", output_root, "NKI", "networkpair"))
agebysexint.NKI.networkpair$region <- paste0("7", agebysexint.NKI.networkpair$region)
agebysexint.NKI.networkpair <- sig.effects.interaction(agebysexint.NKI.networkpair, "age", "sex", "NKI")

agebysexint.HBN.networkpair <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_agebysex_interaction_schaefer200x7.csv", output_root, "HBN", "networkpair"))
agebysexint.HBN.networkpair$region <- paste0("7", agebysexint.HBN.networkpair$region)
agebysexint.HBN.networkpair <- sig.effects.interaction(agebysexint.HBN.networkpair, "age", "sex", "HBN")
```

 
 
# 5. Age-by-sex interaction across ALL datasets
- WNC in 11 regions (5%; schaefer200x7) and 22 regions (11%; schafer200x17) has some age-by-sex effects when datasets are pooled.
- network-pair connectivity also has some significant age-by-sex interactions

```{r load age by sex interaction across datasets}
GBC_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
GBC_schaefer7 <- sig.effects.all_datasets(GBC_schaefer7, "GBC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
GBC_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
GBC_schaefer17 <- sig.effects.all_datasets(GBC_schaefer17, "GBC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")

BNC_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
BNC_schaefer7 <- sig.effects.all_datasets(BNC_schaefer7, "BNC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
BNC_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
BNC_schaefer17 <- sig.effects.all_datasets(BNC_schaefer17, "BNC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")

WNC_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
WNC_schaefer7 <- sig.effects.all_datasets(WNC_schaefer7, "WNC", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
WNC_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
WNC_schaefer17 <- sig.effects.all_datasets(WNC_schaefer17, "WNC", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
WNC_schaefer17 %>% arrange(desc(int_sig_effect))

netpair_schaefer7 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_agebysex_interaction_schaefer200x7.csv")
netpair_schaefer7 <- sig.effects.all_datasets(netpair_schaefer7, "netpair", "sex", "all_datasets 7 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
netpair_schaefer17 <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_agebysex_interaction_schaefer200x17.csv")
netpair_schaefer17 <- sig.effects.all_datasets(netpair_schaefer17, "netpair", "sex", "all_datasets 17 networks", "GAM.int.pvalue", "GAM.int.Fvalue")
netpair_schaefer17 %>% arrange(desc(int_sig_effect))
```

- didn't run age-by-sex fits yet but these are the regions
```{r plot WNC age by sex regions, fig.height = 10, fig.width = 10}
WNC_schaefer17$region <- paste0("17", WNC_schaefer17$region)
sex.int.all_dataset.WNC_lh <- plot_cortex_int(WNC_schaefer17, hemi = "left", measure = "int_sig_effect", ylim1 = 1, ylim2 = 9, atlas = "schaefer17_200") 
sex.int.all_dataset.WNC_rh <- plot_cortex_int(WNC_schaefer17, hemi = "right", measure = "int_sig_effect", ylim1 = 1, ylim2 = 9, atlas = "schaefer17_200")

ylim1 = 1
ylim2 = 9
p <- ggplot() + 
    geom_brain(data = WNC_schaefer17, atlas = schaefer17_200, 
               mapping=aes(fill=int_sig_effect, colour=significant_status, size=I(0.7)), 
               show.legend=TRUE) +
    scale_fill_paletteer_c("ggthemes::Blue-Green Sequential", na.value = "white") + 
    scale_colour_manual(values = c("Sig" = "black", "Nonsig" = "grey50")) + 
    theme_void() +
    theme(legend.title = element_blank(),
          legend.text = element_text(size = 24),
        legend.position = "bottom", 
        legend.box = "horizontal", 
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(2, 'cm'),
        plot.margin = unit(c(0, 1, 0, -0.5), "cm")) + guides(color = "none")
  
  
legend <- get_legend(p)
blank_space <- ggplot() + theme_void()

annotate_figure(
  plot_grid(
    annotate_figure(
      plot_grid(
        sex.int.all_dataset.WNC_lh,
        sex.int.all_dataset.WNC_rh,
        ncol = 2
      ),
      top = text_grob("WNC age-by-sex all datasets", size = 24)
    ),
    legend,
    ncol = 1,
    rel_heights = c(1, 0.2)
  ),
  bottom = text_grob("Interaction (F-value)", size = 24)
)

 print(WNC_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))
```


```{r print networkpair age by sex pairs}
 print(netpair_schaefer17 %>% arrange(desc(int_sig_effect)) %>% filter(significant_status == "Sig") %>% pull(region))

```

# 6. Whole brain and clinical measures
```{r clinical measures and whole brain}

GBC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
GBC_clinical_maineffects <- GBC_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples")) %>% arrange(p_value)
GBC_clinical_maineffects <- sig.effects.all_datasets(GBC_clinical_maineffects, "GBC whole brain clinical measures", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

WNC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
#"p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples"
WNC_clinical_maineffects <- WNC_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% arrange(p_value)
WNC_clinical_maineffects <- sig.effects.all_datasets(WNC_clinical_maineffects, "WNC whole brain clinical measures", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

BNC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
BNC_clinical_maineffects <- BNC_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% arrange(p_value)
BNC_clinical_maineffects <- sig.effects.all_datasets(BNC_clinical_maineffects, "BNC whole brain clinical measures", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj")   

networkpair_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
networkpair_clinical_maineffects <- networkpair_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% arrange(p_value)
networkpair_clinical_maineffects <- sig.effects.all_datasets(networkpair_clinical_maineffects, "networkpair whole brain clinical measures", "network pairs", "all_datasets 17 networks", "p_value", "deltaR2_adj")  # frontoparietalControlA_temporoparietal (externalizing) and somatomotorA_visualCentral (internalizing)

edge_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/edge/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
edge_clinical_maineffects <- edge_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% arrange(p_value)
edge_clinical_maineffects <- sig.effects.all_datasets(edge_clinical_maineffects, "edge whole brain  clinical measures", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj")  
# 1 DMN edge: Networks_LH_DefaultB_PFCd_2_to_Networks_LH_DefaultC_PHC_1

```


# 7. DMN and clinical measures
-   looking at PNC, NKI, and HBN
-   clinical main effects model -- no main effects of any of the clinical measures....

```{r load clinical measures}
#"p_factor_mcelroy_harmonized_all_samples"
# "internalizing_mcelroy_harmonized_all_samples"
# "externalizing_mcelroy_harmonized_all_samples"
# "attention_mcelroy_harmonized_all_samples

GBC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
GBC_clinical_maineffects <- GBC_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
GBC_clinical_maineffects <- sig.effects.all_datasets(GBC_clinical_maineffects, "GBC DMN_A", "p_factor_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

WNC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
WNC_clinical_maineffects <- WNC_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples"))  %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
WNC_clinical_maineffects <- sig.effects.all_datasets(WNC_clinical_maineffects, "WNC DMN_A", "p_factor_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

BNC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
BNC_clinical_maineffects <- BNC_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples"))  %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
BNC_clinical_maineffects <- sig.effects.all_datasets(BNC_clinical_maineffects, "BNC DMN_A", "p_factor_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

networkpair_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
networkpair_clinical_maineffects <- networkpair_clinical_maineffects %>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples"))  %>% filter(str_detect(region, "defaultA")) %>% arrange(p_value)
networkpair_clinical_maineffects <- sig.effects.all_datasets(networkpair_clinical_maineffects, "DMN_A avg connectivity to other networks", "p_factor_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

edge_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/edge/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
edge_clinical_maineffects <- edge_clinical_maineffects %>%filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples"))  %>% filter(str_detect(region, "Default")) %>% filter(!str_detect(region, "DefaultB") & !str_detect(region, "DefaultC")) %>% arrange(p_value)
edge_clinical_maineffects <- sig.effects.all_datasets(edge_clinical_maineffects, "DMN_A edges", "p_factor_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj")  
 
```

# 8. Limbic and clinical measures

-   looking at PNC, NKI, and HBN
-   clinical main effects model -- no main effects of any of the clinical measures....

```{r clinical measures and limbic}

GBC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
GBC_clinical_maineffects <- GBC_clinical_maineffects %>% filter(covariate %in% c("externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "LimbicA")) %>% arrange(p_value)
GBC_clinical_maineffects <- sig.effects.all_datasets(GBC_clinical_maineffects, "GBC Limbic temporal pole", "externalizing_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

WNC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
#"p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples"
WNC_clinical_maineffects <- WNC_clinical_maineffects %>% filter(covariate %in% c("externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "LimbicA")) %>% arrange(p_value)
WNC_clinical_maineffects <- sig.effects.all_datasets(WNC_clinical_maineffects, "WNC Limbic temporal pole", "externalizing_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

BNC_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
BNC_clinical_maineffects <- BNC_clinical_maineffects %>% filter(covariate %in% c("externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "LimbicA")) %>% arrange(p_value)
BNC_clinical_maineffects <- sig.effects.all_datasets(BNC_clinical_maineffects, "BNC Limbic temporal pole", "externalizing_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj")  # Networks_RH_LimbicA_TempPole_3

networkpair_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
networkpair_clinical_maineffects <- networkpair_clinical_maineffects %>% filter(covariate %in% c("externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "limbicTemporopolar")) %>% arrange(p_value)
networkpair_clinical_maineffects <- sig.effects.all_datasets(networkpair_clinical_maineffects, "Limbic avg connectivity to other networks", "externalizing_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

edge_clinical_maineffects <- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/edge/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
edge_clinical_maineffects <- edge_clinical_maineffects %>% filter(covariate %in% c("externalizing_mcelroy_harmonized_all_samples")) %>% filter(!str_detect(region, "limbicB")) %>% arrange(p_value)
edge_clinical_maineffects <- sig.effects.all_datasets(edge_clinical_maineffects, "limbic edge connectivity", "externalizing_mcelroy_harmonized_all_samples", "all_datasets 17 networks", "p_value", "deltaR2_adj") 
  
```

# 9. Sex-stratified for clinical measures
```{r}

GBC_clinical_maineffectsF<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_clinical_sexstratifiedF_maineffects_schaefer200x17.csv")
GBC_clinical_maineffectsF<- GBC_clinical_maineffectsF%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
GBC_clinical_maineffectsF<- sig.effects.all_datasets(GBC_clinical_maineffectsF, "GBC DMN_A", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

WNC_clinical_maineffectsF<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
#"p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples"
WNC_clinical_maineffectsF<- WNC_clinical_maineffectsF%>% filter(covariate %in% c( "internalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
WNC_clinical_maineffectsF<- sig.effects.all_datasets(WNC_clinical_maineffectsF, "WNC DMN_A", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

BNC_clinical_maineffectsF<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
BNC_clinical_maineffectsF<- BNC_clinical_maineffectsF%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
BNC_clinical_maineffectsF<- sig.effects.all_datasets(BNC_clinical_maineffectsF, "BNC DMN_A", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

networkpair_clinical_maineffectsF<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
networkpair_clinical_maineffectsF<- networkpair_clinical_maineffectsF%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "defaultA")) %>% arrange(p_value)
networkpair_clinical_maineffectsF<- sig.effects.all_datasets(networkpair_clinical_maineffectsF, "DMN_A avg connectivity to other networks", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

edge_clinical_maineffectsF<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/edge/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
edge_clinical_maineffectsF<- edge_clinical_maineffectsF%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(!str_detect(region, "DefaultB") & !str_detect(region, "DefaultC")) %>% arrange(p_value)
edge_clinical_maineffectsF<- sig.effects.all_datasets(edge_clinical_maineffectsF, "DMN_A edges", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj")   
```


```{r}

GBC_clinical_maineffectsM<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/GBC/all_datasets_GAM_clinical_sexstratifiedF_maineffects_schaefer200x17.csv")
GBC_clinical_maineffectsM<- GBC_clinical_maineffectsM%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
GBC_clinical_maineffectsM<- sig.effects.all_datasets(GBC_clinical_maineffectsM, "GBC DMN_A", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

WNC_clinical_maineffectsM<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/WNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
#"
WNC_clinical_maineffectsM<- WNC_clinical_maineffectsM%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
WNC_clinical_maineffectsM<- sig.effects.all_datasets(WNC_clinical_maineffectsM, "WNC DMN_A", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

BNC_clinical_maineffectsM<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/BNC/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
BNC_clinical_maineffectsM<- BNC_clinical_maineffectsM%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "DefaultA")) %>% arrange(p_value)
BNC_clinical_maineffectsM<- sig.effects.all_datasets(BNC_clinical_maineffectsM, "BNC DMN_A", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

networkpair_clinical_maineffectsM<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/networkpair/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
networkpair_clinical_maineffectsM<- networkpair_clinical_maineffectsM%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(str_detect(region, "defaultA")) %>% arrange(p_value)
networkpair_clinical_maineffectsM<- sig.effects.all_datasets(networkpair_clinical_maineffectsM, "DMN_A avg connectivity to other networks", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj") 

edge_clinical_maineffectsM<- read.csv("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/GAM/edge/all_datasets_GAM_clinical_maineffects_schaefer200x17.csv")
edge_clinical_maineffectsM<- edge_clinical_maineffectsM%>% filter(covariate %in% c("p_factor_mcelroy_harmonized_all_samples", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples")) %>% filter(!str_detect(region, "DefaultB") & !str_detect(region, "DefaultC")) %>% arrange(p_value)
edge_clinical_maineffectsM<- sig.effects.all_datasets(edge_clinical_maineffectsM, "DMN_A edges", "clinical", "all_datasets 17 networks", "p_value", "deltaR2_adj")   
```

# 10. NEST resuls for WNC

```{r load NEST}
PNC_NEST <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/PNC/NEST/WNC/NEST_DefaultA_WNC.RData")
HCPD_NEST <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HCPD/NEST/WNC/NEST_DefaultA_WNC.RData")
NKI_NEST <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/NKI/NEST/WNC/NEST_DefaultA_WNC.RData")
HBN_NEST <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/HBN/NEST/WNC/NEST_DefaultA_WNC.RData")


PNC_NEST$pval
HCPD_NEST$pval
NKI_NEST$pval
HBN_NEST$pval
```

# Check schaefer 17 SA ranks
```{r}

# helper function for mapping parcels to network names  
map_network <- function(x, num_networks) {
  if (num_networks == 7) {
    dplyr::case_when(
      stringr::str_detect(x, "Vis")         ~ "Visual",
      stringr::str_detect(x, "SomMot")      ~ "SomMot",
      stringr::str_detect(x, "DorsAttn")    ~ "DorsAttn",
      stringr::str_detect(x, "SalVentAttn") ~ "SalVentAttn",
      stringr::str_detect(x, "Cont")        ~ "Frontoparietal",
      stringr::str_detect(x, "Limb")        ~ "Limbic",
      stringr::str_detect(x, "Default")     ~ "Default",
      TRUE                                  ~ x    # pass through original label if no match
    )
  } else if (num_networks == 17) {
    dplyr::case_when(
      stringr::str_detect(x, "VisCent")           ~ "visualCentral",
      stringr::str_detect(x, "VisPeri")           ~ "visualPeripheral",
      stringr::str_detect(x, "SomMotA")           ~ "somatomotorA",
      stringr::str_detect(x, "SomMotB")           ~ "somatomotorBAuditory",
      stringr::str_detect(x, "DorsAttnA")         ~ "dorsalAttentionA",
      stringr::str_detect(x, "DorsAttnB")         ~ "dorsalAttentionB",
      stringr::str_detect(x, "SalVentAttnA")      ~ "salienceVentralAttentionA",
      stringr::str_detect(x, "SalVentAttnB")      ~ "salienceVentralAttentionB",
      stringr::str_detect(x, "LimbicA_TempPole")  ~ "limbicTemporopolar",
      stringr::str_detect(x, "LimbicB_OFC")       ~ "limbicOrbitofrontal",
      stringr::str_detect(x, "ContA")             ~ "frontoparietalControlA",
      stringr::str_detect(x, "ContB")             ~ "frontoparietalControlB",
      stringr::str_detect(x, "ContC")             ~ "frontoparietalControlC",
      stringr::str_detect(x, "DefaultA")          ~ "defaultA",
      stringr::str_detect(x, "DefaultB")          ~ "defaultB",
      stringr::str_detect(x, "DefaultC")          ~ "defaultC",
      stringr::str_detect(x, "TempPar")           ~ "temporoparietal",
      TRUE                                  ~ x     # pass through original label if no match
    )
  }
} 


schaefer200x17_SAaxis <- read.csv("/cbica/projects/network_replication/SAaxis/schaefer200x17_SAaxis.csv")

schaefer200x17_SAaxis <- cbind(schaefer200x17_SAaxis, map_network(schaefer200x17_SAaxis$label, 17))  
schaefer200x17_SAaxis <- schaefer200x17_SAaxis[,-1]
schaefer200x17_SAaxis <- schaefer200x17_SAaxis %>% setNames(c("SA.axis_rank", "label", "network"))

schaefer200x17_SAaxis %>% group_by(network) %>% summarise(mean_SA = mean(SA.axis_rank)) %>% arrange(desc(mean_SA))
```


# Clinical measures exploration: attention has the biggest sex difference
```{r pfactor explore, fig.height = 10, fig.width = 10}
 

PNC_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "PNC"))
HCPD_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "HCPD"))
NKI_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "NKI"))
HBN_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "HBN"))

################### 
# Define functions 
###################
# load pfactor data and merge with demographics
load_pfactor_data <- function(file_path) {
  pfactor <- fread(file_path)
  pfactor <- pfactor %>% rename(sub = participant_id)
  pfactor$sub <- paste0("sub-", pfactor$sub)
  pfactor <- pfactor %>% select(sub, p_factor_mcelroy_harmonized_all_samples, internalizing_mcelroy_harmonized_all_samples, externalizing_mcelroy_harmonized_all_samples, attention_mcelroy_harmonized_all_samples)
  pfactor <- pfactor[!duplicated(pfactor), ]
  pfactor <- pfactor[complete.cases(pfactor), ]
  return(pfactor)
}

# load demographics for all datasets and combine
PNC_demographics <- read.csv(PNC_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "PNC") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
NKI_demographics <- read.csv(NKI_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "NKI") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
HBN_demographics <- read.csv(HBN_config_data$demographics, stringsAsFactors = TRUE) %>% rename(site = ses) %>% mutate(dataset_site = paste0("HBN_", site)) %>% select(sub, age, sex, meanFD_avgSes, dataset_site)

#load clinical measures
PNC_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/PNC/sample_info/study-PNC_desc-participants.tsv")
NKI_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/NKI/sample_info/study-NKI_desc-participants.tsv")
NKI_pfactor$sub <- gsub("sub-", "", NKI_pfactor$sub)
HBN_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/HBN/sample_info/study-HBN_desc-participants.tsv")

PNC_demographics <- inner_join(PNC_pfactor, PNC_demographics,by = "sub")
NKI_demographics <- inner_join(NKI_pfactor, NKI_demographics,by = "sub")
HBN_demographics <- inner_join(HBN_pfactor, HBN_demographics,by = "sub")

demographics <- rbind(PNC_demographics, NKI_demographics, HBN_demographics)
# load demographics for all datasets and combine
PNC_demographics <- read.csv(PNC_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "PNC") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
NKI_demographics <- read.csv(NKI_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "NKI") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
HBN_demographics <- read.csv(HBN_config_data$demographics, stringsAsFactors = TRUE) %>% rename(site = ses) %>% mutate(dataset_site = paste0("HBN_", site)) %>% select(sub, age, sex, meanFD_avgSes, dataset_site)

#load clinical measures
PNC_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/PNC/sample_info/study-PNC_desc-participants.tsv")
NKI_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/NKI/sample_info/study-NKI_desc-participants.tsv")
NKI_pfactor$sub <- gsub("sub-", "", NKI_pfactor$sub)
HBN_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/HBN/sample_info/study-HBN_desc-participants.tsv")

PNC_demographics <- inner_join(PNC_pfactor, PNC_demographics,by = "sub")
NKI_demographics <- inner_join(NKI_pfactor, NKI_demographics,by = "sub")
HBN_demographics <- inner_join(HBN_pfactor, HBN_demographics,by = "sub")

demographics <- rbind(PNC_demographics, NKI_demographics, HBN_demographics)



pfactor_plot <- ggplot(demographics, aes(x = sex, y = p_factor_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "P-factor by Sex",
       x = "Sex", y = "P-factor (McElroy Harmonized)") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))



int_plot <- ggplot(demographics, aes(x = sex, y = internalizing_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Internalizing by Sex",
       x = "Sex", y = "Internalizing") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))


ext_plot <- ggplot(demographics, aes(x = sex, y = externalizing_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Externalizing by Sex",
       x = "Sex", y = "Externalizing") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))

att_plot <- ggplot(demographics, aes(x = sex, y = attention_mcelroy_harmonized_all_samples, fill = sex)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "t.test") +
  labs(title = "Attention by Sex",
       x = "Sex", y = "Attention") +
  theme_classic() +
  scale_fill_manual(values = c("pink", "lightblue"))

plot_grid(pfactor_plot, int_plot, ext_plot, att_plot, ncol=2)

```



# 5. Spatial correlation between sex effects and p-factor effects in edge-level functional connectivity
- General psychopathology, or p-factor, is greater in males than females (N = 2502)
- Edges showing stronger sex differences in functional connectivity also tend to show stronger associations with p-factor
```{r sex differences in pfactor}
PNC_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "PNC"))
HCPD_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "HCPD"))
NKI_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "NKI"))
HBN_config_data <- fromJSON(file=sprintf("/cbica/projects/network_replication/covariate_analyses/sex_diff/code/config/config_%1$s.json", "HBN"))
 
# load demographics for all datasets and combine
PNC_demographics <- read.csv(PNC_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "PNC") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
NKI_demographics <- read.csv(NKI_config_data$demographics, stringsAsFactors = TRUE) %>% mutate(dataset_site = "NKI") %>% select(sub, age, sex, meanFD_avgSes, dataset_site)
HBN_demographics <- read.csv(HBN_config_data$demographics, stringsAsFactors = TRUE) %>% rename(site = ses) %>% mutate(dataset_site = paste0("HBN_", site)) %>% select(sub, age, sex, meanFD_avgSes, dataset_site)

# load clinical measures
PNC_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/PNC/sample_info/study-PNC_desc-participants.tsv")
NKI_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/NKI/sample_info/study-NKI_desc-participants.tsv")
NKI_pfactor$sub <- gsub("sub-", "", NKI_pfactor$sub)
HBN_pfactor <- load_pfactor_data("/cbica/projects/network_replication/covariate_analyses/pfactor/input/HBN/sample_info/study-HBN_desc-participants.tsv")

PNC_demographics <- inner_join(PNC_pfactor, PNC_demographics,by = "sub")
NKI_demographics <- inner_join(NKI_pfactor, NKI_demographics,by = "sub")
HBN_demographics <- inner_join(HBN_pfactor, HBN_demographics,by = "sub")

# final sample for pfactor (aggregated across datasets)
demographics <- rbind(PNC_demographics, NKI_demographics, HBN_demographics)
 
# make plot for pfactor sex differences 
t_out <- t.test(p_factor_mcelroy_harmonized_all_samples ~ sex, data = demographics)
cohen_d <- effsize::cohen.d(p_factor_mcelroy_harmonized_all_samples ~ sex, data = demographics)$estimate
p_str <- ifelse(t_out$p.value < 0.0001, "< 0.0001",
                sprintf("%.3f", t_out$p.value))
stat_label <- bquote(
  italic(t)[.(round(t_out$parameter))] == .(round(t_out$statistic, 2)) * "," ~
  italic(p) ~ .(p_str) * "," ~
  "Cohen's" ~ italic(d) == .(round(cohen_d, 2))
)
pfactor_plot <- ggplot(demographics, aes(x = sex, y = p_factor_mcelroy_harmonized_all_samples, fill = sex, color = sex)) +
  geom_boxplot(alpha = 0.4, outlier.shape = NA, size = 0.7) +
  labs(y = "P-factor (z-score)") +
  theme_classic(base_size = 14) +
  scale_fill_manual(values = c("#F0518B", "#20C0C6")) +
  scale_color_manual(values = c("#F0518B", "#20C0C6")) +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text = element_text(size=20), axis.title.y = element_text(size = 20),plot.margin = unit(c(1, 0.5, 0.2, 1), "cm")) + annotate(geom="text", x=1.5, y=3, label=stat_label, color="black", size=6) 

```

```{r load edge level sex effects and pfactor effects}
# edge gam output
clinical.main.all_datasets.edge <- read.csv(sprintf("%1$s/%2$s/GAM/%3$s/%2$s_GAM_clinical_maineffects_schaefer200x17.csv", output_root, "all_datasets", "edge"))

# format df's for plotting (and do FDR correction)
clinical.main.all_datasets.edge_pfactor <- clinical.main.all_datasets.edge %>% filter(covariate == "p_factor_mcelroy_harmonized_all_samples") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
clinical.main.all_datasets.edge_sex <- clinical.main.all_datasets.edge %>% filter(covariate == "sex") %>% rename(GAM.cov.pvalue = p_value, GAM.cov.tvalue = t_value)
double.pfactor <- make_double_df(clinical.main.all_datasets.edge_pfactor, "edge", "pfactor", "All datasets")
double.sex <- make_double_df(clinical.main.all_datasets.edge_sex, "edge", "sex", "All datasets")

# surface plots for sex and pfactor
pfactor_surf <- make_surface_plot(double.pfactor, dataset = "P-factor", measure = "GAM.cov.tvalue", ylim1 = -2, ylim2  = 2, 
                                   p_label = "", legend = T)

pfactor_surf <- annotate_figure(pfactor_surf, bottom = text_grob("P-factor Effect (t-value)", size = 20, x = 0.57, y = 2))
 
sex_surf <- make_surface_plot(double.sex, dataset = "Sex Difference", measure = "GAM.cov.tvalue", ylim1 = -3, ylim2  = 3, 
                                   p_label = "", legend = T)

sex_surf <- annotate_figure(sex_surf, bottom = text_grob("Sex Effect (t-value)", size = 20, x = 0.57, y = 2))

 
 
```


```{r hex plot for sex and pfactor}
pfactor_sex_spin_results <- readRDS("/cbica/projects/network_replication/covariate_analyses/sex_diff/output/all_datasets/spin_test/edge/pfactor_sex_effect_schaefer200x17_spin_test_results.RData")

# format pfactor and sex df's in order to combine as wide df
pfactor_to_combine <- clinical.main.all_datasets.edge %>% filter(covariate == "p_factor_mcelroy_harmonized_all_samples") %>% rename(pfactor_tvalue = t_value) %>% select(region, pfactor_tvalue)
sex_to_combine <- clinical.main.all_datasets.edge %>% filter(covariate == "sex") %>% rename(sex_tvalue = t_value) %>% select(region, sex_tvalue)
 
# combine
combined_sex_pfactor <- merge(sex_to_combine, pfactor_to_combine) 
hex_plot_text = bquote(italic(r) == .(round(pfactor_sex_spin_results$observed_r, 2)) * "," ~ italic(p[spin]) < .(format(round(pfactor_sex_spin_results$p_spin, 4), scientific = FALSE)))


sex_pfactor_hexplot <- hex_plot(df = combined_sex_pfactor, x = combined_sex_pfactor$sex_tvalue, y = combined_sex_pfactor$pfactor_tvalue, text = hex_plot_text, ylim1 = -5, ylim2 = 5.5, xlim1 = -11, xlim2 = 11, x_text = -10, y_text = 5.5, x_axis = "Sex Effect (t-value)", y_axis = "P-factor (t-value)", bin_size = 50)  
 
```


```{r combined sex and pfactor plots, fig.height = 15, fig.width = 15}

row1_pfactor_sex <- plot_grid(pfactor_plot, blank_space, sex_pfactor_hexplot, ncol = 3, rel_widths = c(1, 0.1, 1))

row2_pfactor_sex <- plot_grid(pfactor_surf, blank_space, sex_surf, ncol = 3, rel_widths = c(1, 0.15, 1))

plot_grid(row1_pfactor_sex, blank_space, row2_pfactor_sex, nrow = 3, rel_heights = c(1, 0.05, 1))

 
```



